### 2019-09-09 Intro1.tex
Started summary 1

\documentclass[letterpaper,10pt]{article}
\usepackage[top=2cm, bottom=1.5cm, left=1cm, right=1cm]{geometry}
\usepackage{amsmath, amssymb, amsthm,graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}

\lhead{\today}
\chead{MATH 710 Assignment 3}
\rhead{Justin Hood}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newtheorem{lem}{Lemma}

\begin{document}
\end{document}

### 2019-09-09 Intro1.tex
Working..

@@
 \usepackage[top=2cm, bottom=1.5cm, left=1cm, right=1cm]{geometry}
-\usepackage{amsmath, amssymb, amsthm,graphicx}
+\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem}
 \usepackage{fancyhdr}
@@
 \lhead{\today}
-\chead{MATH 710 Assignment 3}
+\chead{MSCS 791 Intro Reading \#1}
 \rhead{Justin Hood}
@@
 \begin{document}
+\begin{itemize}
+\item After an initial skim of the network efficiency paper its purpose appears to be two-fold.
+The paper primarily focuses on delivering the results of numerical simulation of the effects of perturbing the packaging network from equilibrium, and delivering those results in a non-mathematical context that could be presented to industry clients.
+The paper also lays a framework for expanding the model they constructed into a general form for more complex systems or networks.
+\item In ``Analyzing Packaging Network Efficiency", the authors were commissioned by the Kimberly-Clark Corporation to model the effects of machine failure on their packaging network, and other networks in general.
+In particular, the authors were concerned with the packaging network for Huggies\texttrademark .
+This network in particular consists of four ``stages",
+\begin{enumerate}
+\item Network Input (Diapers)
+\item Packaging Diapers into Sleeves
+\item Packaging Sleeves into Boxes
+\item Network Output (Boxes of Diapers on Pallets)
+\end{enumerate}
+and between each stage are a number of ``buffers" that transport the diapers between the machines in a given stage.
+For the Huggies\texttrademark packaging network, the number of machines in a given stage varies depending on the speed of the machines.
+Given that the packaging network can be drawn in a way that is analogus to current running through an electrical circuit, a parallel of Kirchoff's first law takes shape.
+That is to say, that the rate of product flowing into a stage of the packaging process is less than or equal to the net processing rate of all machines in the stage.
+This becomes apparent when considering the network as a whole, as too much product flowing into a given stage would back up the entire process, most likely resulting in scrapped product.\\\\
+The authors began by drawing the entire packaging system as a connected graph, with nodes corresponding to machines in the network, and edges corresponding to buffer connections between the machines of adjacent stages.
+When connected in this manner, the authors were able to apply their analogue of Kirchoff's law to linearly constrain the system, creating a system of rules to optimize.
+Using LINDO the authors were able to optimize the values of the network based on the constraints provided by Kimberly-Clark.
+These optimized rate values form the steady state solution to the network, and as such the authors were then able to implement machine failure into the system to study the effects on network throughput.\\\\
+Once the equilibrium values of the network had been computed, the authors considered machine failure.
+According two Kimberly-Clark, there are two primary types of machine failure that needed to be considered, short-term and long-term.
+The authors also note that machines most often fail within 20 seconds of being started, and that approximately 50\% of all machines will fail within two hours of uptime.
+Using this data, the authors chose to model the probability of machine failure with a log-normal PDF, using the provided parameters from the data.
+This accounts for the spike in failure probability at the beginning of the process, with a gradual reduction as time goes on for the next two hours of runtime.
+With this model of failure probability in place, the authors then consider the downtime distribution for machine repair.
+Given that there are two lengths of common repairs, 30s and 30min, the authors combined two different PDF's into a single
+\end{itemize}
 \end{document}

### 2019-09-10 Intro1.tex
Finished Reading 1

@@
 For the Huggies\texttrademark packaging network, the number of machines in a given stage varies depending on the speed of the machines.
-Given that the packaging network can be drawn in a way that is analogus to current running through an electrical circuit, a parallel of Kirchoff's first law takes shape.
+Given that the packaging network can be drawn in a way that is analogous to current running through an electrical circuit, a parallel of Kirchhoff's first law takes shape.
 That is to say, that the rate of product flowing into a stage of the packaging process is less than or equal to the net processing rate of all machines in the stage.
@@
 The authors began by drawing the entire packaging system as a connected graph, with nodes corresponding to machines in the network, and edges corresponding to buffer connections between the machines of adjacent stages.
-When connected in this manner, the authors were able to apply their analogue of Kirchoff's law to linearly constrain the system, creating a system of rules to optimize.
+When connected in this manner, the authors were able to apply their analogue of Kirchhoff's law to linearly constrain the system, creating a system of rules to optimize.
 Using LINDO the authors were able to optimize the values of the network based on the constraints provided by Kimberly-Clark.
@@
 Using this data, the authors chose to model the probability of machine failure with a log-normal PDF, using the provided parameters from the data.
-This accounts for the spike in failure probability at the beginning of the process, with a gradual reduction as time goes on for the next two hours of runtime.
+This accounts for the spike in failure probability at the beginning of the process, with a gradual reduction as time goes on for the next two hours of run time.
 With this model of failure probability in place, the authors then consider the downtime distribution for machine repair.
-Given that there are two lengths of common repairs, 30s and 30min, the authors combined two different PDF's into a single
+Given that there are two lengths of common repairs, 30s and 30min, the authors combined two different PDF's into a single density function, weighted based on repair data from Kimberly-Clark.
+With this PDF in hand, the CDF can be computed in order to define the ``hazard" rate for the machine repair times.\\\\
+Finally, the authors consider implementing these machine failure functions in a simplified model of the network, in order to test for the effects of altering input variables.
+Their simplified model uses a three stage system, feeding diapers in, bagging them, and finally boxing them.
+In this new system, the failure rates of the machines are modeled along with a count of wasted product due to machine failure, which also takes into account damage to product that is still in the buffer when the machine goes down.
+These values also come from the Kimberly-Clark data.
+Along with waste, the simulation also considers the effect of throughput in the system when one or more machine is down; i.e.
+the effectiveness of the network as a whole.
+Because the goal is to improve the effectiveness of the packaging network, throughput and waste are the primary metrics that can be measured to describe the results.
+After running 500 trials for each set of input perturbations, statistics for the resultant sets were computed.
+The authors discovered that when the mean time for machines to fail was increased, ``Better Machines", the amount of waste in the network was reduced, and the daily throughput was increased as well, though only marginally.
+When the mean repair time was reduced, ``Improved repair protocols", the authors discovered that throughput was increased.
+The conclusion being that improving throughput is closely tied to repair time, and waste is tied to machine reliability.
+\item Figure Analysis:
+\begin{enumerate}
+\item This figure does clearly explain the ``Law of Conservation of Diapers", though it is hard to take out of the context of the paragraph that it is related to.
+Additionally, the color scheme could be challenging for someone who is color blind to interpret.
+I feel that the addition of vertical lines to partition each ``stage" of the process could have improved the readability.
+\item This figure is helpful for understanding the optimized throughput of the model. The numbers are easy to read and add in your head, so it is easy to see how the flow would occur.
+\item This figure describes the sharp uptick in failure at the startup of the machine.
+It could possibly be improved by cutting the length of the $x$ axis to show the degrading slope more clearly towards the beginning, as most readers of this type of paper are likely familiar with exponential decay.
+\item I found this figure to be quite helpful in understanding what the weighted repair time PDF looks like. It also clearly encompasses the two types of repair described in the paper itself.
+\item This figure felt slightly unnecessary, as both the first and second figures describe such a system in more detail, it would likely have been sufficient to merely write a description that detailed the removal of the final step.
+\item This figure clearly shows the distribution for the standard conditions, and was helpful for understand the scope of a given simulation run.
+\item This figure was helpful for showing the results from modifying the long term repair time.
+\item This figure was helpful for showing the results from modifying the median failure time.\\\\
+Overall, I felt that the figures did a good job of explaining the data, though I would have made a few minor quality of life changes.
+\end{enumerate}
+\item While reading this paper, I enjoyed the level of detail that was put into explaining the linear programming approach to the problem.
+By clearly mapping out the relationships in a sort of ``matrix form", it was easy to understand what the LINDO software was attempting to accomplish.
+I also felt that the box plots at the end of the paper clearly enumerated the results in a very readable way.
+\item If I was to make any changes, I would probably change the scopes of the machine failure section and the results section.
+While it is interesting to read about how the PDF's were chosen, and to see the equations, for the scope of this paper it seems slightly overboard, as a representative for Kimberly-Clark may not have the mathematics background to benefit from it.
+For the scope of the problem, as well as the potential audience, it would most likely be more useful to provide a more detailed results section that showcased all of the changes that were tested, as well as the concise results that were given in the paper.
+In addition, I would also have considered providing more summary statistics of the data given, to increase the understanding of the problem space itself.
+\item The questions I have after reading the paper,
+\begin{enumerate}
+\item Why was the final model that was run so simplified compared to the model from Figure 1.?
+\begin{enumerate}
+\item Was it due to computational time constraints?
+\end{enumerate}
+\item How might this model have been used on a more complex network, especially without having to rely on LINDO to recompute the steady states each time?
+\end{enumerate}
 \end{itemize}

### 2019-09-17 Intro Reading 2/Intro2.tex
Setting up for semester
Finished reading #2

--- 2019-09-09 Intro1.tex
@@
 \usepackage[top=2cm, bottom=1.5cm, left=1cm, right=1cm]{geometry}
-\usepackage{amsmath, amssymb, amsthm,graphicx}
+\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem}
 \usepackage{fancyhdr}
 \pagestyle{fancy}
-
 \lhead{\today}
-\chead{MATH 710 Assignment 3}
+\chead{MSCS 791 Intro Reading \# 2}
 \rhead{Justin Hood}
-
 \newcommand{\Z}{\mathbb{Z}}
@@
 \newtheorem{lem}{Lemma}
-
 \begin{document}
+\begin{itemize}
+\item After an initial skim, it appears that the goal of this paper is to explain a new method for processing heart rate tracker from a wearable device on the wrist into usable data.
+The authors note that the gait of a person effects the data from a wrist mounted monitor, and they sought to remove that noise for precise measurements of heart rate.
+\item Based on reading the article itself, as well as noting its original source, I would say that the audience is other industry oriented mathematicians.
+Given the content of SVD and signal processing, I would guess that the audience would also need at least an undergraduate degree, if not some graduate studies as well.
+\item In ``Detecting heart rate while jogging: blind source separation of gait and heartbeat", the authors were tasked to construct a method of isolating heart rate data from potentially noisy data from a wrist mounted photo-diode.
+The authors were told that in prototypes of a new wrist mounted fitness tracker, the users gait was obfuscating the pulse data, and as such, the tracker was computing gait as opposed to pulse from the user.\\\\
+To begin, the authors considered a number of existing modeling strategies and related problems, such as isolating fetal and maternal heartbeats from each other, among others.
+Most of the existing research was able to make use of a known frequency or temporal fact to isolate the signals, e.g.
+fetal heartbeats are much faster than the mothers.
+Because a users pulse and gait are often quite similar, such implicit facts about the system cannot be used in this instance.
+Moving forward, the authors settle on a modified SVD approach to some ``ersatz data" because none was given to them to analyze.\\\\
+The authors obtained arterial blood pressure data as a starting point, and then applied the Beer-Lambert law to transform it from pressure to light intensity data using the map,
+\[I(t)=[1+0.05\sin(7t)]e^{\frac{-0.05P(t)}{\max(P(t))}}\]
+Here, the $0.05$ value corresponds to the noise ratio of the data, the coefficient inside of the sine function is computed from the frequency of the original data, and $P(t)$ is the original pressure data.\\\\
+From this pressure and resultant intensity data, the authors constructed spectrograms in an effort to see if there were any visually distinct characteristics that would assist in the analysis.
+Because the frequencies of pulse and gait are not necessarily distinguishable, the authors note no real discernible value.
+As such, they chose to analyze the phase space using the time series data.
+By plotting the resultant trajectories of the intensity data against itself in a phase plane, the authors were able to isolate two distinct movement types.
+One, the larger and more noticeable were the ``D" shaped paths that correspond to the gait; and two, smaller loops that correspond to heartbeats.\\\\
+Because the authors found a distinction in the behavior of gait and heart beats in the phase space representation, they begin a SVD analysis of the intensity data.
+First, they arranged the data in an $m\times n$ matrix of the following form,
+\[M=\begin{bmatrix}
+I_1 & I_{2} & \ldots & I_{n}\\
+I_{n+1} & \ddots & \ldots & \vdots
+\end{bmatrix}\]
+and then computed the SVD decomposition,
+\[M_{m\times n}=U_{m\times m}S_{m\times n}V^T_{n\times n}\]
+By construction, the $S$ matrix contains the singular values sorted by magnitude.
+Because the ``D" shape occurred in two dimensions, the authors created a new matrix by setting the two largest singular values to zero and recomputing the $M$ matrix.
+This new matrix contains the heartbeat pulse data, without the gait interference in the same form as the original $M$ matrix, and as such, the time series can be extracted and plotted.\\\\
+The authors discovered that the resultant data from the modified SVD matrix exactly matched the original pressure data that they began with, with no interference from the gait function.
+In addition, by rectifying and smoothing the signal, a plot that is almost identical to the original pressure data can be obtained.
+As such, they have found a means of isolating the original heartbeat signal from noisy data that they note is not sensitive to the amount of input data given, which is crucial for a wearable application.
+\item Figure Analysis:
+\begin{enumerate}
+\item This figure was helpful to understand the product that was generating the noisy data.
+\item I found this figure to be helpful for seeing both what the ``ersatz pulse" looked like and what the resultant measurement the monitor would be making.
+\item I felt that this figure was not necessary to include, especially because the authors note that nothing can be concluded from the plots.
+\item This figure was very helpful in understanding what their phase reconstruction resulted in, and was helpful to show the difference in gait and pulse in the data.
+\item I found this figure helpful in seeing each step of the analysis process in order.
+\item I found this figure helpful in seeing each step of the analysis process in order, especially since this model shows that the analysis is robust to different gait inputs.
+\item This figure is a powerful statement of how accurate their analysis was. To see the original pulses lined up with the output reaffirmed the accuracy of the analysis.
+\item I did not find this figure to be particularly helpful. A combination of Figure 7 and Figure 5 is much easier to understand than an overlay in this manner, at least to me.
+\item This figure was helpful to understand the reconstruction and smoothing of the result signal vs the original pulse data in another form.
+\end{enumerate}
+\item While reading this paper, I enjoyed the level of detail that was put into each step of the analysis.
+I never felt like the authors were leaving too many details out, or making jumps that I could not easily follow.
+\item If I was to change anything about this paper, I would have added a little more detail into the phase space reconstruction portion, specifically in the area where they note the ``D" loops, and what they mean.
+\item Questions:
+\begin{enumerate}
+\item Given their statement about the lack of sensitivity to the length of the input time series, what would their ideal length be?
+\begin{enumerate}
+\item I ask this because they never address the changing in pace of an athlete.
+The tracker will have to be able to account for the gradual increases and decreases in speed and heart rate from the users.
+A runner that starts a warm-up by walking and gradually increases to a full sprint will see their gait change much more quickly than their pulse, especially at a professional level.
+As such, the amount of data being actively filtered would need to account for that.
+\end{enumerate}
+\item As someone who has never worked with the Beer-Lambert law, how was this model function derived?
+\end{enumerate}
+\item Upon reading this paper, I feel fairly comfortable with the mechanics of the process.
+I am fairly familiar with the SVD application portion, so that made sense to me.
+The only part that confused me at first was the phase space reconstruction, but upon some reflection, I was able to make the connection to Lorenz attractors, and I remembered from my undergraduate doing phase plane analysis and bifurcation analysis.
+\item While reading this paper, I needed to remind myself of the phase plane construction, and after some brief research, I was able to find the following article online, which helped me recall some hazy details.\\
+$http://www.scholarpedia.org/article/Attractor\_reconstruction$
+\end{itemize}
 \end{document}

### 2019-09-30 NHL/NHL Report.tex
Workin on report

\documentclass[11pt]{report}            % Report class in 11 points
\parindent0pt  \parskip10pt             % make block paragraphs
\raggedright                            % do not right-justify
\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem, threeparttable, hyperref,gensymb}
\newcommand{\ro}{\mathcal{R}_0}
\makeatletter
\newcommand*{\centerfloat}{%
  \parindent \z@
  \leftskip \z@ \@plus 1fil \@minus \textwidth
  \rightskip\leftskip
  \parfillskip \z@skip}
\makeatother

\title{\bf Hockey Hockey Hockey\\
\large and more Hockey}  % Supply information
\author{Justin Hood\\
MSCS 791}              %   for the title page.
\date{\today}                           %   Use current date.

\begin{document}                        % End of preamble, start of text.
\maketitle                              % Print title page.
\pagenumbering{roman}                   % roman page number for toc
\setcounter{page}{2}                    % make it start with "ii"
\tableofcontents                        % Print table of contents
\newpage
%\setcounter{section}{1}
\section*{Introduction}                % Print a "chapter" heading\
\addcontentsline{toc}{section}{Introduction}
\pagenumbering{arabic}                  % Start text with arabic 1
As with any professional sporting league, the number of teams and their spatial distribution relative to one another is very important, and for the National Hockey League (NHL), this is no exception. \textit{In fact, it is possibly even more important given the seasonal and temperature dependent nature of the game itself.} When new teams are added to the league, they may have negative impacts on nearby teams, as well as struggle to be profitable if placed in an unfitting locale. Of all leagues, it seems that the NHL feels these impacts the most, as hockey requires just as much specialized equipment, if not more than other sports, but the NHL also lacks many of the national TV contracts that other professional sports use as a source of revenue\cite{light}. As such, expansion of the NHL is a complex problem that encompasses a large number of varibles. 
************* MIL vs ORD/MIL *******************************************
\section*{Methods}
\addcontentsline{toc}{section}{Methods}
\subsection*{SIR Model}
\addcontentsline{toc}{subsection}{SIR Model}
Given that the sucess of a team in the NHL is mostly dependent on fan base size and growth, we consider fan loyalty to spread as in a traditional SIR disease model as in Light \textit{et al}.\cite{light} The model for two geographically close teams follows, the isolated geographic case follows quite easily.
\begin{equation} \label{SIRMODEL}
\begin{split}
\dot{S} &= -S[\beta_1(I_1+C_1)+\beta_2(I_2+C_2)]\\
\dot{I}_1 &= \beta_1S(I_1+C_1)-\gamma I_1-\alpha_1I_1+\delta_{21}[(I_1+C_1)I_2]-\delta_{12}[I_1(I_2+C_2)]\\
\dot{I}_2 &= \beta_2S(I_2+C_2)-\gamma I_2-\alpha_2I_2+\delta_{12}[(I_2+C_2)I_1]-\delta_{21}[I_2(I_1+C_1)]\\
\dot{C}_1 &= \alpha_1I_1\\
\dot{C}_2 &= \alpha_2I_2\\
\dot{R} &= \gamma (I_1+I_2)\\
N &= S+I_1+I_2+C_1+C_2+R
\end{split}
\end{equation}
As in \cite{light}, we consider a model of disease spread that includes a ``Chronically infected" fan category. As the SIR model is well studied, we know that we may compute the basic reprodictive ratio $\ro$ as,
\[\ro =\frac{\beta N}{\gamma}\]
with $\beta$ the mean rate of transmission of fan allegiance for a given team, $N$ is the population drawn from, and $1/\gamma$ is the mean transmission period, or ~9 months (1 Season). Knowing that $\ro>1$ means that the infected population is growing, and that $\ro<1$ is a dying infected population, we consider our computation of $\beta$ subject to this constraint.
\subsection*{Beta}
\addcontentsline{toc}{subsection}{Beta}
$\beta$ is a product of many factors, the main being team success, physical locale (weather, population, income), and the social environment\cite{light}.
\subsubsection*{Team Success}
\addcontentsline{toc}{subsection}{Team Success}
The success of a team can be quantified as a function of its successes in previous post seasons following the following equation,
\begin{equation}\label{Success}
S_t = \frac{1.875PSA+3.75PSW+30SC}{N}
\end{equation}
Where, $PSA$ is the number of series appearances by a team, $PSW$ is the number of wins, and $SC$ is the number of stanley cups won over $N$ seasons. Taking the analysis of 2001-2015 from Light \textit{et al.}\cite{light}, and extending it to include the seasons that have passed in the interim, we arrive at the updated Tables \ref{table:Revenue}, \ref{table:St} below.

\begin{table}[ht]
\centerfloat
\begin{tabular}{lrrrr}
\hline
\multicolumn{5}{c}{Revenue and Success Rates of NHL Teams 2001-2019} \\
Team & Revenue$^a$ & Playoff Appearances$^b$ & Playoff Wins$^c$ & Stanley Cup Wins$^d$ \\ 
\hline
Anaheim Ducks & 134 &  26 &  15 &   1 \\ 
Arizona Coyotes &  96 &   6 &   2 &   0 \\ 
Boston Bruins & 191 &  26 &  14 &   1 \\ 
Buffalo Sabres & 128 &  10 &   5 &   0 \\ 
Calgary Flames & 132 &  12 &   4 &   0 \\ 
Carolina Hurricanes & 109 &  15 &  11 &   1 \\ 
Chicago Blackhawks & 201 &  24 &  16 &   3 \\ 
Colorado Avalanche & 119 &  19 &  10 &   1 \\ 
Columbus Blue Jackets & 111 &   6 &   1 &   0 \\ 
Dallas Stars & 144 &  15 &   6 &   0 \\ 
Detroit Red Wings & 171 &  30 &  17 &   2 \\ 
Edmonton Oilers & 145 &   8 &   4 &   0 \\ 
Florida Panthers &  99 &   3 &   0 &   0 \\ 
L.A. Kings & 193 &  18 &  11 &   2 \\ 
Minnesota Wild & 142 &  13 &   4 &   0 \\ 
Montreal Canadians & 239 &  19 &   8 &   0 \\ 
Nashville Predators & 132 &  19 &   7 &   0 \\ 
New Jersey Devils & 166 &  22 &  12 &   1 \\ 
New York Islanders & 107 &  10 &   2 &   0 \\ 
New York Rangers & 253 &  22 &  11 &   0 \\ 
Ottawa Senators & 124 &  21 &  10 &   0 \\ 
Philadelphia Flyers & 186 &  23 &  10 &   0 \\ 
Pittsburgh Penguins & 185 &  33 &  22 &   3 \\ 
San Jose Sharks & 148 &  23 &  10 &   0 \\ 
St. Louis Blues & 148 &  32 &  18 &   1 \\ 
Tampa Bay Lightning & 146 &  23 &  14 &   1 \\ 
Toronto Maple Leafs & 232 &  12 &   4 &   0 \\ 
Vancouver Canucks & 168 &  18 &   7 &   0 \\ 
Washington Capitals & 194 &  22 &  10 &   1 \\ 
Winnipeg Jets & 135 &   5 &   2 &   0 \\ 
Las Vegas Knights & 180 &   5 &   3 &   0 \\ 
\hline
\end{tabular}
\caption{$^a$in Millions of USD as of 2018 \cite{money}; $^b$Playoff series appearances 2001-2019 \cite{stats}; $^c$Playoff series wins 2001-2019 \cite{stats}; $^d$Stanley Cup wins 2001-2019 \cite{stats}}
\label{table:Revenue}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{lrr}
\hline
\multicolumn{3}{c}{Computed and Normalized Success Scores by Team} \\
Team & $S_t^a$ & $s_t^b$ \\ 
\hline
Anaheim Ducks & 7.50 & 1.63 \\ 
Arizona Coyotes & 1.04 & 0.23 \\ 
Boston Bruins & 7.29 & 1.59 \\ 
Buffalo Sabres & 2.08 & 0.45 \\ 
Calgary Flames & 2.08 & 0.45 \\ 
Carolina Hurricanes & 5.52 & 1.20 \\ 
Chicago Blackhawks & 10.83 & 2.36 \\ 
Colorado Avalanche & 5.73 & 1.25 \\ 
Columbus Blue Jackets & 0.83 & 0.18 \\ 
Dallas Stars & 2.81 & 0.61 \\ 
Detroit Red Wings & 10.00 & 2.18 \\ 
Edmonton Oilers & 1.67 & 0.36 \\ 
Florida Panthers & 0.31 & 0.07 \\ 
L.A. Kings & 7.50 & 1.63 \\ 
Minnesota Wild & 2.19 & 0.48 \\ 
Nashville Predators & 3.44 & 0.75 \\ 
New Jersey Devils & 6.46 & 1.40 \\ 
New York Islanders & 1.46 & 0.32 \\ 
New York Rangers & 4.58 & 1.00 \\ 
Ottawa Senators & 4.27 & 0.93 \\ 
Philadelphia Flyers & 4.48 & 0.97 \\ 
Pittsburgh Penguins & 13.02 & 2.83 \\ 
San Jose Sharks & 4.48 & 0.97 \\ 
St. Louis Blues & 8.75 & 1.90 \\ 
Tampa Bay Lightning & 6.98 & 1.52 \\ 
Toronto Maple Leafs & 2.08 & 0.45 \\ 
Vancouver Canucks & 3.33 & 0.73 \\ 
Washington Capitals & 6.04 & 1.31 \\ 
Winnipeg Jets & 0.94 & 0.20 \\ 
Las Vegas Knights & 1.15 & 0.25 \\ 
\hline
\end{tabular}
\caption{$^a$Table \ref{table:Revenue} and Eq. \ref{Success}; $^b$Normalized by mean of $S_t$}
\label{table:St}
\end{table}
\subsubsection*{Locale}
\addcontentsline{toc}{subsection}{Locale}
The location of a team is very important for hockey. A number of teams in the NHL consistently struggle in terms of revenue, seemingly due to what Light \textit{et al.} and Jones call low locational quality\cite{light}\cite{jones}. In Jones and Ferguson \cite{jones}, the variable,
\begin{equation}\label{ht}
H_t=\frac{1}{4}\frac{a_t^2}{b_t^2}
\end{equation}
is defined to be the locational quality, dependent on the equations,
\begin{equation}\label{a}
\log(a_t) = \alpha_0+\alpha_1(CAN)+\alpha_2\log(POP)+\alpha_3\log(INC)
\end{equation}
\begin{equation}\label{b}
\log(b_t) = \beta_0+\beta_1(CAN)+\beta_2\log(POP)+\beta_3\log(INC)
\end{equation}
Where $CAN$ is a binary variable, $POP$ is the population of the metro area in millions, and $INC$ is GDP per capita of the area. For our analysis, we shall take the convention of Light \textit{et al.}, and replace the $CAN$ variable with a variable called $WINT$, which will be a binary value describing if a location has a colder mean monthly temperature than 6 \degree C. Using the data from Table 3 of \cite{light}, we perform a least squares regression on the locational data in an attempt to compute the coefficents $\alpha_i,\ \beta_i$ from \ref{a} and \ref{b}. The coefficients we obtain are,
\begin{equation}\label{acoeff}
\log(a_t) = 14.1 + 0.2205(WINT)+.091\log(POP)-0.3766\log(INC)
\end{equation}
\begin{equation}\label{bcoeff}
\log(b_t) = 9.171 + .03(WINT)+.028\log(POP)-.1879\log(INC)
\end{equation}
Each of the coefficents of these regressions are significant at the $\alpha=10^{-6}$ level, so we know to keep them for our analysis.

\subsubsection*{Social Environment}
\addcontentsline{toc}{subsection}{Social Environment}

\begin{thebibliography}{9}
\bibitem{light} J. Light, A. Chernin, and J. M. Heffernan, ``NHL expansion and fan allegiance: a mathematical modelling study,” \textit{Mathematics-in-Industry Case Studies}, vol. 7, no. 1, Apr. 2016.
\bibitem{money} M. Ozanian and K. Badenhausen, ``The NHLs Most Valuable Teams” \textit{Forbes}, 21-Feb-2019. [Online]. Available: \url{https://www.forbes.com/sites/mikeozanian/2018/12/05/the-nhls-most-valuable-teams/}. [Accessed: 25-Sep-2019].
\bibitem{stats}  HockeyDB.com (2019) National Hockey League history and statistics. \url{http://www.hockeydb.com/ihdb/stats/leagues/141.html}. Web
\bibitem{jones}J. C. H. Jones and D. G. Ferguson, ``Location and Survival in the National Hockey League,” \textit{The Journal of Industrial Economics}, vol. 36, no. 4, p. 443, Jun. 1988.
\end{thebibliography}
\end{document}                          % The required last line

### 2019-09-30 NHL/NHL.R

@@ -1,0 +1,56 @@
+#setwd("~/Desktop/PSM/Fall 2019/Capstone/NHL")
+################################################
+########### H_t ################################
+rm(list = ls())
+library(xtable)
+X=read.csv("./hvals.csv")
+
+## All Team data a_t computation
+ALLTEAMS=X[,c(2,3,5,6,7,9)]
+amod <- lm(log(a)~WINT+log(POP)+log(INC), data=ALLTEAMS)
+summary(amod)
+bmod <- lm(log(b)~WINT+log(POP)+log(INC), data=ALLTEAMS)
+summary(bmod)
+
+## Only WINT teams
+# WINTTEAMS<-ALLTEAMS[which(ALLTEAMS$WINT==1),]
+# amodWINT <- lm(log(a)~WINT+log(POP)+log(INC), data=WINTTEAMS)
+# summary(amodWINT)
+# bmodWINT <- lm(log(b)~WINT+log(POP)+log(INC), data=WINTTEAMS)
+# summary(bmodWINT)
+
+#Milwaukee Data
+MIL=data.frame("POP"=1.572245,"INC"=73805,"WINT"=1)
+(a_MIL=exp(predict(amod,MIL)))
+(b_MIL=exp(predict(bmod,MIL)))
+(H_MIL=(1/4)*(a_MIL^2)/(b_MIL^2))
+
+(h_mil = H_MIL/mean(X$H_t))
+
+#####################################################
+################# S_t ###############################
+X=read.csv("./success.csv")
+SDat <- data.frame(X$Team,X$Revenue,X$Playoff.Appearances.Total,X$Playoff.Wins.Total,X$Stanley.Cup.Total)
+S_t <- ((30/16)*SDat$X.Playoff.Appearances.Total+(30/8)*SDat$X.Playoff.Wins.Total+30*SDat$X.Stanley.Cup.Total)/sum(SDat$X.Stanley.Cup.Total)
+s_t <- S_t/mean(S_t)
+SDat$S_t=S_t
+SDat$s_t=s_t
+RevenueTable = data.frame("Team"=SDat$X.Team, "Revenue"=SDat$X.Revenue, "Playoff Appearances"=SDat$X.Playoff.Appearances.Total, "Playoff Wins"=SDat$X.Playoff.Wins.Total, "Stanley Cup Wins"=SDat$X.Stanley.Cup.Total)
+print(xtable(RevenueTable, type="latex"), file="RevenueTable.tex")
[…]

### 2019-09-30 NHL/NHL.R
Oh boy

@@ -20,7 +20,7 @@ summary(bmod)
 # summary(bmodWINT)
 
 #Milwaukee Data
-MIL=data.frame("POP"=1.572245,"INC"=73805,"WINT"=1)
+MIL=data.frame("POP"=1.572245,"INC"=58680,"WINT"=1)
 (a_MIL=exp(predict(amod,MIL)))
 (b_MIL=exp(predict(bmod,MIL)))
 (H_MIL=(1/4)*(a_MIL^2)/(b_MIL^2))

### 2019-09-30 NHL/NHL Report.tex
Cruising

@@
 \raggedright                            % do not right-justify
-\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem, threeparttable, hyperref,gensymb}
+\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem, hyperref,gensymb, float} %, threeparttable}
 \newcommand{\ro}{\mathcal{R}_0}
@@
 
+%*******************************************************************%
 \title{\bf Hockey Hockey Hockey\\
@@
 Of all leagues, it seems that the NHL feels these impacts the most, as hockey requires just as much specialized equipment, if not more than other sports, but the NHL also lacks many of the national TV contracts that other professional sports use as a source of revenue\cite{light}.
-As such, expansion of the NHL is a complex problem that encompasses a large number of varibles.
+As such, expansion of the NHL is a complex problem that encompasses a large number of variables.
+In this case study, we will assess the viability of Milwaukee as a potential expansion location, and the possible effects of Chicago's proximity.
 ************* MIL vs ORD/MIL *******************************************
@@
 \addcontentsline{toc}{subsection}{SIR Model}
-Given that the sucess of a team in the NHL is mostly dependent on fan base size and growth, we consider fan loyalty to spread as in a traditional SIR disease model as in Light \textit{et al}.\cite{light} The model for two geographically close teams follows, the isolated geographic case follows quite easily.
+Given that the success of a team in the NHL is largely dependent on fan base size and growth, we may effectively model a teams success by modeling the fan base size.
+We consider fan loyalty to spread as in a traditional SIR disease model as in Light \textit{et al}\cite{light}, as people are more likely to become fans when exposed to fans.
+The model for two geographically close teams follows, the isolated geographic case follows quite easily.
 \begin{equation} \label{SIRMODEL}
@@
 \end{equation}
+Here, $S$ corresponds to the susceptible population, people without a team loyalty.
+$I_i$ corresponds to the normal fans of team $i$ and $C_i$ corresponds to avid fans, and $R$ represents people who were fans of a team, but have lost their loyalty.
+These fans are often not willing to choose an allegiance to a new team immediately, and as such, they remain a separate population in our model.
 As in \cite{light}, we consider a model of disease spread that includes a ``Chronically infected" fan category.
-As the SIR model is well studied, we know that we may compute the basic reprodictive ratio $\ro$ as,
+These ``chronically infected" fans are those who are very loyal to their team, and will likely remain ``infected" regardless of how many seasons are considered.
+Accordingly, these categories in (\ref{SIRMODEL}), $C_1,C_2$ have no loss of population, and can only increase in size.
+\\
+Because the standard SIR model is well studied, we know that we may compute the basic reproductive ratio $\ro$ of the ``disease" as,
 \[\ro =\frac{\beta N}{\gamma}\]
-with $\beta$ the mean rate of transmission of fan allegiance for a given team, $N$ is the population drawn from, and $1/\gamma$ is the mean transmission period, or ~9 months (1 Season).
-Knowing that $\ro>1$ means that the infected population is growing, and that $\ro<1$ is a dying infected population, we consider our computation of $\beta$ subject to this constraint.
+with $\beta$ equal to the mean rate of transmission of fan allegiance for a given team, $N$ is the population drawn from, and $1/\gamma$ is the mean transmission period, or $\sim 9$ months (1 Season).
+Knowing that $\ro>1$ means that the fan base is growing, and that $\ro<1$ is a dying fan base, we consider our computation of $\beta$ subject to this constraint.
 \subsection*{Beta}
 \addcontentsline{toc}{subsection}{Beta}
-$\beta$ is a product of many factors, the main being team success, physical locale (weather, population, income), and the social environment\cite{light}.
+$\beta$ is a product of many factors, the main being team success, physical locale (weather, population, income), and the social environment of the city\cite{light}.
+The quantification of these factors is the bulk?
+of our analysis.
 \subsubsection*{Team Success}
 \addcontentsline{toc}{subsection}{Team Success}
-The success of a team can be quantified as a function of its successes in previous post seasons following the following equation,
+The success of a team can be quantified as a function of its successes in past post seasons following the following equation,
 \begin{equation}\label{Success}
@@
 \end{equation}
-Where, $PSA$ is the number of series appearances by a team, $PSW$ is the number of wins, and $SC$ is the number of stanley cups won over $N$ seasons.
+Where, $PSA$ is the number of playoff series appearances by a team, $PSW$ is the number of playoff series wins, and $SC$ is the number of stanley cups won over $N$ seasons.
 Taking the analysis of 2001-2015 from Light \textit{et al.}\cite{light}, and extending it to include the seasons that have passed in the interim, we arrive at the updated Tables \ref{table:Revenue}, \ref{table:St} below.
+Table \ref{table:Revenue} contains the data related to existing team revenue and the variables in (\ref{Success}).
+Table \ref{table:St} contains the computations of $S_t$ and its normalized counterpart $s_t$.
+From these tables, we begin to obtain a sense of how the success of teams such as the Blackhawks and Red Wings generates high normalized success scores, while teams such as the Coyotes who's success is low in post season play have lower normalized scores.
+This aligns with our assumption that team success will be an important factor in computing $\beta$ for a given team.
 
-\begin{table}[ht]
+\begin{table}[htp]
 \centerfloat
@@
 
-\begin{table}[ht]
+\begin{table}[htp]
 \centering
@@
 \end{equation}
-is defined to be the locational quality, dependent on the equations,
+is defined to be the location quality, dependent on the equations,
 \begin{equation}\label{a}
@@
 \end{equation}
-Where $CAN$ is a binary variable, $POP$ is the population of the metro area in millions, and $INC$ is GDP per capita of the area.
+Where $CAN$ is a binary variable describing if a team is located in Canada, $POP$ is the population of the metro area in millions, and $INC$ is GDP per capita of the area.
 For our analysis, we shall take the convention of Light \textit{et al.}, and replace the $CAN$ variable with a variable called $WINT$, which will be a binary value describing if a location has a colder mean monthly temperature than 6 \degree C.
-Using the data from Table 3 of \cite{light}, we perform a least squares regression on the locational data in an attempt to compute the coefficents $\alpha_i,\ \beta_i$ from \ref{a} and \ref{b}.
+Using the data from Table 3 of \cite{light}, we perform a least squares regression on the location data in an attempt to compute the coefficients $\alpha_i,\ \beta_i$ from \ref{a} and \ref{b}.
 The coefficients we obtain are,
@@
 \end{equation}
-Each of the coefficents of these regressions are significant at the $\alpha=10^{-6}$ level, so we know to keep them for our analysis.
+Each of the coefficients we compute have incredibly large T-scores, which aligns with the linear nature of (\ref{a}) and (\ref{b}).
+As such, we are confident that these coefficients are correct for the purposes of our analysis.
+With these coefficients computed, we can compute the following location score for our potential Milwaukee team,
+\begin{table}[H]
+\centerfloat
+\begin{tabular}{lrrrrrrrr}
+\hline
+\multicolumn{9}{c}{Location Score for Milwaukee} \\
+Team & Population$^a$ & GDP per capita$^b$ & Temperature$^c$ & WINT & $a_t$ & $b_t$ & $H_t$ & $h_t$\\
+\hline
+Milwaukee & 1.572245 & \$58,680.00 & -2 & 1 & 27583.4 & 1274.342 & 117.1288 & 0.9990123
+\end{tabular}
+\caption{$^a$in Millions *CITE*; $^b$USD *CITE*; $^c$ \degree C *CITE*}
+\label{table:Milwaukee_H}
+\end{table}
+So, we see that Milwaukee has a location score that is approximately equal to the mean score for all existing teams.
+Based on the analysis in \cite{light}, we see that this score is similar to, Boston (121.91), Edmonton (111.6611), and Winnipeg (121.93).
+So, when considering the necessary team success score for Milwaukee, we will compare with these teams.
 
@@
 \addcontentsline{toc}{subsection}{Social Environment}
+Finally, we consider how the social environment of a susceptible person could influence the rate at which allegiance can spread. As with \cite{light}, we consider three cases,
+\begin{enumerate}
+\item $p=0.05$: no regular contact with any existing fans\\
+\item $p=0.25$: some friends or family in $I_t$\\
+\item $p=0.75$: friends or family in $C_t$
+\end{enumerate}
 

### 2019-10-15 Mayo/Timeline/Proposal.tex
timeline

\documentclass[letterpaper,10pt]{article}
\usepackage[top=2cm, bottom=1.5cm, left=1cm, right=1cm]{geometry}
\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\today}
\chead{MSCS 791 Mayo Project Proposal and Timeline}
\rhead{Justin Hood}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newtheorem{lem}{Lemma}
\begin{document}
In this case study, we are tasked with optimizing a pharmacies workflow under the constraints related to both the number of and types of employees available.\\\\
The initial problem that must be solved is to construct a model of the starting conditions. We are given that there are 5 pharmacy technicians and 2 pharmacists available to work in our hypothetical pharmacy environment, wherein they process two types of drugs, oral and IV. These two different jobs have tasks as follows:
\begin{center}
\begin{tabular}{|c|c|}
\hline
Technician & Pharmacist\\\hline\hline
Order Entry & Order Entry \\\hline
& Entry Verification \\\hline
Drug Preparation & Drug Preparation\\\hline
& Preparation Verification\\\hline
Distribution through Window & Distribution through Window\\\hline
\end{tabular}
\end{center}
So, we see that the tasks that a technician may perform are a proper subset of the tasks a pharmacist may perform. In addition to this role constraint, only one technician is initially allocated to the task of filling IV specific prescriptions. First, a full process flow chart must be constructed. Based on the rough explanation in the problem and an initial study of the given papers, we may construct an initial flowchart as follows:
\begin{center}
\includegraphics[scale=.5]{Flowchart.png}
\end{center}
We note that in our rough chart, that the filling of the IV prescription is done in an isolated room by an individual technician, which will present a challenge when it comes to the construction of the model.\\\\
In addition to the working constraints, we are also provided with data related to the incoming order times for both IV and oral drugs. We know that the IV times are distributed exponentially, but the oral distribution is unknown. In order to model this pharmacy environment, the distribution of this data set must be identified. If I recall correctly we may be able to compare the unknown data to other potential distributions using the Kolmogorov-Smirnov test. This test will enable us to compare the data to potential distributions, with the only weakness coming from our lack of knowledge of the parameters in the potential distribution, however it is possible to rule out distributions based on the shape of the data itself, reducing the number of parameter estimates required. This same process can be applied to the data for entry, prep, and verification times.\\\\
With these distribution estimates in hand, as well as our model of the process, we can use a discrete event modeling program such as Arena to simulate the events over a day of work. Software like Arena will provide us with the necessary statistics for the problem, like utilization of employees.\\\\
Using the results from our simulation, we will attempt to optimize the process. This could involve increasing or decreasing employees in either category, as well as changing the workflow of the process dependent on the results of the summary statistics from the base model.\\\\
A tentative timeline follows:\\
\begin{itemize}
\item October 13-18: Review provided material. Establish complete understanding of problem, and ask relevant initial questions related to the parameters of the problem. Review relevant concepts for distributions, and Arena programming.
\item October 19-22: Analyze the unknown data distributions to arrive at potential models. Attempt a first run in Arena of base model.
\item October 23: Status Report \# 1
\item October 24-31: Refine model in Arena. Ensure base case is correct.
\item November 1-7: Consider potential optimizations to the model, begin implementation.
\item November 8-13: Fully implement optimizations in model, address any issues that arise from comparison to base case.
\item November 13: Status Report \# 2
\item November 14-21: Begin drafting of project, construction of relevant figures and summary data sets.
\item November 22-Dec 1: Finish Draft
\item December 2: Rough Draft
\item December 3-12: Use feedback to correct and finish project.
\item December 13: Final Project Submission
\end{itemize}
\end{document}

### 2019-10-15 NHL/NHL Report.tex
timeline

@@
 \makeatother
-
 %*******************************************************************%
-\title{\bf Hockey Hockey Hockey\\
-\large and more Hockey}  % Supply information
+\title{\bf An Evaluation of Milwaukee as a Candidate for NHL Expansion\\
+\large Using an SIR Model Approach}  % Supply information
 \author{Justin Hood\\
@@
 \date{\today}                           %   Use current date.
-
 \begin{document}                        % End of preamble, start of text.
@@
 \newpage
-%\setcounter{section}{1}
+\section*{Abstract}
+\addcontentsline{toc}{section}{Abstract}
+As the National Hockey League continues to grow, the assessment of viable expansion location becomes increasingly more important.
+Using a model of fan allegiance represented as an infectious disease, we will test whether the city of Milwaukee is a viable candidate for a new NHL team.
+For this analysis we will consider Milwaukee as an isolated city, as well as the geographic impact of having the Chicago Blackhawks within 100 miles.
+Upon analyzing the requisite team success rate for a team in Milwaukee, we find that it is a viable candidate when Chicago is ignored; but the presence of a successful rival team could prove to be sub optimal in the long term.
 \section*{Introduction}                % Print a "chapter" heading\
@@
 As with any professional sporting league, the number of teams and their spatial distribution relative to one another is very important, and for the National Hockey League (NHL), this is no exception.
-\textit{In fact, it is possibly even more important given the seasonal and temperature dependent nature of the game itself.} When new teams are added to the league, they may have negative impacts on nearby teams, as well as struggle to be profitable if placed in an unfitting locale.
-Of all leagues, it seems that the NHL feels these impacts the most, as hockey requires just as much specialized equipment, if not more than other sports, but the NHL also lacks many of the national TV contracts that other professional sports use as a source of revenue\cite{light}.
+In fact, it is possibly even more important given the seasonal and temperature dependent nature of the game itself.
+When new teams are added to the league, they may have negative impacts on the revenue and stability of nearby teams, as well as struggle to be profitable if placed in an unfitting locale.
+Of all leagues, it seems that the NHL feels these impacts the most, as hockey requires just as much specialized equipment, if not more than other sports, but the NHL also lacks many of the national TV contracts that other professional sports use as a major source of revenue\cite{light}.
 As such, expansion of the NHL is a complex problem that encompasses a large number of variables.
 In this case study, we will assess the viability of Milwaukee as a potential expansion location, and the possible effects of Chicago's proximity.
-************* MIL vs ORD/MIL *******************************************
+By considering fan allegiance to a team as a spreadable ``disease", we shall implement an SIR model and analyze the $\ro$ value to determine Milwaukees potential viability as a location for the next new NHL team.
 \section*{Methods}
@@
 Given that the success of a team in the NHL is largely dependent on fan base size and growth, we may effectively model a teams success by modeling the fan base size.
-We consider fan loyalty to spread as in a traditional SIR disease model as in Light \textit{et al}\cite{light}, as people are more likely to become fans when exposed to fans.
-The model for two geographically close teams follows, the isolated geographic case follows quite easily.
+We consider fan loyalty to spread like a disease would under a traditional SIR disease model.\cite{light}, as people are more likely to become fans when exposed to fans.
+The model for two geographically close teams follows, the isolated geographic case follows quite easily by removing the second categories for each population, as well as the cross terms.
 \begin{equation} \label{SIRMODEL}
@@
 $\beta$ is a product of many factors, the main being team success, physical locale (weather, population, income), and the social environment of the city\cite{light}.
-The quantification of these factors is the bulk?
-of our analysis.
+In order to compute a given teams $\beta$ value, we must quantify these factors as follows.
 \subsubsection*{Team Success}
@@
 \end{equation}
-Where, $PSA$ is the number of playoff series appearances by a team, $PSW$ is the number of playoff series wins, and $SC$ is the number of stanley cups won over $N$ seasons.
+Where, $PSA$ is the number of playoff series appearances by a team, $PSW$ is the number of playoff series wins, and $SC$ is the number of Stanley cups won over $N$ seasons.
 Taking the analysis of 2001-2015 from Light \textit{et al.}\cite{light}, and extending it to include the seasons that have passed in the interim, we arrive at the updated Tables \ref{table:Revenue}, \ref{table:St} below.
@@
 Table \ref{table:St} contains the computations of $S_t$ and its normalized counterpart $s_t$.
-From these tables, we begin to obtain a sense of how the success of teams such as the Blackhawks and Red Wings generates high normalized success scores, while teams such as the Coyotes who's success is low in post season play have lower normalized scores.
+This normalization is extended to include the data from the Las Vegas Golden Knights, a team who joined the league following the publication of \cite{light}.
+From these tables, we begin to obtain a sense of how the success of teams influences the potential revenue of a franchise.
+Teams such as the Blackhawks and Red Wings generate high normalized success scores, and have some of the highest revenues in the league, while teams such as the Coyotes with low success rates in post season play have lower normalized scores, and lower incomes.
 This aligns with our assumption that team success will be an important factor in computing $\beta$ for a given team.
-
 \begin{table}[htp]
@@
 \end{table}
-
 \begin{table}[htp]
@@
 \addcontentsline{toc}{subsection}{Locale}
-The location of a team is very important for hockey.
-A number of teams in the NHL consistently struggle in terms of revenue, seemingly due to what Light \textit{et al.} and Jones call low locational quality\cite{light}\cite{jones}.
+In addition to team success rates, the location of a team is very important for hockey.
+A number of teams in the NHL consistently struggle in terms of revenue, seemingly due to what Light \textit{et al.} and Jones call low location quality\cite{light}\cite{jones}.
 In Jones and Ferguson \cite{jones}, the variable,
@@
 For our analysis, we shall take the convention of Light \textit{et al.}, and replace the $CAN$ variable with a variable called $WINT$, which will be a binary value describing if a location has a colder mean monthly temperature than 6 \degree C.
-Using the data from Table 3 of \cite{light}, we perform a least squares regression on the location data in an attempt to compute the coefficients $\alpha_i,\ \beta_i$ from \ref{a} and \ref{b}.
+Using the data from Table 3 of \cite{light}, we perform a least squares regression on the location data in an attempt to compute the coefficients $\alpha_i,\ \beta_i$ from (\ref{a}) and (\ref{b}).
 The coefficients we obtain are,
@@
 \end{equation}
-Each of the coefficients we compute have incredibly large T-scores, which aligns with the linear nature of (\ref{a}) and (\ref{b}).
+Each of the coefficients we compute have incredibly large t-values, which aligns with the linear nature of (\ref{a}) and (\ref{b}).
 As such, we are confident that these coefficients are correct for the purposes of our analysis.
@@
 \end{tabular}
-\caption{$^a$in Millions *CITE*; $^b$USD *CITE*; $^c$ \degree C *CITE*}
+\caption{$^a$in Millions \cite{population}; $^b$USD \cite{gdp}; $^c$ \degree C \cite{weather}}
 \label{table:Milwaukee_H}
@@
 So, when considering the necessary team success score for Milwaukee, we will compare with these teams.
-
 \subsubsection*{Social Environment}
@@
 \end{enumerate}
-
+These cases act as a scaling on the success and location scores for a given team.
+Even if a team is wildly successful in the best possible location, if there is no fan base to interact with, allegiance will never begin to spread.
+\subsection*{Computation of Beta}
+\addcontentsline{toc}{subsection}{Computation of Beta}
+Now that we have defined each of the component variables of $\beta$, we can begin to compute it according to the equation from \cite{light},
+\begin{equation}\label{beta}
+\beta_t=ps_th_t
+\end{equation}
+So, $\beta$ is the product of a teams normalized success and location score, scaled by the social factor. It follows then, that we may write $\ro$ as,
+\begin{equation}\label{Ro}
+\ro = \frac{ps_th_tS}{\gamma} = 9ps_th_t
+\end{equation}
+Letting $S=1$ represent the proportion of the population infected, and $\gamma=\frac{1}{9}$months as noted before.
+Using this equation, we may compute the cutoff $\ro$ values for fan base growth for each of the above $p$ values in Table \ref{table:Ro}.
+As in \cite{light}, we see that for very successful teams, such as Chicago and Detroit, the reproductive rate is always greater than zero.
+As such, we we would expect these teams to have an expanding fan base almost all of the time, at least during the season itself.
+\begin{table}[H]
+\centerfloat
+\begin{tabular}{lrrr}
+\hline
+\multicolumn{4}{c}{$\ro$ score for each $p$ scaling} \\
+Team & $p=0.05$ & $p=0.25$ & $p=0.75$ \\ 
+\hline
+Anaheim Ducks & 0.57 & 2.83 & 8.48 \\ 
+Arizona Coyotes & 0.09 & 0.43 & 1.30 \\ 
+Boston Bruins & 0.74 & 3.71 & 11.13 \\ 
+Buffalo Sabres & 0.19 & 0.95 & 2.84 \\ 
+Calgary Flames & 0.19 & 0.94 & 2.82 \\ 
+Carolina Hurricanes & 0.38 & 1.88 & 5.63 \\ 
+Chicago Blackhawks & 1.33 & 6.64 & 19.93 \\ 
+Colorado Avalanche & 0.59 & 2.95 & 8.84 \\ 
+Columbus Blue Jackets & 0.09 & 0.43 & 1.29 \\ 
+Dallas Stars & 0.23 & 1.13 & 3.38 \\ 
+Detroit Red Wings & 1.19 & 5.97 & 17.90 \\ 
+Edmonton Oilers & 0.16 & 0.78 & 2.33 \\ 
+Florida Panthers & 0.03 & 0.14 & 0.41 \\ 
+LA Kings & 0.59 & 2.94 & 8.83 \\ 
+Minnesota Wild & 0.23 & 1.17 & 3.51 \\ 
+Montreal Canadians & 0.47 & 2.34 & 7.03 \\ 
+Nashville Predators & 0.24 & 1.21 & 3.63 \\ 
+New Jersey Devils & 0.69 & 3.45 & 10.36 \\ 
+NY Islanders & 0.15 & 0.75 & 2.25 \\ 
+NY Rangers & 0.53 & 2.67 & 8.01 \\ 
+Ottawa Senators & 0.45 & 2.27 & 6.82 \\ 
+Philly Flyers & 0.52 & 2.62 & 7.87 \\ 
+Pittsburgh Penguins & 1.34 & 6.70 & 20.11 \\ 
+San Jose Sharks & 0.27 & 1.35 & 4.06 \\ 
+St. Louis Blues & 0.98 & 4.89 & 14.66 \\ 
+Tampa Bay Lightning & 0.56 & 2.78 & 8.35 \\ 
+Toronto Maple Leafs & 0.27 & 1.33 & 3.98 \\ 
+Vancouver Canucks & 0.38 & 1.92 & 5.76 \\ 
+Washington Capitals & 0.64 & 3.22 & 9.67 \\ 
+Winnipeg Jets & 0.10 & 0.48 & 1.43 \\ 
+Las Vegas & 0.09 & 0.43 & 1.30 \\ 
+\hline
+\end{tabular}
+\caption{Values computed according to eqn. \ref{Ro}}
+\label{table:Ro}
+\end{table}
+\section*{Results}
+\addcontentsline{toc}{section}{Results}
+We shall now consider the viability of Milwaukee as a candidate for expansion based on the two cases described above; Milwaukee as an isolated team, and a consideration of Chicago's geographic adjacency.
+\begin{description}
+\item[Isolated Case:] For Milwaukee to be viable, a potential team would need a success rate similar to Boston($\ro > 1$ for $p=0.25,\ 0.75$), Edmonton($\ro > 1$ for $p=0.75$), and Winnipeg($\ro > 1$ for $p=0.75$).
+Based on the above analysis of $\ro$, we consider Table \ref{table:min_st} which contains the $s_t$ values required to have fan base growth for a given $p$ value,
+\begin{table}[H]
+\centerfloat
+\begin{tabular}{lrrr}
+\hline
+\multicolumn{4}{c}{$\min{s_t}$ for $\ro>1$} \\
+Team & $s_t,\ p=0.05$ & $s_t,\ p=0.25$ & $s_t,\ p=0.75$\\
+\hline
+Milwaukee & 2.224419 & 0.4448838 & 0.1482946\\\hline
+\end{tabular}
+\caption{Computed according to eqn. \ref{Ro}}
+\label{table:min_st}
+\end{table}
+Given Milwaukee's location quality, for $p=0.75$ a potential team would only need to make it to round three of a post season once in 18 years, or make the playoffs 7 times in the 18 years.
+In the $p=0.25$ case, Milwaukee would need to lose the Stanley Cup finals twice, or make it to the second round of the playoffs 5 times in 18 years.
+For the $p=0.05$ case, the cutoff is much more severe.
+A team would need 3 Stanley Cups and an additional finals loss in the next 18 years, or to advance to the third round 14 times over the next eighteen years.
+This is challenging for even a highly competitive team like Chicago or Pittsburgh.\\
+Estimating the success of a new NHL team is a challenging task.
+Much of the issue with determining potential success is an attempt to quantify how good a team will be upon their entry, given how the NHL draft system operates.
+In the past, many expansion teams have struggled initially due to the fact that many well established, talented players in the NHL are under long term contracts with existing teams, making it hard to fill a roster with experienced players.
+When the NHL expanded to include the Las Vegas Golden Knights in the 2017-2018 season, new drafting rules were agreed upon that allowed the team to draft experienced players from other teams, as well as a normal entry into the existing draft \cite{draft}.
+In their inaugural season, Las Vegas made it to the Stanley Cup finals, losing to Washington, showing that even new teams to the league could be competitive with this system.
+In addition to this, it is important to note that Milwaukee also has two unique advantages already.
+First, the existence of a semi-pro team, the Milwaukee Admirals, who have previously set attendance records.
+This shows an established hockey fan base in the area.
+Secondly, Milwaukee benefits from the fact that Wisconsin has produced more professional hockey players than any other state that lacks an NHL team\cite{wisco}.
+It is reasonable to assume that a team in Wisconsin would be quite popular across the entire state, as other professional sports teams in Wisconsin, the Packers (NFL), Brewers (MLB), and Bucks (NBA), all maintain large and committed fan bases across the state, including cities that are much closer geographically to rival teams (e.g.
+Menomonie).
+In addition to this state wide support, a constant stream of local talent could help to create a consistently high ranked team, even in the teams early years.\\
+Overall, it seems that ignoring the close location of Chicago leads to the conclusion that Milwaukee is a viable candidate for an expansion team.
+Given its proclivity to a higher $p$ value, the required team success rate for its location seems achievable, especially under the drafting rules used for the last expansion team.
+\item[Non-Isolated Case:] If we consider the fact that Chicago is $\sim 100$ miles away from Milwaukee, our results change.
+Given the success of the Blackhawks (See Table \ref{table:St}) over the last eighteen years, as well as our two team model (\ref{SIRMODEL}), it is reasonable to assume that Chicago already has large ``Infected" and ``Chronic" populations of fans.
+This fact reduces the size of the susceptible population available to a new team in Milwaukee, and would require more cross team switching to generate a large and stable fan base in Milwaukee.
+In addition to the lack of fan population available, we also note that Chicago's revenue in 2018 is one of the largest in the entire NHL (Table \ref{table:Revenue}).
+Given Chicago's success in the league, as well as how long it has been a member of the NHL, we assume that it has control of the net hockey revenue available in the region.
+Even if a team in Milwaukee was able to steal 30\% of that net income, it would only generate $\sim \$60$ million in revenue, which is significantly lower than even the lowest revenue teams in the league.
+As such, a team in Milwaukee would most likely struggle to find a financial foothold, as well as grow its fan base in an effective manner.
+Because of this, Milwaukee is probably not the optimal choice for a new expansion team.
+Based on the spatial distribution of existing NHL franchises, as well as what we know from eqn \ref{ht}, a better location for a new franchise might be in an area like northern Idaho or Montana.
+This location is isolated from existing teams, so revenue would not need to be shared as much, but maintains a colder climate, which, as our analysis shows is an important factor to consider.
+\end{description}
 \begin{thebibliography}{9}
@@
 \bibitem{jones}J. C. H. Jones and D. G. Ferguson, ``Location and Survival in the National Hockey League,” \textit{The Journal of Industrial Economics}, vol. 36, no. 4, p. 443, Jun. 1988.
+\bibitem{population} US Census Bureau and Data Integration Division, ``Population Estimates,” \textit{Metropolitan and Micropolitan Statistical Area Totals Dataset: Population and Estimated Components of Change: April 1, 2010 to July 1, 2014 - U.S Census Bureau}.
+[Online].
+\url{https://web.archive.org/web/20150504102404/http://www.census.gov/popest/data/metro/totals/2014/CBSA-EST2014-alldata.html}.
+[Accessed: 30-Sep-2019].
+\bibitem{gdp} ``Regional Economic Accounts GDP and Personal Income,” \textit{BEA}.
+[Online].
+\url{https://apps.bea.gov/itable/drilldown.cfm?reqid=70&stepnum=40&Major_Area=5&State=5&Area=XX&TableId=504&Statistic=1&Year=2014&YearBegin=-1&Year_End=-1&Unit_Of_Measure=Levels&Rank=1&Drill=1&nRange=5}.
+[Accessed: 28-Sep-2019].
+\bibitem{weather} ``Milwaukee Temperatures: Averages by Month,” \textit{Milwaukee WI Average Temperatures by Month - Current Results}.
+[Online].
+\url{https://www.currentresults.com/Weather/Wisconsin/Places/milwaukee-temperatures-by-month-average.php}.
+[Accessed: 30-Sep-2019].
+\bibitem{whynot} J.
+Hand, C.
+Jozwik, H.
+Magner, Z.
+Brooke, A.
+Landowski, A.
+Parquette, and E.
+Johnson, ``Why Milwaukee is Not an NHL City,” \textit{Milwaukee Magazine}, 16-Nov-2018.
+[Online].
+\url{https://www.milwaukeemag.com/milwaukee-not-nhl-city/}.
+[Accessed: 29-Sep-2019].
+\bibitem{draft} ``2017 NHL Expansion Draft,” \textit{Wikipedia}, 27-Apr-2019. [Online]. \url{https://en.wikipedia.org/wiki/2017_NHL_Expansion_Draft}. [Accessed: 29-Sep-2019].
+\bibitem{wisco} ``NHL Players Born in Wisconsin, United States,” \textit{Hockey}.
+[Online].
+\url{https://www.hockey-reference.com/friv/birthplaces.cgi?country=US&province&state=WI&fbclid=IwAR1vb6vzR95-DX0B_zRyV_gLxYcWMneos3Ppn8RBNsnHQqzA9d4sJj4X_aA}.
+[Accessed: 29-Sep-2019].
 \end{thebibliography}

### 2019-10-15 NHL/NHL.R

@@ -54,3 +54,7 @@ R_075 = Beta_75*9
 
 
 Reprod = data.frame("Team"=X$Team, "R_0 0.05"=R_005, "R_0 0.25"=R_025, "R_0 0.75"=R_075)
+
+##########Minscores #################################
+Mins_t <- data.frame("Team"="Milwaukee", "p=0.05"=1/(9*.05*h_mil), "p=0.25"=1/(9*.25*h_mil), "p=0.75"=1/(9*.75*h_mil))
+print(xtable(Mins_t, type="latex"), file="min.tex")

### 2019-10-22 Mayo/FirstRun/Worker.cpp
Worker implement 1

@@ -1,0 +1,61 @@
+#include "Worker.h"
+
+	Worker::Worker(){
+		isTech=false;
+		isIV=false;
+		isIdle=true;
+		idleTime=0;
+	}
+
+	Worker::Worker(bool tech, bool iv){
+		isTech=tech;
+		isIV=iv;
+		isIdle=true;
+		idleTime=0;
+	}
+
+	bool Worker::getTech(){
+		return isTech;
+	}
+
+	void Worker::setTech(bool tech){
+		isTech = tech;
+	}
+
+	bool Worker::getIV(){
+		return isIV;
+	}
+	void Worker::setIV(bool iv){
+		isIV=iv;
+	}
+	bool Worker::getIdle(){
+		return isIdle;
+	}
+	void Worker::setIdle(bool idle){
+		isIdle=idle;
+	}
+	double Worker::getIdleTime(){
+		return idleTime;
+	}
+	void Worker::updateIdleTime(double t){
+		idleTime+=t;
+	}
+	void Worker::setIdleTime(double t){
+		idleTime=t;
+	}
+	Script Worker::getCurrentScript(){
+		return currentScript;
+	}
+	void Worker::setCurrentScript(Script s){
+		currentScript=s;
+	}
+	void Worker::updateWorkTime(double t){
+		workTime += t;
+	}
+	double Worker::getWorkTime(){
+		return workTime;
+	}
+	void Worker::setWorkTime(double t){
+		workTime=t;
+	}
+

### 2019-10-22 Mayo/FirstRun/Worker.h

@@ -4,6 +4,8 @@
 #include <vector>
 #include <string>
 #include <queue>
+#include "Script.h"
+
 
 using namespace std;
 
@@ -16,5 +18,23 @@ class Worker{
 		void setTech(bool tech);
 		bool getIV();
 		void setIV(bool iv);
+		bool getIdle();
+		void setIdle(bool idle);
+		double getIdleTime();
+		void updateIdleTime(double t);
+		void setIdleTime(double t);
+		Script getCurrentScript();
+		void setCurrentScript(Script s);
+		void updateWorkTime(double t);
+		double getWorkTime();
+		void setWorkTime(double t);
+	private:
+		bool isTech;
+		bool isIV;
+		bool isIdle;
+		double idleTime;
+		double workTime;
+		//vector<bool> idleChecks;
+		Script currentScript;
 
 };

### 2019-10-22 Mayo/FirstRun/main.cpp

@@ -5,13 +5,21 @@
 #include <random>
 #include <string>
 #include <queue>
+#include <algorithm>
 #include "Script.h"
-
+#include "Worker.h"
 
 using namespace std;
 
 //Globals
 int numOrders;
+int tic;
+int nSteps;
+int nTrials;
+vector<Worker> idleWorkers;
+vector<Worker> activeWorkers;
+
+////Setup Queues
 queue<double> oralIncoming;
 queue<double> ivIncoming;
 queue<double> entryTimes;
@@ -20,7 +28,20 @@ queue<double> oralPrepTimes;
 queue<double> ivPrepTimes;
 queue<double> prepVerTimes;
 queue<double> dispenseTimes;
-
+////Process Queues
+queue<Script> entryQ;
+queue<Script> entryVerQ;
+queue<Script> oralFillQ;
+queue<Script> ivFillQ;
+queue<Script> fillVerQ;
+queue<Script> distQ;
+//////Queue Length Holder
+vector<int> entryQLengths;
+vector<int> entryVerQLengths;
+vector<int> oralFillQLengths;
+vector<int> ivFillQLengths;
+vector<int> fillVerQLengths;
+vector<int> distQLengths;
 
 //Funky Bois
 queue<double> getOralIncoming(int hours);
@@ -41,19 +62,35 @@ int main(){
 	int numT; //Number of Technicians
 	cout << "Please enter the duration of the simulation in hours:" <<  endl;
 	cin >> hrs;
+	cout << "Please enter the number of steps per minute:" << endl;
+	cin >> tic;
 	cout << "Please enter the number of Pharmacists in the simulation:" << endl;
 	cin >> numP;
 	cout << "Please enter the number of Technicians in the sumulation:" << endl;
 	cin >> numT;
-	cout << hrs << numP << numT << endl;
+
+	nSteps=tic*hrs*60;
+	
+	for(int i=1; i<=numP; i++){
+		idleWorkers.push_back(Worker(false, false));
+	}
+	for(int i=1; i<numT; i++){
+		idleWorkers.push_back(Worker(true, false));
+	}
+	idleWorkers.push_back(Worker(true, true));
+	for(int i=0; i<idleWorkers.size(); i++){
+		cout << "Is Tech: " << idleWorkers[i].getTech() << ", Is IV: " << idleWorkers[i].getIV() << endl;
+	}
+	cout << "***************************************" << endl;
[…]

### 2019-10-23 Mayo/FirstRun/main.cpp
First Buffer Up and running. 100hr w/ 1000 steps per min ~3.75 min with printing, .7s w/o print. dang.

@@ -1,5 +1,6 @@
 //Justin Hood 2019 Capstone Project
 
+#include <chrono>
 #include <iostream>
 #include <ctime>
 #include <random>
@@ -14,8 +15,10 @@ using namespace std;
 //Globals
 int numOrders;
 int tic;
+double toc;
 int nSteps;
 int nTrials;
+int step;
 vector<Worker> idleWorkers;
 vector<Worker> activeWorkers;
 
@@ -68,9 +71,14 @@ int main(){
 	cin >> numP;
 	cout << "Please enter the number of Technicians in the sumulation:" << endl;
 	cin >> numT;
-
-	nSteps=tic*hrs*60;
 	
+	chrono::steady_clock::time_point begin = chrono::steady_clock::now();
+	//Compute number of steps for full simulaiton based on tic and hour inputs
+	nSteps=tic*hrs*60;
+	toc = 1.0/tic;
+	cout << "toc: " << toc << endl;
+	
+	//Setup workers. For base case we have n pharmacists, and m techs with only one tech being an IV designated worker. Workers start in the Idle case, as no products are in the queues yet. Upon the arrival of the first script to the entry Q, the first worker in the shuffled vector will get a chance to do it.
 	for(int i=1; i<=numP; i++){
 		idleWorkers.push_back(Worker(false, false));
 	}
@@ -78,16 +86,10 @@ int main(){
 		idleWorkers.push_back(Worker(true, false));
 	}
 	idleWorkers.push_back(Worker(true, true));
-	for(int i=0; i<idleWorkers.size(); i++){
-		cout << "Is Tech: " << idleWorkers[i].getTech() << ", Is IV: " << idleWorkers[i].getIV() << endl;
-	}
-	cout << "***************************************" << endl;
+	//This shuffles the vector for fairness in the simulation.
 	random_shuffle(idleWorkers.begin(), idleWorkers.end());
-	for(int i=0; i<idleWorkers.size(); i++){
-		cout << "Is Tech: " << idleWorkers[i].getTech() <<     ", Is IV: " << idleWorkers[i].getIV() << endl;
-	}
 	
-	//Setup of our time buffers.
[…]

### 2019-10-24 Mayo/FirstRun/Worker.cpp
Started processing loop

@@ -58,4 +58,9 @@
 	void Worker::setWorkTime(double t){
 		workTime=t;
 	}
-
+	string Worker::getTask(){
+		return currentTask;
+	}
+	void Worker::setTask(string s){
+		currentTask = s;
+	}

### 2019-10-24 Mayo/FirstRun/Worker.h

@@ -28,6 +28,11 @@ class Worker{
 		void updateWorkTime(double t);
 		double getWorkTime();
 		void setWorkTime(double t);
+		string getTask();
+		void setTask(string s);
+
+
+
 	private:
 		bool isTech;
 		bool isIV;
@@ -36,5 +41,5 @@ class Worker{
 		double workTime;
 		//vector<bool> idleChecks;
 		Script currentScript;
-
+		string currentTask;
 };

### 2019-10-24 Mayo/FirstRun/main.cpp

@@ -21,6 +21,13 @@ int nTrials;
 int step;
 vector<Worker> idleWorkers;
 vector<Worker> activeWorkers;
+string entry = "Entry";
+string entryVer = "EntryVer";
+string fill = "Fill";
+string fillVer = "FillVer";
+string dispense = "Dispense";
+
+
 
 ////Setup Queues
 queue<double> oralIncoming;
@@ -306,20 +313,50 @@ int main(){
 			//pop the front off of Iv time
 			ivIncoming.pop();
 		}
-		/* Now that new orders have been entered into the first queue, */
-		/*cout << "Oral Head: " << oralIncoming.front() << ", Oral Size: " << oralIncoming.size() << endl;
-                cout << "IV Head: " << ivIncoming.front() << ", IV Size: " << ivIncoming.size()     << endl;
-                cout << "EntryQ size: " << entryQ.size() << endl;
-		cout << "*****************************************************" << endl;*/
+		/* Now that new orders have been entered into the first queue, we check all active tasks to see if the time step
+		 * finishes the task at hand*/
+		//Check Whole Vector
+		Script transition;
+		for(int i=0; i < activeWorkers.size(); i++){
+			//Check if task will finish
+			if(activeWorkers[i].getWorkTime()-toc <= 0){
+				//Push to relevant queue after completion.
+				switch(activeWorkers[i].getTask()){
+					case entry:
+						//Pull the script
+						transition = activeWorkers[i].getCurrentScript();
+						//Make Idle
+						activeWorkers[i].setIdle(true);
+						//Put in Idle Queue
+						idleWorkers.push_back(activeWorkers[i]);
+						//Push Script to ENTRYVER QUEUE
+						entryVerQ.push(transition);
+					case entryVer:
+						//Pull the script
+						transition = activeWorkers[i].getCurrentScript();
+						//Make Idle
+						activeWorkers[i].setIdle(true);
+						//Put in Idle Queue
+						idleWorkers.push_back(activeWorkers[i]);
+						//Push to appropriate fill queue
+						if(transition.getIV()){
+							ivFillQ.push(transition);
+						}else{
+							oralFillQ.push(transition);
+						}
+					case fill:
+						//Pull the Script
+						transition = activeWorkers[i].getCurrentScript();
+						//Make Idle
+						activeWorkers[i]/s
+				}		
+			}
 		
-		
+		}	
+
+		//Increment the loop
 		step+=1;
 	}
[…]

### 2019-10-25 Mayo/FirstRun/Script.cpp
Working???

@@ -81,4 +81,9 @@
 	void Script::setInQueue(bool b){
 		inQueue=b;
 	}
-
+	int Script::getOrderNum(){
+		return orderNumber;
+	}
+	void Script::setOrderNum(int i){
+		orderNumber=i;
+	}

### 2019-10-25 Mayo/FirstRun/Script.h

@@ -33,7 +33,8 @@ class Script{
 		void setWaitTime(double t);
 		bool getInQueue();
 		void setInQueue(bool b);
-
+		int getOrderNum();
+		void setOrderNum(int i);
 
 	private:
 		//gimme the deets
@@ -46,5 +47,6 @@ class Script{
 		double totalTime;
 		double waitTime;
 		bool inQueue;
+		int orderNumber;
 };
 

### 2019-10-25 Mayo/FirstRun/Worker.cpp

@@ -50,7 +50,7 @@
 		currentScript=s;
 	}
 	void Worker::updateWorkTime(double t){
-		workTime += t;
+		workTime -= t;
 	}
 	double Worker::getWorkTime(){
 		return workTime;

### 2019-10-25 Mayo/FirstRun/main.cpp

@@ -7,6 +7,7 @@
 #include <string>
 #include <queue>
 #include <algorithm>
+#include <map>
 #include "Script.h"
 #include "Worker.h"
 
@@ -21,12 +22,13 @@ int nTrials;
 int step;
 vector<Worker> idleWorkers;
 vector<Worker> activeWorkers;
-string entry = "Entry";
+int orderNum;
+/*string entry = "Entry";
 string entryVer = "EntryVer";
 string fill = "Fill";
 string fillVer = "FillVer";
 string dispense = "Dispense";
-
+*/
 
 
 ////Setup Queues
@@ -44,14 +46,15 @@ queue<Script> entryVerQ;
 queue<Script> oralFillQ;
 queue<Script> ivFillQ;
 queue<Script> fillVerQ;
-queue<Script> distQ;
+queue<Script> dispQ;
+queue<Script> endQ;
 //////Queue Length Holder
 vector<int> entryQLengths;
 vector<int> entryVerQLengths;
 vector<int> oralFillQLengths;
 vector<int> ivFillQLengths;
 vector<int> fillVerQLengths;
-vector<int> distQLengths;
+vector<int> dispQLengths;
 
 //Funky Bois
 queue<double> getOralIncoming(int hours);
@@ -65,7 +68,7 @@ queue<double> getDispenseTimes(int num);
 
 int main(){
 	//srand(1);
-
+	orderNum=1;
 	//Get the user input to the simulation here.
 	int hrs; //Duration of Sim in hours
 	int numP; //Number of Pharmacists
@@ -107,6 +110,8 @@ int main(){
 	prepVerTimes = getPrepVerTimes(numOrders);
 	dispenseTimes = getDispenseTimes(numOrders);
 	
+	cout << "Oral Incoming + IV incoming=" << numOrders << endl;
+	cout << "***************************" << endl;
 	//main loop. oh boy
 	step=0;
 	Script nextOral = Script(false);
@@ -134,9 +139,12 @@ int main(){
 				//Dispense Times
 				nextOral.setDispTime(dispenseTimes.front());
 				dispenseTimes.pop();
-				//Set wait time to zero and inQ. Push to entry Queue.
+				//Set wait time to zero and inQ.
 				nextOral.setWaitTime(0);
 				nextOral.setInQueue(true);
+				//Set order number and push to queue
+				nextOral.setOrderNum(orderNum);
+				orderNum+=1;
 				entryQ.push(nextOral);
[…]

### 2019-10-25 Mayo/1stUpdate/update1.tex
Added print outs. Need to modify code to avoid copies of the workers from spooling up.

\documentclass[letterpaper,10pt]{article}
\usepackage[top=2cm, bottom=1.5cm, left=1cm, right=1cm]{geometry}
\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\today}
\chead{MSCS 791 Status Update 1}
\rhead{Justin Hood}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newtheorem{lem}{Lemma}
\begin{document}
After working on the Mayo project for about two weeks, I have accomplished a few milestones for implementation, the main ones being,
\begin{enumerate}
\item Computation of distribution estimations of the given time data.
\item Decision to implement my own discrete event modeler custom built to this model.
\end{enumerate}
In regards to the first milestone, my results follow in tabular form,
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Data & Distribution & Parameters\\\hline
Order Entry Times & Normal & $\mu=9.873784,\ \sigma=2.095579$\\\hline
Entry Verification Times & Uniform & min=$1.2726$, max=$3.4059$\\\hline
Oral Drug Preparation Time & log-normal & $\mu=2.99140489,\ \sigma=0.06300657$\\\hline
IV Drug Preparation Time & Weibull & shape=$2.362195$, scale=$6.359247$\\\hline
Order Preparation Verification Time & Weibull & shape=$2.911269$, scale=$2.143830$\\\hline
Dispensing Time & Normal & $\mu=2.947898,\ \sigma=0.566620$\\\hline
Oral Drug Incoming Time & Exponential & $\lambda=0.129199$\\\hline
IV Drug Incoming Time & Exponential & $\lambda=0.05988024$\\\hline
\end{tabular}
\end{center}
These distributions were chosen based on the computation of the AIC for a number of distributions applied to the data, based on a Cullen and Frey graph. In addition to the Cullen and Frey graph, I also have histograms of the data sets for fit verification.\\\\
In regards to the second milestone, I have had some success at the implementation, though my simulation is not fully running due to an issue with the compiler that took me several days to resolve. As it stands, I am currently finishing implementing the random choice logic for the idle workers to choose a new task if any are available. I expect that I will have this working by the beginning of next week, so with any luck my timeline itself will not change by too much.\\
This being said, I have run a few benchmarks on my program, and it runs quite quickly as is. I am able to run six million steps of simulation in under 30 seconds, which is dramatically more than the 12 hour simulation will require. This is good news for the analysis of the confidence intervals, as I will be able to acquire more data points to increase the accuracy of the calculations.\\\\
As it stands, we have communicated several times regarding my questions on the implementation, so I do not have any new questions for the time being in this category. I do however have a question regarding the base simulation confidence intervals. Have you implemented the model, or do you have an estimation of what the intervals should be? I only ask because I was hoping you could tell me if my intervals were in the correct ballpark, so that I do not base the entire analysis on a faulty model implementation.\\\\
I am hoping that my timeline through the next status report should remain the same, with both the base case and the optimizations at least mostly implemented and data collected. I am sure that I will be in email contact with you throughout with any questions that arise, so I should be able to remain on track with the timeline in this regard as well.
\end{document}

### 2019-10-25 Mayo/FirstRun/main.cpp

@@ -8,8 +8,11 @@
 #include <queue>
 #include <algorithm>
 #include <map>
+#include <fstream>
 #include "Script.h"
 #include "Worker.h"
+
+
 
 using namespace std;
 
@@ -23,12 +26,6 @@ int step;
 vector<Worker> idleWorkers;
 vector<Worker> activeWorkers;
 int orderNum;
-/*string entry = "Entry";
-string entryVer = "EntryVer";
-string fill = "Fill";
-string fillVer = "FillVer";
-string dispense = "Dispense";
-*/
 
 
 ////Setup Queues
@@ -88,6 +85,27 @@ int main(){
 	toc = 1.0/tic;
 	cout << "toc: " << toc << endl;
 	
+	//Setup output files
+	ofstream oInOut;
+	oInOut.open("OralIncomingCounts.txt");
+	ofstream iInOut;
+	iInOut.open("IVIncomingCounts.txt");
+	ofstream entryOut;
+	entryOut.open("entryQueueCounts.txt");
+	ofstream entryVerOut;
+	entryVerOut.open("entryVerQueueCounts.txt");
+	ofstream oralFillOut;
+	oralFillOut.open("oralFillQueueCounts.txt");
+	ofstream ivFillOut;
+	ivFillOut.open("ivFillQueueCounts.txt");
+	ofstream fillVerOut;
+	fillVerOut.open("fillVerQueueCounts.txt");
+	ofstream dispOut;
+	dispOut.open("dispQueueCounts.txt");
+	ofstream endOut;
+	endOut.open("endQueueCounts.txt");
+	
+	
 	//Setup workers. For base case we have n pharmacists, and m techs with only one tech being an IV designated worker. Workers start in the Idle case, as no products are in the queues yet. Upon the arrival of the first script to the entry Q, the first worker in the shuffled vector will get a chance to do it.
 	for(int i=1; i<=numP; i++){
 		idleWorkers.push_back(Worker(false, false));
@@ -110,6 +128,11 @@ int main(){
 	prepVerTimes = getPrepVerTimes(numOrders);
 	dispenseTimes = getDispenseTimes(numOrders);
 	
+	oInOut << oralIncoming.size();
+	oInOut.close();
+	iInOut << ivIncoming.size();
+	iInOut.close();
+
 	cout << "Oral Incoming + IV incoming=" << numOrders << endl;
 	cout << "***************************" << endl;
 	//main loop. oh boy
[…]

### 2019-11-12 Mayo/FirstRun/main.cpp
Fixed the infinite workers boiiiiii. Starting to set up the multiple loop and the queue stat outputs.

@@ -64,7 +64,6 @@ queue<double> getPrepVerTimes(int num);
 queue<double> getDispenseTimes(int num);
 
 int main(){
-	//srand(1);
 	orderNum=1;
 	//Get the user input to the simulation here.
 	int hrs; //Duration of Sim in hours
@@ -379,20 +378,15 @@ int main(){
 		 * finishes the task at hand*/
 		//Check Whole Vector
 		Script transition;
-		vector<int> indexes;
 		for(int i=0; i < activeWorkers.size(); i++){
 			//Check if task will finish
 			if(activeWorkers[i].getWorkTime()-toc <= 0){
-				//Note the index of a newly idled worker
-				indexes.push_back(i);
 				//Push to relevant queue after completion.
 				if(activeWorkers[i].getTask()=="Entry"){
 					//Pull the script
                                         transition = activeWorkers[i].getCurrentScript();
                                         //Make Idle
                                         activeWorkers[i].setIdle(true);
-                                        //Put in Idle Queue
-                                        idleWorkers.push_back(activeWorkers[i]);
                                         //Push Script to ENTRYVER QUEUE
                                         entryVerQ.push(transition);
 				}else if(activeWorkers[i].getTask()=="EntryVer"){
@@ -400,8 +394,6 @@ int main(){
 					transition = activeWorkers[i].getCurrentScript();
 					//Make Idle
 					activeWorkers[i].setIdle(true);
-					//Put in Idle Queue
-					idleWorkers.push_back(activeWorkers[i]);
 					//Push to appropriate fill queue
 					if(transition.getIV()){
 						ivFillQ.push(transition);
@@ -413,8 +405,6 @@ int main(){
 					transition = activeWorkers[i].getCurrentScript();
 					//Make Idle
 					activeWorkers[i].setIdle(true);
-					//Put in Idle Queue
-					idleWorkers.push_back(activeWorkers[i]);
 					//Push to the Verification Queue
 					fillVerQ.push(transition);
 
@@ -423,8 +413,6 @@ int main(){
 					transition = activeWorkers[i].getCurrentScript();
 					//Make Idle
 					activeWorkers[i].setIdle(true);
-					//Put in Idle Queue
[…]

### 2019-11-12 Mayo/FirstRun/Worker.cpp
Think we figured out that stinky segfault mother fucker

@@ -62,5 +62,7 @@
 		return currentTask;
 	}
 	void Worker::setTask(string s){
-		currentTask = s;
+		if(currentTask != s){
+			currentTask = s;
+		}
 	}

### 2019-11-12 Mayo/FirstRun/main.cpp

@@ -468,26 +468,26 @@ int main(){
 					if(myVec.size()==0){
 						myVec.push_back("NONE");
 					}
-					int i = rand()%myVec.size();
-					if(myVec[i]=="Entry"){
+					int myRand = rand()%myVec.size();
+					if(myVec[myRand]=="Entry"){
 						idleWorkers[i].setIdle(false);
 						idleWorkers[i].setCurrentScript(entryQ.front());
 						idleWorkers[i].setWorkTime(entryQ.front().getEntryTime());
 						idleWorkers[i].setTask("Entry");
 						entryQ.pop();
-					}else if(myVec[i]=="Fill"){
+					}else if(myVec[myRand]=="Fill"){
 						idleWorkers[i].setIdle(false);
 						idleWorkers[i].setCurrentScript(oralFillQ.front());
 						idleWorkers[i].setWorkTime(oralFillQ.front().getFillTime());
 						idleWorkers[i].setTask("Fill");
 						oralFillQ.pop();
-					}else if(myVec[i]=="Dispense"){
+					}else if(myVec[myRand]=="Dispense"){
 						idleWorkers[i].setIdle(false);
 						idleWorkers[i].setCurrentScript(dispQ.front());
 						idleWorkers[i].setWorkTime(dispQ.front().getDispTime());
 						idleWorkers[i].setTask("Dispense");
 						dispQ.pop();
-					}else if(myVec[i]=="NONE"){
+					}else if(myVec[myRand]=="NONE"){
 						//None are empty, do nothing.
 					}
 				}
@@ -514,38 +514,38 @@ int main(){
 				if(myVec.size()==0){
 					myVec.push_back("NONE");
 				}
-				int i = rand()%myVec.size();
-				if(myVec[i]=="Entry"){
+				int myRand = rand()%myVec.size();
+				if(myVec[myRand]=="Entry"){
 					idleWorkers[i].setIdle(false);
 					idleWorkers[i].setCurrentScript(entryQ.front());
 					idleWorkers[i].setWorkTime(entryQ.front().getEntryTime());
 					idleWorkers[i].setTask("Entry");
 					entryQ.pop();
-				}else if(myVec[i]=="EntryVer"){
+				}else if(myVec[myRand]=="EntryVer"){
 					idleWorkers[i].setIdle(false);
 					idleWorkers[i].setCurrentScript(entryVerQ.front());
[…]

### 2019-11-13 Mayo/FirstRun/main.cpp
For loop implemented

@@ -46,12 +46,12 @@ queue<Script> fillVerQ;
 queue<Script> dispQ;
 queue<Script> endQ;
 //////Queue Length Holder
-vector<int> entryQLengths;
+/*vector<int> entryQLengths;
 vector<int> entryVerQLengths;
 vector<int> oralFillQLengths;
 vector<int> ivFillQLengths;
 vector<int> fillVerQLengths;
-vector<int> dispQLengths;
+vector<int> dispQLengths;*/
 
 //Funky Bois
 queue<double> getOralIncoming(int hours);
@@ -69,6 +69,7 @@ int main(){
 	int hrs; //Duration of Sim in hours
 	int numP; //Number of Pharmacists
 	int numT; //Number of Technicians
+	int numSim; //Number of simulations to run
 	cout << "Please enter the duration of the simulation in hours:" <<  endl;
 	cin >> hrs;
 	cout << "Please enter the number of steps per minute:" << endl;
@@ -77,6 +78,8 @@ int main(){
 	cin >> numP;
 	cout << "Please enter the number of Technicians in the sumulation:" << endl;
 	cin >> numT;
+	cout << "Please enter the number of times to run the simulation:" << endl;
+	cin >> numSim;
 	
 	chrono::steady_clock::time_point begin = chrono::steady_clock::now();
 	//Compute number of steps for full simulaiton based on tic and hour inputs
@@ -105,63 +108,227 @@ int main(){
 	endOut.open("endQueueCounts.txt");
 	
 	
-	//Setup workers. For base case we have n pharmacists, and m techs with only one tech being an IV designated worker. Workers start in the Idle case, as no products are in the queues yet. Upon the arrival of the first script to the entry Q, the first worker in the shuffled vector will get a chance to do it.
-	for(int i=1; i<=numP; i++){
-		idleWorkers.push_back(Worker(false, false));
-	}
-	for(int i=1; i<numT; i++){
-		idleWorkers.push_back(Worker(true, false));
-	}
-	idleWorkers.push_back(Worker(true, true));
-	//This shuffles the vector for fairness in the simulation.
-	random_shuffle(idleWorkers.begin(), idleWorkers.end());
-	
+	for(int simCount=0; simCount<numSim; simCount++){
 
-	//Look at idle times
-	cout << "Active idles" << endl;
-	for(int i=0; i< activeWorkers.size(); i++){
[…]

### 2019-11-13 Mayo/FirstRun/main.cpp
Oral and IV incoming counts output

@@ -147,10 +147,8 @@ int main(){
 		prepVerTimes = getPrepVerTimes(numOrders);
 		dispenseTimes = getDispenseTimes(numOrders);
 		
-		oInOut << oralIncoming.size();
-		oInOut.close();
-		iInOut << ivIncoming.size();
-		iInOut.close();
+		oInOut << oralIncoming.size() << endl;
+		iInOut << ivIncoming.size() << endl;
 
 		cout << "Oral Incoming + IV incoming=" << numOrders << endl;
 		cout << "***************************" << endl;
@@ -630,7 +628,9 @@ int main(){
 	ivFillOut.close();
 	fillVerOut.close();
 	dispOut.close();
-	endOut.close(); 
+	endOut.close();
+	oInOut.close();
+	iInOut.close();
 
 
 	chrono::steady_clock::time_point end = chrono::steady_clock::now();

### 2019-11-13 Mayo/FirstRun/main.cpp
Average number processed, average queue lengths, and utilization working. Next is the wait times.

@@ -106,7 +106,16 @@ int main(){
 	dispOut.open("dispQueueCounts.txt");
 	ofstream endOut;
 	endOut.open("endQueueCounts.txt");
-	
+	ofstream oralFilled;
+	oralFilled.open("oralFilled.txt");
+	ofstream ivFilled;
+	ivFilled.open("ivFilled.txt");
+	ofstream pharmIdle;
+	pharmIdle.open("pharmIdle.txt");
+	ofstream techIdle;
+	techIdle.open("techIdle.txt");
+	ofstream ivTechIdle;
+	ivTechIdle.open("ivTechIdle.txt");	
 	
 	for(int simCount=0; simCount<numSim; simCount++){
 
@@ -601,6 +610,53 @@ int main(){
 		endOut << endl;
 		
 		
+
+		//Lets go through the end Queue to see what kind everything was and note that!
+		int ivCount=0;
+		int oralCount=0;
+		while(!endQ.empty()){
+			if(endQ.front().getIV()){
+				ivCount+=1;
+			}else{
+				oralCount+=1;
+			}
+			endQ.pop();
+		}
+		oralFilled << oralCount << endl;
+		ivFilled << ivCount << endl;
+		
+		//Now lets look at our worker idle Times
+		for(int i=0; i<idleWorkers.size(); i++){
+			if(!idleWorkers[i].getTech()){
+				pharmIdle << idleWorkers[i].getIdleTime() << ",";
+			}else{
+				if(idleWorkers[i].getIV()){
+					ivTechIdle << idleWorkers[i].getIdleTime() << ",";
+				}else{
+					techIdle << idleWorkers[i].getIdleTime() << ",";
+				}
+			}
+		}
+		for(int i=0; i<activeWorkers.size(); i++){
+			if(!activeWorkers[i].getTech()){
+				pharmIdle << activeWorkers[i].getIdleTime() << ",";
+			}else{
+				if(activeWorkers[i].getIV()){
+					ivTechIdle << activeWorkers[i].getIdleTime() << ",";
+				}else{
+					techIdle << activeWorkers[i].getIdleTime() << ",";
+				}
+			}
+		}
+		//Add a new Line to each
+		pharmIdle << endl;
+		techIdle << endl;
+		ivTechIdle << endl;
+
+
+
+
+
 		idleWorkers.clear();
 		activeWorkers.clear();
 
@@ -631,6 +687,11 @@ int main(){
 	endOut.close();
[…]

### 2019-11-14 Mayo/FirstRun/CI.R
Confidence intervals for all but the throughput times. ugh.

@@ -1,0 +1,142 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/FirstRun")
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
+X <- read.csv("entryVerQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryVerQ <- colMeans(X)
+mu=mean(entryVerQ)
+s=sd(entryVerQ)
+delta <- zstar*s/sqrt(length(entryVerQ))
+(lowerEntryVerQ<- mu-delta)
+(upperEntryVerQ<- mu+delta)
+
+##### Oral Fill Queue Lengths
+X <- read.csv("oralFillQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+oralFillQ <- colMeans(X)
+mu=mean(oralFillQ)
+s=sd(oralFillQ)
+delta <- zstar*s/sqrt(length(oralFillQ))
+(lowerOralFillQ<- mu-delta)
+(upperOralFillQ<- mu+delta)
+
+##### IV Fill Queue Lengths
+X <- read.csv("ivFillQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
[…]

### 2019-11-14 Mayo/FirstRun/main.cpp

@@ -132,14 +132,14 @@ int main(){
 		
 
 		//Look at idle times
-		cout << "Active idles" << endl;
+		/*cout << "Active idles" << endl;
 		for(int i=0; i< activeWorkers.size(); i++){
 			cout << "Idle time (s): " << activeWorkers[i].getIdleTime() << endl;
 		}
 		cout << "Idle idles" << endl;
 		for(int i=0; i<idleWorkers.size(); i++){
 			cout << "Idle time (s): " << idleWorkers[i].getIdleTime() << endl;
-		}
+		}*/
 
 
 
@@ -159,8 +159,8 @@ int main(){
 		oInOut << oralIncoming.size() << endl;
 		iInOut << ivIncoming.size() << endl;
 
-		cout << "Oral Incoming + IV incoming=" << numOrders << endl;
-		cout << "***************************" << endl;
+		/*cout << "Oral Incoming + IV incoming=" << numOrders << endl;
+		cout << "***************************" << endl;*/
 		//main loop. oh boy
 		step=0;
 		Script nextOral = Script(false);
@@ -588,7 +588,7 @@ int main(){
 			step+=1;
 		}
 		//Now that the logic is a flowin, lets print some test shit. 
-		cout << "endQ size=" << endQ.size() << endl;
+		/*cout << "endQ size=" << endQ.size() << endl;
 		cout << "Please God" << endl;
 	
 		//Look at idle times
@@ -599,7 +599,7 @@ int main(){
 		cout << "Idle idles" << endl;
 		for(int i=0; i<idleWorkers.size(); i++){
 			cout << "Idle time (s): " << idleWorkers[i].getIdleTime() << endl;
-		}				
+		}*/				
 		//Add an extra blank to the data
 		entryOut << endl;
 		entryVerOut << endl;

### 2019-11-14 Mayo/FirstRun/CI.R
Throughputs working, yay

@@ -140,3 +140,29 @@ s=sd(ivTechIdle)/duration*100
 delta <- zstar*s/sqrt(length(ivTechIdle))
 (lowerIVTechIdle<- mu-delta)
 (upperIVTechIdle<- mu+delta)
+
+### Oral Throughput Times
+no_col <- max(count.fields("oralTotals.txt", sep = ","))
+X <- read.table("oralTotals.txt" ,sep=",",fill=TRUE,header = F,col.names=c("chr", "start", "end", "length",1:no_col))
+X <- t(X)
+oralThrough <- colMeans(X, na.rm=TRUE)
+#Convert from steps to minutes
+oralThrough <- oralThrough*toc
+mu=mean(oralThrough)
+s=sd(oralThrough)
+delta <- zstar*s/sqrt(length(oralThrough))
+(lowerOralThrough<- mu-delta)
+(upperOralThrough<- mu+delta)
+
+### IV Throughput Times
+no_col <- max(count.fields("ivTotals.txt", sep = ","))
+X <- read.table("ivTotals.txt" ,sep=",",fill=TRUE,header = F,col.names=c("chr", "start", "end", "length",1:no_col))
+X <- t(X)
+ivThrough <- colMeans(X, na.rm=TRUE)
+#Convert from steps to minutes
+ivThrough <- ivThrough*toc
+mu=mean(ivThrough)
+s=sd(ivThrough)
+delta <- zstar*s/sqrt(length(ivThrough))
+(lowerIVThrough<- mu-delta)
+(upperIVThrough<- mu+delta)

### 2019-11-14 Mayo/FirstRun/Script.cpp

@@ -87,3 +87,12 @@
 	void Script::setOrderNum(int i){
 		orderNumber=i;
 	}
+	double Script::getTotalTime(){
+		return totalTime;
+	}
+	void Script::setTotalTime(double d){
+		totalTime=d;
+	}
+	void Script::updateTotalTime(double d){
+		totalTime=d-totalTime;
+	}

### 2019-11-14 Mayo/FirstRun/Script.h

@@ -35,6 +35,9 @@ class Script{
 		void setInQueue(bool b);
 		int getOrderNum();
 		void setOrderNum(int i);
+		double getTotalTime();
+		void setTotalTime(double d);
+		void updateTotalTime(double d);
 
 	private:
 		//gimme the deets

### 2019-11-14 Mayo/FirstRun/main.cpp

@@ -116,7 +116,14 @@ int main(){
 	techIdle.open("techIdle.txt");
 	ofstream ivTechIdle;
 	ivTechIdle.open("ivTechIdle.txt");	
-	
+	ofstream oralTotals;
+	oralTotals.open("oralTotals.txt");
+	ofstream ivTotals;
+	ivTotals.open("ivTotals.txt");
+
+
+
+
 	for(int simCount=0; simCount<numSim; simCount++){
 
 		//Setup workers. For base case we have n pharmacists, and m techs with only one tech being an IV designated worker. Workers start in the Idle case, as no products are in the queues yet. Upon the arrival of the first script to the entry Q, the first worker in the shuffled vector will get a chance to do it.
@@ -174,6 +181,8 @@ int main(){
 			if(oralIncoming.size() > 0 && ivIncoming.size() > 0){
 				//First Case, oral enters, but iv does not.
 				if(oralIncoming.front()-toc <=0 && ivIncoming.front()-toc >0){
+					//Start the total timer.
+					nextOral.setTotalTime(step);
 					//Entry Time
 					nextOral.setEntryTime(entryTimes.front());
 					entryTimes.pop();
@@ -201,6 +210,8 @@ int main(){
 					ivIncoming.front()-=toc;
 					oralIncoming.pop();
 				}else if(oralIncoming.front()-toc >0 && ivIncoming.front()-toc <= 0){
+					//Start the total timer.
+					nextIV.setTotalTime(step);
 					//Entry Time
 					nextIV.setEntryTime(entryTimes.front());
 					entryTimes.pop();
@@ -230,6 +241,8 @@ int main(){
 					//Case where oral is first, prioritize oral on tie(if possible)
 					if(oralIncoming.front()-toc >= ivIncoming.front()){
 						//OralTYME
+						//Start the total timer.
+						nextOral.setTotalTime(step);
 						//Entry Time
 						nextOral.setEntryTime(entryTimes.front());
 						entryTimes.pop();
@@ -255,6 +268,8 @@ int main(){
 						oralIncoming.pop();
 
 						//IVTYME
+						//Start the total timer.
+						nextIV.setTotalTime(step);
 						//Entry Time
 						nextIV.setEntryTime(entryTimes.front());
 						entryTimes.pop();
@@ -281,6 +296,8 @@ int main(){
 
 					}else{
 						//IVTYME
+						//Start the total timer.
[…]

### 2019-11-14 Mayo/FirstRun/CI.R
Finished up the R through Throughput and pictures

@@ -2,6 +2,7 @@ setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/FirstRun")
 rm(list = ls())
 zstar <- qnorm(.975)
 duration <- 12*60
+toc <- 0.25
 
 ##### Oral Incoming Stats
 X <- read.csv("OralIncomingCounts.txt", header = FALSE)
@@ -20,6 +21,21 @@ s=sd(ivIn)
 delta <- zstar*s/sqrt(length(ivIn))
 (lowerIVIn<- mu-delta)
 (upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
 
 ##### Entry Queue Lengths
 X <- read.csv("entryQueueCounts.txt", header = FALSE)
@@ -87,6 +103,21 @@ delta <- zstar*s/sqrt(length(dispQ))
 (lowerDispQ<- mu-delta)
 (upperDispQ<- mu+delta)
 
+
+### Queue Length intervals:
+df <- data.frame(x=c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"), L=c(lowerEntryQ,lowerEntryVerQ, lowerOralFillQ, lowerIVFillQ, lowerFillVerQ, lowerDispQ), C=c(mean(entryQ), mean(entryVerQ), mean(oralFillQ), mean(ivFillQ),mean(fillVerQ), mean(dispQ)), U=c(upperEntryQ, upperEntryVerQ, upperOralFillQ, upperIVFillQ, upperFillVerQ, upperDispQ))
+p <- ggplot(df, aes(x = x, y = C)) +
[…]

### 2019-11-14 Mayo/FirstRun/progress2.tex
Running through throughput, and progress 2 tex

\documentclass[letterpaper,10pt]{article}
\usepackage[top=2cm, bottom=1.5cm, left=1cm, right=1cm]{geometry}
\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}

\lhead{\today}
\chead{MSCS 791 Progress Report 2}
\rhead{Justin Hood}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newtheorem{lem}{Lemma}

\begin{document}
Over the last few weeks I have gotten a large amount accomplished, with no small amount of setbacks. In summary,
\begin{itemize}
\item I have built my discrete event modeler in C++
\item I have resolved several issues in the logic of the code that included issues with:
\begin{itemize}
\item Number of Workers not remaining constant
\item Worker job assignments not sticking
\item Script throughput time causing cascading issues throughout the code as Segfaults and memory access crashes.
\end{itemize}
\item Setup the R framework to analyze the results of my output data (Cleaning up my csv files and some plots- see below)
\item Setup the C++ framework for several potential optimizations. Not run yet, as I am waiting to see what you think of the results for my base case.
\end{itemize}
As of now, my current simulation parameters are,
\begin{itemize}
\item Number of Hours: 12
\item Number of Updates per Minute: 4 (Every 15 seconds)
\item Number of Pharmacists: 2
\item Number of Techs: 5 (4 Normal and 1 IV)
\item Number of Trials: 30
\end{itemize}
I chose the 30 trials as it is sufficient for CLT assumptions of normality, and I wanted to keep the number of trials limited, as increased numbers of trials rely too heavily on our assumed parameters for the sampling distribution, and does not provide particularly interesting results. Running my model with the above parameters, I obtain the following 95 \% intervals:
\begin{align*}
\text{Oral Incoming} &= [91.69264,\ 97.70736] && \text{Number of Orders}\\
\text{IV Incoming} &= [41.48018,\ 46.11982] && \text{Number of Orders}\\\\
\text{Entry Queue} &= [0.3995144,\ 0.5428235] && \text{Number of Orders}\\
\text{Entry Verification Queue} &= [7.356473,\ 11.06084] && \text{Number of Orders}\\
\text{Oral Fill Queue} &= [0.1261225,\ 0.1614932] && \text{Number of Orders}\\
\text{IV Fill Queue} &= [0.0566676,\ 0.08567036] && \text{Number of Orders}\\
\text{Fill Verification Queue} &= [3.918231,\ 6.045171] && \text{Number of Orders}\\
\text{Dispense Queue} &= [0.2207893,\ 0.2724746] && \text{Number of Orders}\\\\
\text{Oral Filled} &= [67.55312,\ 70.91354] && \text{Number of Orders}\\
\text{IV Filled} &= [30.55001,\ 34.78332] && \text{Number of Orders}\\\\
\text{Pharmacist Idle Time} &= [3.350241,\ 4.793278] && \text{Percent of Total Time}\\
\text{Technician Idle Time} &= [17.70447,\ 20.13233] && \text{Percent of Total Time}\\
\text{IV Technician Idle Time} &= [69.77078,\ 73.3357] && \text{Percent of Total Time}\\\\
\text{Oral Throughput Times} &= [104.115,\ 130.0625] && \text{Minutes}\\
\text{IV Throughput Times} &= [88.9775,\ 118.2537] && \text{Minutes}\\\\
\end{align*}
These are displayed graphically below,
\begin{center}
\includegraphics[scale=.5]{IncomingCIs.png}
\includegraphics[scale=.5]{QueueCIs.png}\\
\includegraphics[scale=.5]{FilledCIs.png}
\includegraphics[scale=.5]{IdleCIs.png}\\
\includegraphics[scale=.5]{ThroughputCIs.png}
\end{center}
While it is clear from the numerical results, the graphs make it very clear that the main bunching points of the process flow are the verification steps. This is to be expected, as in our base model the pharmacists do not prioritize these orders in the workflow, instead, they only account for 40\% of the potential tasks they perform.\\\\
I am slightly behind my proposed timeline, but this is mainly due to the issues that I hope I have resolved. As I stated before, running the confidence analysis on my theorized optimizations should take under 5 minutes, as it is merely a matter of executing the code that I have already written, which I will do once I have the OK from you on my base case.\\\\
I have some questions on how I might be able to quantify improving the process, but I will save these until I reach that point in the process.\\\\
Assuming that my analysis for the base case looks good, I will run my optimizations and discuss with you what improvements I think are best, and then begin the rough draft of my project.\\\\\\
Note: I am sorry for the ``Radio Silence" from your last email. I updated my phone, and it logged me out of my school email account, so I did not see your email last week.
\end{document}

### 2019-11-14 Mayo/FirstRun/CI.R

@@ -142,7 +142,7 @@ p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
   geom_errorbar(aes(ymax = U, ymin = L))
 p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
-png("FilledCIs")
+png("FilledCIs.png")
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
   geom_errorbar(aes(ymax = U, ymin = L))

### 2019-12-01 Mayo/Priority Comparisons/ANOVA on Base Case.R
Started ANOVA

@@ -18,31 +18,31 @@ smart <- X[,1]
 
 treat <- rep("base", times=length(base))
 df <- data.frame(base, treat)
-names(df) <- c("Oral Throughput", "Treatment")
+names(df) <- c("OralThroughput", "Treatment")
 anovaDat <- df
 treat <- rep("prof", times=length(prof))
 df <- data.frame(prof, treat)
-names(df) <- c("Oral Throughput", "Treatment")
+names(df) <- c("OralThroughput", "Treatment")
 anovaDat <- rbind(anovaDat,df)
 treat <- rep("max", times=length(large))
 df <- data.frame(large, treat)
-names(df) <- c("Oral Throughput", "Treatment")
+names(df) <- c("OralThroughput", "Treatment")
 anovaDat <- rbind(anovaDat,df)
 treat <- rep("smart", times=length(smart))
 df <- data.frame(smart, treat)
-names(df) <- c("Oral Throughput", "Treatment")
+names(df) <- c("OralThroughput", "Treatment")
 anovaDat <- rbind(anovaDat,df)
 
 library(dplyr)
 group_by(anovaDat, Treatment) %>%
   summarise(
     count = n(),
-    mean = mean(weight, na.rm = TRUE),
-    sd = sd(weight, na.rm = TRUE)
+    mean = mean(OralThroughput, na.rm = TRUE),
+    sd = sd(OralThroughput, na.rm = TRUE)
   )
 
-library("ggpubr")
-ggboxplot(my_data, x = "Treatment", y = "Oral Throughput", 
+library(ggplot2)
+ggboxplot(my_data, x = "Treatment", y = "OralThroughput", 
           color = "Treatment", palette = c("#00AFBB", "#E7B800", "#FC4E07",  "#55FF00" ),
           order = c("base", "prof", "max", "smart"),
           ylab = "Throughput", xlab = "Treatment")

### 2019-12-01 Mayo/LatinSquare/10p10t/10p10t.R
Did the latin square and started on draft. did heat map and fixed the txt line in gitignore file to maintain consistency.

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/10p10t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/1p10t/1p10t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p10t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+mu=mean(oralOut)
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+mu=mean(ivOut)
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/1p1t/1p1t.R

@@ -1,0 +1,271 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p1t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
[…]

### 2019-12-01 Mayo/LatinSquare/1p2t/1p2t.R

@@ -1,0 +1,271 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p2t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
[…]

### 2019-12-01 Mayo/LatinSquare/1p3t/1p3t.R

@@ -1,0 +1,271 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p3t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
[…]

### 2019-12-01 Mayo/LatinSquare/1p4t/1p4t.R

@@ -1,0 +1,271 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p4t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
[…]

### 2019-12-01 Mayo/LatinSquare/1p5t/1p5t.R

@@ -1,0 +1,271 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p5t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
[…]

### 2019-12-01 Mayo/LatinSquare/1p6t/1p6t.R

@@ -1,0 +1,271 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p6t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
[…]

### 2019-12-01 Mayo/LatinSquare/1p7t/1p7t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p7t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+mu=mean(oralOut)
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+mu=mean(ivOut)
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/1p8t/1p8t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p8t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+mu=mean(oralOut)
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+mu=mean(ivOut)
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/1p9t/1p9t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/1p9t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+mu=mean(oralOut)
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+mu=mean(ivOut)
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p10t/2p10t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p10t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p1t/2p1t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p1t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p2t/2p2t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p2t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+mu=mean(oralOut)
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+mu=mean(ivOut)
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p3t/2p3t.R

@@ -1,0 +1,287 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p3t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+
+require(ggplot2)
+
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+mu=mean(oralOut)
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+mu=mean(ivOut)
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p4t/2p4t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p4t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p5t/2p5t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p5t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+mu=mean(oralOut)
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+mu=mean(ivOut)
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p6t/2p6t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p6t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p7t/2p7t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p7t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p8t/2p8t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p8t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/2p9t/2p9t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/2p9t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p10t/3p10t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p10t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p1t/3p1t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p1t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p2t/3p2t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p2t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+42s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p3t/3p3t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p3t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p4t/3p4t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p4t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p5t/3p5t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p5t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p6t/3p6t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p6t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p7t/3p7t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p7t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p8t/3p8t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p8t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/3p9t/3p9t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/3p9t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/4p10t/4p10t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/4p10t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/4p1t/4p1t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/4p1t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/4p2t/4p2t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/4p2t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/4p3t/4p3t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/4p3t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/4p4t/4p4t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/4p4t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/5p10t/5p10t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/5p10t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/5p1t/5p1t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/5p1t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/5p2t/5p2t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/5p2t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/6p10t/6p10t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/6p10t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/6p1t/6p1t.R

@@ -1,0 +1,285 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/6p1t")
+
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+
+
+
+#### Oral Filled Stats
+X <- read.csv("oralFilled.txt", header = FALSE)
+oralOut <- X[,1]
+(mu=mean(oralOut))
+s=sd(oralOut)
+delta <- zstar*s/sqrt(length(oralOut))
+(lowerOralOut<- mu-delta)
+(upperOralOut<- mu+delta)
+
+#### IV Filled Stats
+X <- read.csv("ivFilled.txt", header = FALSE)
+ivOut <- X[,1]
+(mu=mean(ivOut))
+s=sd(ivOut)
+delta <- zstar*s/sqrt(length(ivOut))
+(lowerIVOut<- mu-delta)
+(upperIVOut<- mu+delta)
+
+### Filled intervals:
+df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+png("FilledCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
+dev.off()
+
+
+
+
+
+
+
+
+
+
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
[…]

### 2019-12-01 Mayo/LatinSquare/Worker.h

@@ -1,0 +1,45 @@
+#pragma once
+
+#include <iostream>
+#include <vector>
+#include <string>
+#include <queue>
+#include "Script.h"
+
+
+using namespace std;
+
+//Worker class
+class Worker{
+	public:
+		Worker();
+		Worker(bool tech, bool iv);
+		bool getTech();
+		void setTech(bool tech);
+		bool getIV();
+		void setIV(bool iv);
+		bool getIdle();
+		void setIdle(bool idle);
+		double getIdleTime();
+		void updateIdleTime(double t);
+		void setIdleTime(double t);
+		Script getCurrentScript();
+		void setCurrentScript(Script s);
+		void updateWorkTime(double t);
+		double getWorkTime();
+		void setWorkTime(double t);
+		int getTask();
+		void setTask(int s);
+
+
+
+	private:
+		bool isTech;
+		bool isIV;
+		bool isIdle;
+		double idleTime;
+		double workTime;
+		//vector<bool> idleChecks;
+		Script currentScript;
+		int currentTask;
+};

### 2019-12-01 Mayo/LatinSquare/inputs/InputMaker.R

@@ -1,0 +1,26 @@
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LatinSquare/inputs")
+rm(list = ls())
+set.seed(420)
+oralIncomingTimes <- rexp(1, rate=.129199)
+while(sum(oralIncomingTimes) < 720){
+  oralIncomingTimes <- c(oralIncomingTimes, rexp(1, rate=.129199))
+}
+ivIncomingTimes <- rexp(1, rate=.05988024)
+while(sum(ivIncomingTimes) < 720){
+  ivIncomingTimes <- c(ivIncomingTimes, rexp(1, rate=.05988024))
+}
+n <- length(oralIncomingTimes)+length(ivIncomingTimes)
+entryTimes <- rnorm(n,9.873784,2.095579)
+entryVerTimes <-runif(n,1.2726,3.4059)
+oralPrepTimes <- rlnorm(length(oralIncomingTimes),2.99140489,.06300657)
+ivPrepTimes <- rweibull(length(ivIncomingTimes),2.362195,6.359247)
+prepVerTimes <- rweibull(n,2.911269,2.143830)
+dispTimes <- rnorm(n,2.947898,.566620)
+write.table(oralIncomingTimes, "oralIn.txt", row.names = FALSE, col.names = FALSE)
+write.table(ivIncomingTimes, "ivIn.txt", row.names = FALSE, col.names = FALSE)
+write.table(entryTimes, "entry.txt", row.names = FALSE, col.names = FALSE)
+write.table(entryVerTimes, "entryver.txt", row.names = FALSE, col.names = FALSE)
+write.table(oralPrepTimes, "oralprep.txt", row.names = FALSE, col.names = FALSE)
+write.table(ivPrepTimes, "ivprep.txt", row.names = FALSE, col.names = FALSE)
+write.table(prepVerTimes, "prepver.txt", row.names = FALSE, col.names = FALSE)
+write.table(dispTimes, "disp.txt", row.names = FALSE, col.names = FALSE)

### 2019-12-01 Mayo/LatinSquare/main.cpp

@@ -1,0 +1,986 @@
+//Justin Hood 2019 Capstone Project
+
+#include <chrono>
+#include <iostream>
+#include <ctime>
+#include <random>
+#include <string>
+#include <queue>
+#include <algorithm>
+#include <map>
+#include <fstream>
+#include "Script.h"
+#include "Worker.h"
+
+
+
+using namespace std;
+
+//Globals
+int numOrders;
+int tic;
+double toc;
+int nSteps;
+int nTrials;
+int step;
+vector<Worker> idleWorkers;
+vector<Worker> activeWorkers;
+int orderNum;
+
+
+////Setup Queues
+queue<double> oralIncoming;
+queue<double> ivIncoming;
+queue<double> entryTimes;
+queue<double> entryVerTimes;
+queue<double> oralPrepTimes;
+queue<double> ivPrepTimes;
+queue<double> prepVerTimes;
+queue<double> dispenseTimes;
+////Process Queues
+queue<Script> entryQ;
+queue<Script> entryVerQ;
+queue<Script> oralFillQ;
+queue<Script> ivFillQ;
+queue<Script> fillVerQ;
+queue<Script> dispQ;
+queue<Script> endQ;
+//////Queue Length Holder
+/*vector<int> entryQLengths;
+vector<int> entryVerQLengths;
+vector<int> oralFillQLengths;
+vector<int> ivFillQLengths;
+vector<int> fillVerQLengths;
+vector<int> dispQLengths;*/
+
+//Funky Bois
+queue<double> getOralIncoming(int hours);
+queue<double> getIVIncoming(int hours);
+queue<double> getEntryTimes(int num);
+queue<double> getEntryVerTimes(int num);
+queue<double> getOralPrepTimes(int num);
+queue<double> getIVPrepTimes(int num);
+queue<double> getPrepVerTimes(int num);
+queue<double> getDispenseTimes(int num);
+
+int main(){
+	orderNum=1;
+	//Get the user input to the simulation here.
+	int hrs; //Duration of Sim in hours
+	int numP; //Number of Pharmacists
+	int numT; //Number of Technicians
+	int numSim; //Number of simulations to run
+	cout << "Please enter the duration of the simulation in hours:" <<  endl;
+	cin >> hrs;
+	cout << "Please enter the number of steps per minute:" << endl;
+	cin >> tic;
+	cout << "Please enter the number of Pharmacists in the simulation:" << endl;
+	cin >> numP;
[…]

### 2019-12-01 Mayo/Priority Comparisons/ANOVA on Base Case.R

@@ -1,4 +1,5 @@
-setwd("~/Desktop/Capstone/Mayo/Priority Comparisons")
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Priority Comparisons")
+#setwd("~/Desktop/Capstone/Mayo/Priority Comparisons")
 rm(list = ls())
 
 ## Get My Data for Oral Filled
@@ -40,9 +41,20 @@ group_by(anovaDat, Treatment) %>%
     mean = mean(OralThroughput, na.rm = TRUE),
     sd = sd(OralThroughput, na.rm = TRUE)
   )
-
 library(ggplot2)
-ggboxplot(my_data, x = "Treatment", y = "OralThroughput", 
-          color = "Treatment", palette = c("#00AFBB", "#E7B800", "#FC4E07",  "#55FF00" ),
-          order = c("base", "prof", "max", "smart"),
-          ylab = "Throughput", xlab = "Treatment")
+library(viridis)
+# Basic box plot
+p <- ggplot(anovaDat, aes(x=Treatment, y=OralThroughput, color=Treatment)) + 
+  geom_boxplot()
+p + scale_color_viridis(discrete = TRUE, option="D")
+
+oral.aov <- aov(OralThroughput~Treatment, data=anovaDat)
+summary(oral.aov)
+TukeyHSD(oral.aov)
+pairwise.t.test(anovaDat$OralThroughput, anovaDat$Treatment,
+                p.adjust.method = "BH", pool.sd = FALSE)
+
+# Extract the residuals
+aov_residuals <- residuals(object = oral.aov )
+# Run Shapiro-Wilk test
+shapiro.test(x = aov_residuals )

### 2019-12-02 Mayo/Rough Draft/Draft.tex
Drafting. Might have to swap base and prof

\documentclass[11pt]{report}            % Report class in 11 points
\parindent0pt  \parskip10pt             % make block paragraphs
\raggedright                            % do not right-justify
\usepackage{amsmath, amssymb, amsthm,graphicx, enumitem, hyperref,gensymb, float} %, threeparttable}
\newcommand{\ro}{\mathcal{R}_0}
\makeatletter
\newcommand*{\centerfloat}{%
  \parindent \z@
  \leftskip \z@ \@plus 1fil \@minus \textwidth
  \rightskip\leftskip
  \parfillskip \z@skip}
\makeatother
%*******************************************************************%
\title{\bf Mayo Case Study Rough Draft\\
\large Using Discrete Event Simulation}  % Supply information
\author{Justin Hood\\
MSCS 791}              %   for the title page.
\date{\today}                           %   Use current date.
\begin{document}                        % End of preamble, start of text.
\maketitle                              % Print title page.
\pagenumbering{roman}                   % roman page number for toc
\setcounter{page}{2}                    % make it start with "ii"
\tableofcontents                        % Print table of contents
\newpage
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

\section*{Introduction}                % Print a "chapter" heading\
\addcontentsline{toc}{section}{Introduction}
\pagenumbering{arabic}                  % Start text with arabic 1
In this case study, we are tasked with both modeling and optimizing the workflow for a pharmacy based on a sample of data regarding task duration and incoming order frequency. In addition to the sample data for the pharmacy, we are also given a brief overview of the basic workflow for the pharmacy. Using this information, we shall begin by constructing a discrete event simulation in c++ to test our so called ``control" case, i.e. the pharmacy described by the basic information. Once this simulation is running and tested, we shall attack the optimization on two fronts.
\begin{enumerate}
\item Optimizing task priority within the workflow (Picking the best queue to pull from)
\item Optimizing staff breakdown (Best number of pharmacists vs. technicians to employ)
\end{enumerate}
\section*{Methods}
\addcontentsline{toc}{section}{Methods}
In order to effectively model and optimize the workflow in this pharmacy, we

\subsection*{Process Workflow}
\addcontentsline{toc}{subsection}{Process Workflow}
To begin, we consider the basic workflow. As stated, due to regulations, pharmacists are able to perform tasks that technicians are unable to. The task breakdown is as follows:
\begin{center}
\begin{tabular}{|c||c|}
\hline
Technician & Pharmacist\\\hline\hline
Order Entry & Order Entry \\\hline
& Entry Verification \\\hline
Drug Preparation & Drug Preparation\\\hline
& Preparation Verification\\\hline
Distribution & Distribution\\\hline
\end{tabular}
\end{center}
This is to say that $T_{Technician}\subset T_{Pharmacist}$.  With this distinction in mind, we consider the flowchart contained in Figure \ref{fig:flowchart}, which describes the process workflow graphically.
\begin{figure}[H]
\centering
\includegraphics[scale=.5]{Flowchart.png}
\caption{Pharmacy workflow by task position noting which tasks are pharmacist only.}
\label{fig:flowchart}
\end{figure}
Here we may clearly see that with the exception of the IV Fill step, the workflow is fairly linear, which will make the simulation fairly simple to write. The basic workflow is:
\begin{enumerate}
\item Order comes in and enters the Entry Task Queue
\item Employee enters the order, order enters the Entry Verification Queue
\item Pharmacist verifies the entry, order enters the Fill Queue
\item Employee fills the order, order enters the Fill Verification Queue
\item Pharmacist verifies the fill, order enters the Dispense Queue
\item Employee dispenses the order through the window
\end{enumerate}
There is a fork in the process workflow after step 3, where the order's type (Oral vs. IV) must be checked so it may be put in the appropriate filling queue, however this does not affect the linearity of the process at this step. 
%\subsection*{SIR Model}
%\addcontentsline{toc}{subsection}{SIR Model}
%
%\subsection*{Beta}
%\addcontentsline{toc}{subsection}{Beta}
%$\beta$ is a product of many factors, the main being team success, physical locale (weather, population, income), and the social environment of the city\cite{light}. In order to compute a given teams $\beta$ value, we must quantify these factors as follows.
%\subsubsection*{Team Success}
%\addcontentsline{toc}{subsection}{Team Success}
%
%\begin{equation}\label{acoeff}
%\log(a_t) = 14.1 + 0.2205(WINT)+.091\log(POP)-0.3766\log(INC)
%\end{equation}
%\begin{equation}\label{bcoeff}
%\log(b_t) = 9.171 + .03(WINT)+.028\log(POP)-.1879\log(INC)
%\end{equation}
%Each of the coefficients we compute have incredibly large t-values, which aligns with the linear nature of (\ref{a}) and (\ref{b}). As such, we are confident that these coefficients are correct for the purposes of our analysis. With these coefficients computed, we can compute the following location score for our potential Milwaukee team,
%
%\begin{table}[H]
%\centerfloat
%\begin{tabular}{lrrrrrrrr}
%\hline
%\multicolumn{9}{c}{Location Score for Milwaukee} \\
%Team & Population$^a$ & GDP per capita$^b$ & Temperature$^c$ & WINT & $a_t$ & $b_t$ & $H_t$ & $h_t$\\
%\hline
%Milwaukee & 1.572245 & \$58,680.00 & -2 & 1 & 27583.4 & 1274.342 & 117.1288 & 0.9990123
%\end{tabular}
%\caption{$^a$in Millions \cite{population}; $^b$USD \cite{gdp}; $^c$ \degree C \cite{weather}}
%\label{table:Milwaukee_H}
%\end{table}
%
%\end{description}
\begin{thebibliography}{9}
%\bibitem{light} J. Light, A. Chernin, and J. M. Heffernan, ``NHL expansion and fan allegiance: a mathematical modelling study,” \textit{Mathematics-in-Industry Case Studies}, vol. 7, no. 1, Apr. 2016.
%\bibitem{money} M. Ozanian and K. Badenhausen, ``The NHLs Most Valuable Teams” \textit{Forbes}, 21-Feb-2019. [Online]. Available: \url{https://www.forbes.com/sites/mikeozanian/2018/12/05/the-nhls-most-valuable-teams/}. [Accessed: 25-Sep-2019].
%\bibitem{stats}  HockeyDB.com (2019) National Hockey League history and statistics. \url{http://www.hockeydb.com/ihdb/stats/leagues/141.html}. Web
%\bibitem{jones}J. C. H. Jones and D. G. Ferguson, ``Location and Survival in the National Hockey League,” \textit{The Journal of Industrial Economics}, vol. 36, no. 4, p. 443, Jun. 1988.
%\bibitem{population} US Census Bureau and Data Integration Division, ``Population Estimates,” \textit{Metropolitan and Micropolitan Statistical Area Totals Dataset: Population and Estimated Components of Change: April 1, 2010 to July 1, 2014 - U.S Census Bureau}. [Online]. \url{https://web.archive.org/web/20150504102404/http://www.census.gov/popest/data/metro/totals/2014/CBSA-EST2014-alldata.html}. [Accessed: 30-Sep-2019].
%\bibitem{gdp} ``Regional Economic Accounts GDP and Personal Income,” \textit{BEA}. [Online]. \url{https://apps.bea.gov/itable/drilldown.cfm?reqid=70&stepnum=40&Major_Area=5&State=5&Area=XX&TableId=504&Statistic=1&Year=2014&YearBegin=-1&Year_End=-1&Unit_Of_Measure=Levels&Rank=1&Drill=1&nRange=5}. [Accessed: 28-Sep-2019].
%\bibitem{weather} ``Milwaukee Temperatures: Averages by Month,” \textit{Milwaukee WI Average Temperatures by Month - Current Results}. [Online]. \url{https://www.currentresults.com/Weather/Wisconsin/Places/milwaukee-temperatures-by-month-average.php}. [Accessed: 30-Sep-2019].
%\bibitem{whynot} J. Hand, C. Jozwik, H. Magner, Z. Brooke, A. Landowski, A. Parquette, and E. Johnson, ``Why Milwaukee is Not an NHL City,” \textit{Milwaukee Magazine}, 16-Nov-2018. [Online]. \url{https://www.milwaukeemag.com/milwaukee-not-nhl-city/}. [Accessed: 29-Sep-2019].
%\bibitem{draft} ``2017 NHL Expansion Draft,” \textit{Wikipedia}, 27-Apr-2019. [Online]. \url{https://en.wikipedia.org/wiki/2017_NHL_Expansion_Draft}. [Accessed: 29-Sep-2019].
%\bibitem{wisco} ``NHL Players Born in Wisconsin, United States,” \textit{Hockey}. [Online]. \url{https://www.hockey-reference.com/friv/birthplaces.cgi?country=US&province&state=WI&fbclid=IwAR1vb6vzR95-DX0B_zRyV_gLxYcWMneos3Ppn8RBNsnHQqzA9d4sJj4X_aA}. [Accessed: 29-Sep-2019].
\end{thebibliography}
\end{document}                          % The required last line

### 2019-12-03 Mayo/Rough Draft/Draft.tex
Finished Rough draft

@@
-\documentclass[11pt]{report}            % Report class in 11 points
+\documentclass[10pt]{report}            % Report class in 11 points
 \parindent0pt  \parskip10pt             % make block paragraphs
@@
 \usepackage{amsmath, amssymb, amsthm,graphicx, enumitem, hyperref,gensymb, float} %, threeparttable}
+\usepackage[table]{xcolor}
 \newcommand{\ro}{\mathcal{R}_0}
@@
 \addcontentsline{toc}{section}{Abstract}
-
 \section*{Introduction}                % Print a "chapter" heading\
@@
 \pagenumbering{arabic}                  % Start text with arabic 1
-In this case study, we are tasked with both modeling and optimizing the workflow for a pharmacy based on a sample of data regarding task duration and incoming order frequency.
+In this case study, we are tasked with both modeling and optimizing the workflow for a pharmacy based on samples of data regarding task duration and incoming order frequency.
 In addition to the sample data for the pharmacy, we are also given a brief overview of the basic workflow for the pharmacy.
-Using this information, we shall begin by constructing a discrete event simulation in c++ to test our so called ``control" case, i.e.
+Using this information, we shall begin by constructing a discrete event simulation in C++ to test our so called ``control" case, i.e.
 the pharmacy described by the basic information.
@@
 \end{enumerate}
+With these optimizations, we should be able to develop a sense of what makes the pharmacy run more efficiently, as well as an idea of what variables could be changed to further increase the accuracy of our simulation, as well as improve the pharmacy's function.
 \section*{Methods}
 \addcontentsline{toc}{section}{Methods}
-In order to effectively model and optimize the workflow in this pharmacy, we
-
+In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy.
+This workflow is tied to both legal regulations as well as potentially company specific guidelines.
+This workflow will form the backbone for our simulations main loop.
+The second stage of development is centered around identifying the distributions from the time sample data provided.
+In order to run the simulation, we need to know the distributions that each time variable comes from.
+Finally, we run the simulation and report statistical analysis on the results.
+%In order to effectively model and optimize the workflow in this pharmacy, we consider the given scenario, and how we might optimize it.
+As described, there are essentially no guidelines in place to speed up process workflow, which we will find dramatically affects the overall performance.
+As a pharmacy, we assume that maximizing both the number of prescriptions and the speed at which they are filled is paramount to the public image as well as its financial success.
 \subsection*{Process Workflow}
 \addcontentsline{toc}{subsection}{Process Workflow}
-To begin, we consider the basic workflow. As stated, due to regulations, pharmacists are able to perform tasks that technicians are unable to. The task breakdown is as follows:
-\begin{center}
+To begin, we consider the basic workflow.
+As stated, due to regulations, pharmacists are able to perform tasks that technicians are unable to.
+Ignoring the IV technician for the time being as its task is isolated from the main workflow, the task breakdown is as follows:
+\begin{table}[H]
+\centering
 \begin{tabular}{|c||c|}
@@
 Order Entry & Order Entry \\\hline
-& Entry Verification \\\hline
+& \cellcolor{red!25}Entry Verification \\\hline
 Drug Preparation & Drug Preparation\\\hline
-& Preparation Verification\\\hline
+& \cellcolor{red!25}Preparation Verification\\\hline
 Distribution & Distribution\\\hline
 \end{tabular}
-\end{center}
-This is to say that $T_{Technician}\subset T_{Pharmacist}$.
+\caption{Pharmacist vs Technician tasks.}
+\label{table:tasks}
+\end{table}
+As illustrated in Table \ref{table:tasks}, we see that pharmacists are capable of doing all steps in the workflow, while the technicians may only perform three of the five.
+This is to say that $Task_{Technician}\subset Task_{Pharmacist}$.
 With this distinction in mind, we consider the flowchart contained in Figure \ref{fig:flowchart}, which describes the process workflow graphically.
@@
 \end{figure}
-Here we may clearly see that with the exception of the IV Fill step, the workflow is fairly linear, which will make the simulation fairly simple to write. The basic workflow is:
+Here we may clearly see that with the exception of the IV Fill step, the workflow is fairly linear, which will make the simulation fairly simple in theory, allowing for more advanced optimizations.
+The basic workflow is:
 \begin{enumerate}
@@
 IV) must be checked so it may be put in the appropriate filling queue, however this does not affect the linearity of the process at this step.
+With this workflow defined, we consider the next step of building our simulation, identifying the distributions from which we sample times from.
+\section*{Distribution Identification}
+\addcontentsline{toc}{section}{Distribution Identification}
+As we have identified in the workflow above, there are essentially six pivotal points that will have times associated with them: Entry, Entry Verification, Oral Drug Preparation, IV Drug Preparation, Order Prep Verification, and Distribution.
+In addition to these six points, we are also aware of the fact that the times between incoming oral and IV orders come from different distributions.
+As part of the given data, we have a sample of the times from each of these eight different categories, ranging in size from 34 to 60 observations.
+Using each of these samples, we shall construct Cullen and Frey graphs to attempt to isolate the correct distributions.
+With this set of hypothetical distributions in hand, we shall fit the data and test the goodness of fit statistic to identify the best fit.
+\subsection*{Order Entry}
+\addcontentsline{toc}{subsection}{Order Entry}
+To begin, we consider the data provided for the order entry times. Using $R$, we construct both a histogram and a Cullen and Frey graph (Figure \ref{fig:orderEntryHistCullen}),
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.35]{OrderEntryHist.png}
+\includegraphics[scale=.35]{OrderEntryCullen.png}
+\caption{Histogram of order entry times (left) and its corresponding Cullen and Frey graph (right)}
+\label{fig:orderEntryHistCullen}
+\end{figure}
+Looking at these plots, it appears that the data comes from a normal population, and the Cullen and Frey plot supports this.
+For completeness, we shall test this sample as being from a normal distribution as well as a gamma and log-normal distribution.
+Once the data has been fit with each of these distributions, $R$ is used to compute a goodness of fit statistic for each model, and these results follow:
+\begin{table}[H]
+\centerfloat
+\begin{tabular}{|r||c|c|c|}
+\hline
+& Normal Fit & Gamma Fit & log-normal Fit \\\hline
+Kolomogorov-Smirnov & \cellcolor{green!25}0.05172573 & 0.07123761 & 0.08600921\\\hline
+Anderson Darling & \cellcolor{green!25}0.14921512 & 0.28840960 & 0.45314418\\\hline
+AIC & \cellcolor{green!25}219.8769 & 221.3501 & 223.2712\\\hline
+\end{tabular}
+\caption{Goodness-of-Fit statistics for hypothetical fits on the order entry data.}
+\label{table:entryGOF}
+\end{table}
+As highlighted in Table \ref{table:entryGOF}, by treating this sample as part of a larger normal population, we produce the smallest goodness-of-fit statistics, implying the best fit.
+As such, we shall treat this as the correct distribution for sampling purposes in our simulation.
+The relevant distribution statistics follow,
+\[\text{Order Entry}\sim N(\mu=9.873784,\ \sigma=2.095579)\]
+\subsection*{Remaining Distributions}
+\addcontentsline{toc}{subsection}{Remaining Distributions}
+In a similar fashion, the remaining distributions are identified as follows:
+\begin{align*}
+\text{Entry Verification Times} &\sim U(1.2726,\ 3.4059)\\
+\text{Oral Preparation Times} &\sim \text{Lognormal}(\mu=2.99140489,\ \sigma=.06300657)\\
+\text{IV Preparation Times} &\sim \text{Weibull}(shape=2.362195,\ scale=6.359247)\\
+\text{Preparation Verification Times} &\sim \text{Weibull}(shape=2.911269,\ scale=2.143830)\\
+\text{Dispense Times} &\sim N(\mu=2.947898,\ \sigma=0.566620)\\
+\text{Oral Incoming Times} &\sim \text{Exponential}(\lambda = 0.129199 )\\
+\text{IV Incoming Times} &\sim \text{Exponential}(\lambda = 0.05988024 )
+\end{align*}
+With these distributions in hand, we can begin the construction of the base case of the simulation.
+\section*{First Layer of Optimization}
+\addcontentsline{toc}{section}{First Layer of Optimization}
+To begin our two pronged optimization efforts, we begin by trying to improve the task logic. To begin we model the base case.
+\subsection*{Construction of the Base Case}
+\addcontentsline{toc}{subsection}{Base Case}
+To construct the simulation of the pharmacy, the programming language C++ was used due to its speed, as well as object oriented structure.
+This structure allowed for maximal customization of our data.
+To build the simulation, two unique class objects were written to house the details required for a given order, as well as each of the employees.
+Within these classes relevant structures for computing the idle times and other important statistics are included and updated throughout the simulation.
+An outline of the pseudo-code for the simulation follows:
+\begin{verbatim}
+Read in user input (number of hours, sampling frequency, number of employees, etc.)
+For(each simulation){
+    Construct workers and place in idle pool
+    Calculate relevant duration times in queues from distribution data
+    while(!endOfSim){
+        Check and see if new order enters in this time step
+        Check if any active workers have finished task
+        if(Finished){
+            Push order to next queue, move employee to idle pool
+        }else{
+            Increment time step
+        }
+        For(each idle worker){
+            if(any queue not empty){
+                Assign task at random                   
+            }else{
+                Add to idle time
+            }
+        }
+        Write queue lengths to file
+    }
+    Write end of simulation data
+}
+\end{verbatim}
+With this simulation constructed, the base case was run using the following parameters,
+\begin{itemize}
+\item Number of Hours: 12
+\item Number of Updates per Minute: 4 (Every 15 seconds)
+\item Number of Pharmacists: 2
+\item Number of Techs: 5 (4 Normal and 1 IV)
+\item Number of Trials: 30
+\end{itemize}
+It is important to note here the job assignment of the base case.
+In this model, when job assignment begins for each employee, each non-empty job is put into a pool and randomly chosen with no priority.
+So, a pharmacist has an equal probability of doing a pharmacist only task or a technician level task.
+Changing this assignment will become a cornerstone of our optimization efforts.
+\subsubsection*{Base Case Results}
+Using the parameters above, the following 95\% confidence intervals were obtained,
+\begin{align*}
+\text{Oral Incoming} &= [91.6024,\ 98.06426] && \text{Number of Orders}\\
+\text{IV Incoming} &= [42.47068,\ 47.12932] && \text{Number of Orders}\\\\
+\text{Entry Queue} &= [0.4310875,\ 0.6114125] && \text{Number of Orders}\\
+\text{Entry Verification Queue} &= [7.997571,\ 12.58185] && \text{Number of Orders}\\
+\text{Oral Fill Queue} &= [0.1240198,\ 0.1679247] && \text{Number of Orders}\\
+\text{IV Fill Queue} &= [0.079518,\ 0.1349264] && \text{Number of Orders}\\
+\text{Fill Verification Queue} &= [3.427384,\ 5.809907] && \text{Number of Orders}\\
+\text{Dispense Queue} &= [0.1735777,\ 0.2304964] && \text{Number of Orders}\\\\
+\text{Oral Filled} &= [67.26063,\ 70.40604] && \text{Number of Orders}\\
+\text{IV Filled} &= [32.72671,\ 37.33995] && \text{Number of Orders}\\\\
+\text{Pharmacist Idle Time} &= [2.811366,\ 4.692106] && \text{Percent of Total Time}\\
+\text{Technician Idle Time} &= [17.50725,\ 20.02053] && \text{Percent of Total Time}\\
+\text{IV Technician Idle Time} &= [67.62806,\ 71.53167] && \text{Percent of Total Time}\\\\
+\text{Oral Throughput Times} &= [105.1253,\ 136.618] && \text{Minutes}\\
+\text{IV Throughput Times} &= [91.9162,\ 127.0587] && \text{Minutes}\\
+\text{Oral Wait Times} &= [68.11842,\ 99.61155] && \text{Minutes}\\
+\text{IV Wait Times} &= [69.27191,\ 104.3281] && \text{Minutes}\\\\
+\end{align*}
+While these intervals do provide important analysis on the data, a graphical interpretation of this data will help us to more accurately examine potential points of congestion in the model.
+Figure \ref{fig:baseQ} has box and whisker plots for each of the queues in the base case.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.5]{BaseQueueCIs.png}
+\caption{Box and whisker plots for average queue lengths by type}
+\label{fig:baseQ}
+\end{figure}
+We see that the results of this simulation point to the verification queues as being congestion points.
+Notably, these are the two tasks in the workflow that are pharmacist specific.
+This congestion then is likely due to the method by which workers received their job assignments.
+With the pharmacists choosing from all possible tasks equally, they can take work from the technicians, who cannot in return work from the verification tasks.
+Reducing this congestion will be the goal of our first optimization.
+*******Talk about idle times*******************
+\subsection*{First Optimization: Lazy Pharmacists}
+\addcontentsline{toc}{subsection}{Lazy Pharmacists}
+Given that the verification tasks are causing congestion in the base model, we consider the effects of changing the job assignment method in the simulation to the following.
+\begin{verbatim}
+if(pharmacist){
+    if(verification queues !empty){
+        choose one at random
+    }else{
+        do nothing
+    }
+}
+if(technician){
+    if(any queues !empty){
+        choose one at random
+    }else{
+        do nothing
+}
+\end{verbatim}
+Under this scheme, the pharmacists will only do pharmacist specific tasks, leaving the technicians to do the remainder of the tasks.
+Running the simulation with the same parameters as the base case, under the new job choice logic yields some unexpected results.
+Firstly, the average queue lengths are much different.
+Figure \ref{fig:basevprof} shows the differing results.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.35]{BaseQueueCIs.png}
+\includegraphics[scale=.35]{ProfQueueCIs.png}
+\caption{Base case (left) vs. Lazy Pharmacist (Right) average queue lengths}
+\label{fig:basevprof}
+\end{figure}
+Under the original schema, all queues were essentially empty except for the verification queues, while under our new schema all of the non-verification queues show increases.
+Indeed we find that the average queue length for our new case is slightly larger than before,
+\[\overline{Length}_{Base}=2.648<2.898=\overline{Length}_{Lazy Pharmacist}\]
+In addition to this, the average idle time for an employee is significantly larger,
+\[\overline{Idle}_{Base}=14.475\% < 21.627\%=\overline{Idle}_{Lazy Pharmacist}\]
+Looking more closely into this idle time data, we see that the average idle time for a pharmacist in the new scheme is approximately $67\%$, which is clearly not an effective use of their time.
+As such, we seek to find a better process optimization.
+\subsection*{Second Optimization: Largest Queue}
+\addcontentsline{toc}{subsection}{Largest Queue}
+Given that forcing the pharmacists to only pull from the verification tasks is hurting the efficiency of the model, we consider a new job assignment logic, choosing the largest possible task.
+So, a pharmacist will choose to take their next task from the largest of all 5 possible queues, while technicians may choose from the 3 technician level queues.
+Running the simulation with the same parameters as the base case, under the new job choice logic yields results that are more aligned with what we would expect.
+Figure \ref{fig:basevlong} shows the comparison on average queue lengths between the base case and the longest queue method.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.35]{BaseQueueCIs.png}
+\includegraphics[scale=.35]{LongestQueueCIs.png}
+\caption{Base case (left) vs. Largest Queue (Right) average queue lengths}
+\label{fig:basevlong}
+\end{figure}
+We see that under this new system, all of the queues (except IV fill) have non-zero means, but that they are all relatively small compared to the mean of approximately 10 for the base entry verification length.
+Looking deeper into the data, we see that the average queue length is reduced from $2.648$ in the base case to $1.389$ in this new method.
+In addition to this, average idle time for the workers is reduced from $14.475\%$ in our base model to $13.395\%$.
+While these changes may seem somewhat small, consider now the mean throughput times between the two models.
+\begin{figure}
+\centering
+\includegraphics[scale=.35]{BaseThroughputCIs.png}
+\includegraphics[scale=.35]{LongestThroughputCIs.png}
+\caption{Base case (left) vs. Largest Queue (Right) average throughput times by order type}
+\label{fig:basevlongthrough}
+\end{figure}
+We see that by choosing the longest queue as the next task, the average throughput time for an order is reduced by a factor of almost $30\%$, which seems fairly significant.
+While this method is clearly superior to the base case, we consider finally a combination of the Lazy Pharmacist and Longest Queue methods.
+\subsection*{Third Optimization: Smart Method}
+\addcontentsline{toc}{subsection}{Smart Method}
+As our final job assignment optimization we consider a sort of mixture between choosing the longest queue, and relegating the pharmacists to the verification queues.
+Namely, under this schema, the pharmacist will first check to see if any of the verification queues are non-empty, and if so, they will choose the largest one.
+Otherwise, they choose the largest from the remaining queues.
+The technicians remain unchanged from before.
+\begin{verbatim}
+if(pharmacist){
+    if(either verification queue is nonempty){
+        choose largest
+    }else{
+        choose largest technician level queue
+    }
+}
+if(technician){
+    choose largest technician level queue
+}
+\end{verbatim}
+Again we implement this model with the basic parameters from before, getting again better results than before.
+Since we have established that the longest queue is our front-runner for the optimization, we shall use it as a basis for comparison for this smart method.
+First, we compare the base queue lengths,
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.35]{LongestQueueCIs.png}
+\includegraphics[scale=.35]{SmartQueueCIs.png}
+\caption{Largest Queue (left) vs. Smart Method (Right) average queue lengths}
+\label{fig:longvsmart}
+\end{figure}
+As expected based on the results of the lazy pharmacist method, we see improvement in the size of the verification queue lengths at the slight cost to the remainder of the queue lengths.
+Looking into the data we find,
+\[\overline{Length}_{Longest}=1.389 > 1.187 = \overline{Length}_{Smart}\]
+\[\overline{Throughput}_{Longest}=71.813 > 64.920 = \overline{Length}_{Smart}\]
+It would appear that we have achieved a slight increase in effectiveness with this new implementation, but it is hard to say given the relative magnitudes of the standard deviations in the data, thus further analysis is required.
+\section*{Comparing the First Stage Optimizations}
+\addcontentsline{toc}{section}{Comparing First Stage Optimizations}
+Given that a pharmacy is a business above all else, the goal of these optimizations should be to increase the number of orders filled and reduce the employee idle times as much as possible.
+As such, we shall conduct a one-way ANOVA test on the mean number of orders filled to find the most effective model under the given conditions.
+Looking first at the IV filled data across the different methods, we see no marked difference among the four, they are all within one standard deviation of each other.
+As such, we shall focus on the oral filled data, as there is more significant variation in the results.
+First, let us consider a collation of the oral filled data across the methods, Table \ref{table:collate}.
+\begin{table}[H]
+\centerfloat
+\begin{tabular}{|r||c|c|c|}
+\hline
+Method & Mean & Standard Deviation & $n$\\\hline\hline
+Base Case & $68.8$ & $4.40$ & $30$\\\hline
+Lazy Pharmacist & $61.7$ & $4.85$ & $30$\\\hline
+Largest Queue & $73.3$ & $9.18$ & $30$\\\hline
+Smart Method & $78.4$ & $6.04$ & $30$\\\hline
+\end{tabular}
+\caption{Collation of the Oral Fill data for each of the different optimization methods}
+\label{table:collate}
+\end{table}
+While Table \ref{table:collate} allows us to see the numbers, it is more useful to see the difference in a graphical form as in Figure \ref{fig:anovaBox}.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.5]{anovaBox.png}
+\caption{Box plots for the Oral Fill data in each method}
+\label{fig:anovaBox}
+\end{figure}
+We see from Figure \ref{fig:anovaBox} that there does seem to be a difference among the models, though it is hard to confirm visually.
+Running the ANOVA test on the null hypothesis of $\mu_i=\mu_j\ \forall i,j\in\text{Methods}$, we arrive at the $F$ statistic, $F=36.96\Rightarrow p<2\times10^{-16}$, which is highly significant.
+Given this $p$ value, we reject the null hypothesis in favor of the alternative, that there is a difference in at least one of the means.
+Given this result, we shall use $R$ to compute the Tukey honest significant differences between the means, whose results can be found in Table \ref{table:tukey}.
+\begin{table}[H]
+\centerfloat
+\begin{tabular}{|r||c|c|}
+\hline
+Methods & Difference & $p$-value\\\hline\hline
+Lazy-Base   &  $-7.133333$ & $0.0001922$\\\hline
+\cellcolor{yellow!25}Largest-Base  & \cellcolor{yellow!25}$4.500000$ & \cellcolor{yellow!25}$0.0367813$\\\hline
+Smart-Base  &   $9.600000$ & $0.0000003$\\\hline
+Largest-Lazy & $11.633333$ & $0.0000000$\\\hline
+Smart-Lazy  &  $16.733333$ & $0.0000000$\\\hline
+\cellcolor{yellow!25}Smart-Largest & \cellcolor{yellow!25}$5.100000$ & \cellcolor{yellow!25}$0.0132541$\\\hline
+\end{tabular}
+\caption{Tukey HSD for different method means}
+\label{table:tukey}
+\end{table}
+Note, Table \ref{table:tukey} has two rows highlighted.
+These rows correspond to the differences between the base method and largest queue method, as well as the largest queue method to the smart method.
+Based on the table, we can draw the following conclusion comparing the different methods,
+\[\text{Smart $>$ Largest $>$ Base}\]
+Now that we have established an ``optimal" method, we now consider how best to improve efficiency in employees.
+\section*{Efficiency Mesh}
+\addcontentsline{toc}{section}{Efficiency Mesh}
+Up until this point, all of our analysis has been performed on the basic assumptions from the base case,
+\begin{itemize}
+\item Number of Hours: 12
+\item Number of Updates per Minute: 4 (Every 15 seconds)
+\item Number of Pharmacists: 2
+\item Number of Techs: 5 (4 Normal and 1 IV)
+\item Number of Trials: 30
+\end{itemize}
+While this may be the current conditions of the pharmacy, it is still possible that this is not the most cost effective staffing.
+In order to determine the best possible configuration of employees, we shall construct a $10\times 10$ mesh that defines the pharmacies profit as a function of the number of employees of each type.
+Here, each point in our mesh corresponds to a coordinate in the Technician-Pharmacist plane that has a magnitude of profit.
+In order to assure fairness, the simulation is run with the same input sampling for each step, and run 30 times to allow for random variance in choosing queues to be accounted for.
+Let us define the profit function as,
+\[\mathcal{P}=\$55.99(Filled_{Oral}+Filled_{IV})-\$748.92(n_{Pharmacist})-\$63.12(n_{Technician})\] **********Cite money************\\
+That is to say, the pharmacy profit for a given employee configuration is revenue per filled order times the number of filled orders less the cost of employees in the configuration.
+Using the Smart Method developed earlier, we create a 3-D surface that describes the profit.
+A 2-D heat-map projection of profit appears in Figure \ref{fig:heatmap}.
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.75]{profitheatmap.png}
+\caption{Heatmap of profit values using the Smart Method. Note, labeling on the $x$ and $y$ axes is reduced by one due to indexing.}
+\label{fig:heatmap}
+\end{figure}
+As evidenced by the heat map, we see that the most profitable configurations occur for low numbers of pharmacists and higher numbers of technicians to compensate.
+In fact, we find that the optimal numbers of employees for this test is one pharmacist and seven technicians (6 normal and 1 IV).
+This resulted in a net profit, $\mathcal{P}(1,7)=\$5488.85$, though most of the surrounding mesh points had an approximately similar value, at least in the technician direction.\\
+This being said, there are a number of issues with this efficiency mesh.
+It makes broad assumptions about the value of each filled order, which could obviously be fixed using real data that the pharmacy would be able to provide.
+\section*{Conclusions}
+\addcontentsline{toc}{section}{Conclusions}
+After performing both layers of optimization, we see that there is a large range of efficiencies possible for this pharmacy.
+As we found before, simple workflow management methods could be implemented to reduce average throughput time by nearly a third, as well as reduce employee idle times...\\
+Note about skill efficiencies and dispositions, as well as leftovers from before, long term running ideas.
 %\subsection*{SIR Model}

### 2019-12-03 Mayo/Priority Comparisons/BestANOVA.R

@@ -3,32 +3,17 @@ setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Priority Comparisons")
 rm(list = ls())
 
 ## Get My Data for Oral Filled
-#####Base Case
-X <- read.csv("../FirstRun/data/oralFilled.txt", header = FALSE)
-base <- X[,1]
-#####Prof Case
-X <- read.csv("../PharmVer/data/oralFilled.txt", header = FALSE)
-prof <- X[,1]
 #####Max Case
-X <- read.csv("../Largest Queue/data/oralFilled.txt", header = FALSE)
-large <- X[,1]
+X <- read.csv("../VMax Priority/Optimized/oralFilled.txt", header = FALSE)
+best <- X[,1]
 #####Smart Case
 X <- read.csv("../VMax Priority/data/oralFilled.txt", header = FALSE)
 smart <- X[,1]
 
-
-treat <- rep("Base", times=length(base))
-df <- data.frame(base, treat)
+treat <- rep("Best", times=length(best))
+df <- data.frame(best, treat)
 names(df) <- c("OralThroughput", "Treatment")
 anovaDat <- df
-treat <- rep("Lazy", times=length(prof))
-df <- data.frame(prof, treat)
-names(df) <- c("OralThroughput", "Treatment")
-anovaDat <- rbind(anovaDat,df)
-treat <- rep("Largest", times=length(large))
-df <- data.frame(large, treat)
-names(df) <- c("OralThroughput", "Treatment")
-anovaDat <- rbind(anovaDat,df)
 treat <- rep("Smart", times=length(smart))
 df <- data.frame(smart, treat)
 names(df) <- c("OralThroughput", "Treatment")
@@ -47,7 +32,7 @@ library(viridis)
 p <- ggplot(anovaDat, aes(x=Treatment, y=OralThroughput, color=Treatment)) + 
   geom_boxplot()
 p + scale_color_viridis(discrete = TRUE, option="D")
-png("anovaBox.png")
+png("bestBox.png")
 p <- ggplot(anovaDat, aes(x=Treatment, y=OralThroughput, color=Treatment)) + 
   geom_boxplot()
 p + scale_color_viridis(discrete = TRUE, option="D")
@@ -57,7 +42,7 @@ oral.aov <- aov(OralThroughput~Treatment, data=anovaDat)
 summary(oral.aov)
 TukeyHSD(oral.aov)
[…]

### 2019-12-03 Mayo/VMax Priority/Optimized/CI Smart.R

@@ -1,5 +1,5 @@
-setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/FirstRun/data")
-#setwd("~/Desktop/Capstone/Mayo/FirstRun/data")
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/VMax Priority/Optimized")
+#setwd("~/Desktop/Capstone/Mayo/VMax Priority/data")
 rm(list = ls())
 zstar <- qnorm(.975)
 duration <- 12*60
@@ -156,7 +156,7 @@ dev.off()
 X <- read.csv("pharmIdle.txt", header = FALSE)
 X <- t(X)
 X<-X[-dim(X)[1],]
-pharmIdle <- colMeans(X)
+pharmIdle <- X
 pharmIdle <- pharmIdle/duration*100
 # These will be percentages right now, can remove if desired
 mu=mean(pharmIdle)#/duration*100
@@ -259,7 +259,7 @@ delta <- zstar*s/sqrt(length(oralWait))
 (lowerOralWait<- mu-delta)
 (upperOralWait<- mu+delta)
 
-### IV Wait Times
+### IV Throughput Times
 no_col <- max(count.fields("ivWaitTimes.txt", sep = ","))
 X <- read.table("ivWaitTimes.txt" ,sep=",",fill=TRUE,header = F,col.names=c("chr", "start", "end", "length",1:no_col))
 X <- t(X)

### 2019-12-04 Mayo/SmartLongestTask/Worker.cpp
Longest Times??

@@ -1,0 +1,66 @@
+#include "Worker.h"
+
+	Worker::Worker(){
+		isTech=false;
+		isIV=false;
+		isIdle=true;
+		idleTime=0;
+	}
+
+	Worker::Worker(bool tech, bool iv){
+		isTech=tech;
+		isIV=iv;
+		isIdle=true;
+		idleTime=0;
+	}
+
+	bool Worker::getTech(){
+		return isTech;
+	}
+
+	void Worker::setTech(bool tech){
+		isTech = tech;
+	}
+
+	bool Worker::getIV(){
+		return isIV;
+	}
+	void Worker::setIV(bool iv){
+		isIV=iv;
+	}
+	bool Worker::getIdle(){
+		return isIdle;
+	}
+	void Worker::setIdle(bool idle){
+		isIdle=idle;
+	}
+	double Worker::getIdleTime(){
+		return idleTime;
+	}
+	void Worker::updateIdleTime(double t){
+		idleTime+=t;
+	}
+	void Worker::setIdleTime(double t){
+		idleTime=t;
+	}
+	Script Worker::getCurrentScript(){
+		return currentScript;
+	}
+	void Worker::setCurrentScript(Script s){
+		currentScript=s;
+	}
+	void Worker::updateWorkTime(double t){
+		workTime -= t;
+	}
+	double Worker::getWorkTime(){
+		return workTime;
+	}
+	void Worker::setWorkTime(double t){
+		workTime=t;
+	}
+	int Worker::getTask(){
+		return currentTask;
+	}
+	void Worker::setTask(int s){
+		currentTask=s;
+	}

### 2019-12-04 Mayo/SmartLongestTask/data/CI SmartLongest.R

@@ -1,0 +1,271 @@
+#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/SmartLongestTask/data")
+setwd("~/Desktop/Capstone/Mayo/SmartLongestTask/data")
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
+X <- read.csv("entryVerQueueCounts.txt", header = FALSE)
[…]

### 2019-12-04 Mayo/SmartLongestTask/main.cpp

@@ -1,0 +1,958 @@
+//Justin Hood 2019 Capstone Project
+
+#include <chrono>
+#include <iostream>
+#include <ctime>
+#include <random>
+#include <string>
+#include <queue>
+#include <algorithm>
+#include <map>
+#include <fstream>
+#include "Script.h"
+#include "Worker.h"
+
+
+
+using namespace std;
+
+//Globals
+int numOrders;
+int tic;
+double toc;
+int nSteps;
+int nTrials;
+int step;
+vector<Worker> idleWorkers;
+vector<Worker> activeWorkers;
+int orderNum;
+
+
+////Setup Queues
+queue<double> oralIncoming;
+queue<double> ivIncoming;
+queue<double> entryTimes;
+queue<double> entryVerTimes;
+queue<double> oralPrepTimes;
+queue<double> ivPrepTimes;
+queue<double> prepVerTimes;
+queue<double> dispenseTimes;
+////Process Queues
+queue<Script> entryQ;
+queue<Script> entryVerQ;
+queue<Script> oralFillQ;
+queue<Script> ivFillQ;
+queue<Script> fillVerQ;
+queue<Script> dispQ;
+queue<Script> endQ;
+//////Queue Length Holder
+/*vector<int> entryQLengths;
+vector<int> entryVerQLengths;
+vector<int> oralFillQLengths;
+vector<int> ivFillQLengths;
+vector<int> fillVerQLengths;
+vector<int> dispQLengths;*/
+
+//Funky Bois
+queue<double> getOralIncoming(int hours);
+queue<double> getIVIncoming(int hours);
+queue<double> getEntryTimes(int num);
+queue<double> getEntryVerTimes(int num);
+queue<double> getOralPrepTimes(int num);
+queue<double> getIVPrepTimes(int num);
+queue<double> getPrepVerTimes(int num);
+queue<double> getDispenseTimes(int num);
+
+int main(){
+	orderNum=1;
+	//Get the user input to the simulation here.
+	int hrs; //Duration of Sim in hours
+	int numP; //Number of Pharmacists
+	int numT; //Number of Technicians
+	int numSim; //Number of simulations to run
+	cout << "Please enter the duration of the simulation in hours:" <<  endl;
+	cin >> hrs;
+	cout << "Please enter the number of steps per minute:" << endl;
+	cin >> tic;
+	cout << "Please enter the number of Pharmacists in the simulation:" << endl;
+	cin >> numP;
[…]

### 2019-12-06 Mayo/Distributions/DistributionComputer.R
Testing...

@@ -1,4 +1,6 @@
-setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Distributions")
+#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Distributions")
+setwd("~/Desktop/Capstone/Mayo/Distributions")
+
 rm(list = ls())
 library(fitdistrplus)
 library(logspline)
@@ -260,3 +262,11 @@ dev.off()
 ivIncoming.exp <- fitdist(ivIncoming, "exp")
 plot(ivIncoming.exp)
 gofstat(ivIncoming.exp)
+
+########## MEANS ###################
+(entry.mean <- orderEntry.norm[1]$estimate[1])
+(entryVer.mean <- (orderEntryVer.uni[1]$estimate[1]+orderEntryVer.uni[1]$estimate[2])/2)
+(oralPrep.mean <- exp(oralDrugPrep.log[1]$estimate[1]))
+(IVPrep.mean <- ivDrugPrep.w[1]$estimate[2]*gamma(1+1/ivDrugPrep.w[1]$estimate[1]))
+(prepVer.mean <- orderPrepVerification.w[1]$estimate[2]*gamma(1+1/orderPrepVerification.w[1]$estimate[1]))
+(disp.mean <- dispensing.norm[1]$estimate[1])

### 2019-12-06 Mayo/LongestTask/Script.cpp

@@ -1,0 +1,104 @@
+#include "Script.h"
+
+	Script::Script(){
+		isIV=false;
+		totalTime=0;
+		waitTime=0;
+		inQueue=false;
+	}
+
+	Script::Script(bool IV){
+		isIV=IV;
+		totalTime=0;
+		waitTime=0;
+		inQueue=false;
+	}
+
+	bool Script::getIV(){
+		return isIV;
+	}
+
+	void Script::setIV(bool b){
+		isIV=b;
+	}
+
+	double Script::getEntryTime(){
+		return entryTime;
+	}
+
+	void Script::setEntryTime(double t){
+		entryTime = t;
+	}
+
+	double Script::getEntryVerTime(){
+		return entryVerTime;
+	}
+
+	void Script::setEntryVerTime(double t){
+		entryVerTime=t;
+	}
+
+	double Script::getFillTime(){
+		return fillTime;
+	}
+
+	void Script::setFillTime(double t){
+		fillTime = t;
+	}
+
+	double Script::getFillVerTime(){
+		return fillVerTime;
+	}
+
+	void Script::setFillVerTime(double t){
+		fillVerTime = t;
+	}
+
+	double Script::getDispTime(){
+		return dispTime;
+	}
+
+	void Script::setDispTime(double t){
+		dispTime = t;
+	}
+
+	double Script::getWaitTime(){
+		return waitTime;
+	}
+
+	void Script::updateWaitTime(double t){
+		waitTime+=t;
+	}
+
+	void Script::setWaitTime(double t){
+		waitTime=t;
+	}
+
+	bool Script::getInQueue(){
+		return inQueue;
+	}
+
+	void Script::setInQueue(bool b){
+		inQueue=b;
+	}
+	int Script::getOrderNum(){
+		return orderNumber;
+	}
+	void Script::setOrderNum(int i){
+		orderNumber=i;
+	}
+	double Script::getTotalTime(){
+		return totalTime;
+	}
+	void Script::setTotalTime(double d){
+		totalTime=d;
+	}
+	void Script::updateTotalTime(double d){
+		totalTime=d-totalTime;
+	}
+	double Script::getRunTime(){
+		return runTime;
+	}
+	void Script::calcRunTime(){
+		runTime=entryTime+entryVerTime+fillTime+fillVerTime+dispTime;
+	}

### 2019-12-06 Mayo/LongestTask/data/CI LongTask.R

@@ -1,0 +1,271 @@
+#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/LongestTask/data")
+setwd("~/Desktop/Capstone/Mayo/LongestTask/data")
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
+X <- read.csv("entryVerQueueCounts.txt", header = FALSE)
+X <- t(X)
[…]

### 2019-12-06 Mayo/LongestTask/main.cpp

@@ -1,0 +1,955 @@
+//Justin Hood 2019 Capstone Project
+
+#include <chrono>
+#include <iostream>
+#include <ctime>
+#include <random>
+#include <string>
+#include <queue>
+#include <algorithm>
+#include <map>
+#include <fstream>
+#include "Script.h"
+#include "Worker.h"
+
+
+
+using namespace std;
+
+//Globals
+int numOrders;
+int tic;
+double toc;
+int nSteps;
+int nTrials;
+int step;
+vector<Worker> idleWorkers;
+vector<Worker> activeWorkers;
+int orderNum;
+
+
+////Setup Queues
+queue<double> oralIncoming;
+queue<double> ivIncoming;
+queue<double> entryTimes;
+queue<double> entryVerTimes;
+queue<double> oralPrepTimes;
+queue<double> ivPrepTimes;
+queue<double> prepVerTimes;
+queue<double> dispenseTimes;
+////Process Queues
+queue<Script> entryQ;
+queue<Script> entryVerQ;
+queue<Script> oralFillQ;
+queue<Script> ivFillQ;
+queue<Script> fillVerQ;
+queue<Script> dispQ;
+queue<Script> endQ;
+//////Queue Length Holder
+/*vector<int> entryQLengths;
+vector<int> entryVerQLengths;
+vector<int> oralFillQLengths;
+vector<int> ivFillQLengths;
+vector<int> fillVerQLengths;
+vector<int> dispQLengths;*/
+
+//Funky Bois
+queue<double> getOralIncoming(int hours);
+queue<double> getIVIncoming(int hours);
+queue<double> getEntryTimes(int num);
+queue<double> getEntryVerTimes(int num);
+queue<double> getOralPrepTimes(int num);
+queue<double> getIVPrepTimes(int num);
+queue<double> getPrepVerTimes(int num);
+queue<double> getDispenseTimes(int num);
+
+int main(){
+	orderNum=1;
+	//Get the user input to the simulation here.
+	int hrs; //Duration of Sim in hours
+	int numP; //Number of Pharmacists
+	int numT; //Number of Technicians
+	int numSim; //Number of simulations to run
+	cout << "Please enter the duration of the simulation in hours:" <<  endl;
+	cin >> hrs;
+	cout << "Please enter the number of steps per minute:" << endl;
+	cin >> tic;
+	cout << "Please enter the number of Pharmacists in the simulation:" << endl;
+	cin >> numP;
[…]

### 2019-12-06 Mayo/LongestTime/Script.h

@@ -1,0 +1,57 @@
+
+//Sourcing error
+#pragma once
+
+//Includes
+#include <iostream>
+#include <vector>
+#include <string>
+#include <queue>
+
+using namespace std;
+
+//Parent Script Class
+class Script{
+	//Public Variables
+	public:
+		Script();
+		Script(bool IV);
+		bool getIV();
+		void setIV(bool b);
+		double getEntryTime();
+		void setEntryTime(double t);
+		double getEntryVerTime();
+		void setEntryVerTime(double t);
+		double getFillTime();
+		void setFillTime(double t);
+		double getFillVerTime();
+		void setFillVerTime(double t);
+		double getDispTime();
+		void setDispTime(double t);
+		double getWaitTime();
+		void updateWaitTime(double t);
+		void setWaitTime(double t);
+		bool getInQueue();
+		void setInQueue(bool b);
+		int getOrderNum();
+		void setOrderNum(int i);
+		double getTotalTime();
+		void setTotalTime(double d);
+		void updateTotalTime(double d);
+		double getRunTime();
+		void calcRunTime();
+	private:
+		//gimme the deets
+		bool isIV;
+		double entryTime;
+		double entryVerTime;
+		double fillTime;
+		double fillVerTime;
+		double dispTime;
+		double totalTime;
+		double waitTime;
+		bool inQueue;
+		int orderNumber;
+		double runTime;
+};
+

### 2019-12-06 Mayo/LongestTime/data/CI LongTime.R

@@ -1,0 +1,271 @@
+#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Largest Queue/data")
+setwd("~/Desktop/Capstone/Mayo/LongestTime/data")
+rm(list = ls())
+zstar <- qnorm(.975)
+duration <- 12*60
+toc <- 0.25
+require(ggplot2)
+library(ggplot2)
+##### Oral Incoming Stats
+X <- read.csv("OralIncomingCounts.txt", header = FALSE)
+oralIn <- X[,1]
+mu=mean(oralIn)
+s=sd(oralIn)
+delta <- zstar*s/sqrt(length(oralIn))
+(lowerOralIn<- mu-delta)
+(upperOralIn<- mu+delta)
+
+##### IV Incoming Stats
+X <- read.csv("IVIncomingCounts.txt", header = FALSE)
+ivIn <- X[,1]
+mu=mean(ivIn)
+s=sd(ivIn)
+delta <- zstar*s/sqrt(length(ivIn))
+(lowerIVIn<- mu-delta)
+(upperIVIn<- mu+delta)
+
+
+### Incoming intervals:
+df <- data.frame(x=c("Oral Incoming", "IV Incoming"), L=c(lowerOralIn,lowerIVIn), C=c(mean(oralIn), mean(ivIn)), U=c(upperOralIn, upperIVIn))
+ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L)) + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+png("IncomingCIs.png")
+p <- ggplot(df, aes(x = x, y = C)) +
+  geom_point(size = 4) +
+  geom_errorbar(aes(ymax = U, ymin = L))
+p + labs(title = "Incoming Drug Orders", x = "Drug Type", y="Number of Orders")
+dev.off()
+
+
+##### Entry Queue Lengths
+X <- read.csv("entryQueueCounts.txt", header = FALSE)
+X <- t(X)
+X<-X[-dim(X)[1],]
+entryQ <- colMeans(X)
+mu=mean(entryQ)
+s=sd(entryQ)
+delta <- zstar*s/sqrt(length(entryQ))
+(lowerEntryQ<- mu-delta)
+(upperEntryQ<- mu+delta)
+
+##### Entry Verification Queue Lengths
+X <- read.csv("entryVerQueueCounts.txt", header = FALSE)
+X <- t(X)
[…]

### 2019-12-06 Mayo/LongestTime/main.cpp

@@ -1,0 +1,939 @@
+//Justin Hood 2019 Capstone Project
+
+#include <chrono>
+#include <iostream>
+#include <ctime>
+#include <random>
+#include <string>
+#include <queue>
+#include <algorithm>
+#include <map>
+#include <fstream>
+#include "Script.h"
+#include "Worker.h"
+
+
+
+using namespace std;
+
+//Globals
+int numOrders;
+int tic;
+double toc;
+int nSteps;
+int nTrials;
+int step;
+vector<Worker> idleWorkers;
+vector<Worker> activeWorkers;
+int orderNum;
+
+
+////Setup Queues
+queue<double> oralIncoming;
+queue<double> ivIncoming;
+queue<double> entryTimes;
+queue<double> entryVerTimes;
+queue<double> oralPrepTimes;
+queue<double> ivPrepTimes;
+queue<double> prepVerTimes;
+queue<double> dispenseTimes;
+////Process Queues
+queue<Script> entryQ;
+queue<Script> entryVerQ;
+queue<Script> oralFillQ;
+queue<Script> ivFillQ;
+queue<Script> fillVerQ;
+queue<Script> dispQ;
+queue<Script> endQ;
+//////Queue Length Holder
+/*vector<int> entryQLengths;
+vector<int> entryVerQLengths;
+vector<int> oralFillQLengths;
+vector<int> ivFillQLengths;
+vector<int> fillVerQLengths;
+vector<int> dispQLengths;*/
+
+//Funky Bois
+queue<double> getOralIncoming(int hours);
+queue<double> getIVIncoming(int hours);
+queue<double> getEntryTimes(int num);
+queue<double> getEntryVerTimes(int num);
+queue<double> getOralPrepTimes(int num);
+queue<double> getIVPrepTimes(int num);
+queue<double> getPrepVerTimes(int num);
+queue<double> getDispenseTimes(int num);
+
+int main(){
+	orderNum=1;
+	//Get the user input to the simulation here.
+	int hrs; //Duration of Sim in hours
+	int numP; //Number of Pharmacists
+	int numT; //Number of Technicians
+	int numSim; //Number of simulations to run
+	cout << "Please enter the duration of the simulation in hours:" <<  endl;
+	cin >> hrs;
+	cout << "Please enter the number of steps per minute:" << endl;
+	cin >> tic;
+	cout << "Please enter the number of Pharmacists in the simulation:" << endl;
+	cin >> numP;
[…]

### 2019-12-06 Mayo/SmartLongestTime/main.cpp

@@ -1,0 +1,943 @@
+//Justin Hood 2019 Capstone Project
+
+#include <chrono>
+#include <iostream>
+#include <ctime>
+#include <random>
+#include <string>
+#include <queue>
+#include <algorithm>
+#include <map>
+#include <fstream>
+#include "Script.h"
+#include "Worker.h"
+
+
+
+using namespace std;
+
+//Globals
+int numOrders;
+int tic;
+double toc;
+int nSteps;
+int nTrials;
+int step;
+vector<Worker> idleWorkers;
+vector<Worker> activeWorkers;
+int orderNum;
+
+
+////Setup Queues
+queue<double> oralIncoming;
+queue<double> ivIncoming;
+queue<double> entryTimes;
+queue<double> entryVerTimes;
+queue<double> oralPrepTimes;
+queue<double> ivPrepTimes;
+queue<double> prepVerTimes;
+queue<double> dispenseTimes;
+////Process Queues
+queue<Script> entryQ;
+queue<Script> entryVerQ;
+queue<Script> oralFillQ;
+queue<Script> ivFillQ;
+queue<Script> fillVerQ;
+queue<Script> dispQ;
+queue<Script> endQ;
+//////Queue Length Holder
+/*vector<int> entryQLengths;
+vector<int> entryVerQLengths;
+vector<int> oralFillQLengths;
+vector<int> ivFillQLengths;
+vector<int> fillVerQLengths;
+vector<int> dispQLengths;*/
+
+//Funky Bois
+queue<double> getOralIncoming(int hours);
+queue<double> getIVIncoming(int hours);
+queue<double> getEntryTimes(int num);
+queue<double> getEntryVerTimes(int num);
+queue<double> getOralPrepTimes(int num);
+queue<double> getIVPrepTimes(int num);
+queue<double> getPrepVerTimes(int num);
+queue<double> getDispenseTimes(int num);
+
+int main(){
+	orderNum=1;
+	//Get the user input to the simulation here.
+	int hrs; //Duration of Sim in hours
+	int numP; //Number of Pharmacists
+	int numT; //Number of Technicians
+	int numSim; //Number of simulations to run
+	cout << "Please enter the duration of the simulation in hours:" <<  endl;
+	cin >> hrs;
+	cout << "Please enter the number of steps per minute:" << endl;
+	cin >> tic;
+	cout << "Please enter the number of Pharmacists in the simulation:" << endl;
+	cin >> numP;
[…]

### 2019-12-07 Mayo/FirstRun/data/CI Base.R
PNG, axes fixed

@@ -107,14 +107,15 @@ delta <- zstar*s/sqrt(length(dispQ))
 
 ### Queue Length intervals:
 df <- data.frame(x=c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"), L=c(lowerEntryQ,lowerEntryVerQ, lowerOralFillQ, lowerIVFillQ, lowerFillVerQ, lowerDispQ), C=c(mean(entryQ), mean(entryVerQ), mean(oralFillQ), mean(ivFillQ),mean(fillVerQ), mean(dispQ)), U=c(upperEntryQ, upperEntryVerQ, upperOralFillQ, upperIVFillQ, upperFillVerQ, upperDispQ))
+df$x <- factor(df$x, levels = c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"))
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 png("QueueCIs.png")
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 dev.off()
 
@@ -238,12 +239,12 @@ delta <- zstar*s/sqrt(length(ivThrough))
 df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralThrough,lowerIVThrough), C=c(mean(oralThrough), mean(ivThrough)), U=c(upperOralThrough, upperIVThrough))
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(50,145)
 p + labs(title = "Order Throughput Times", x = "Order Type", y="Time (min)")
 png("ThroughputCIs.png")
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
[…]

### 2019-12-07 Mayo/Largest Queue/data/CI Longest.R

@@ -1,5 +1,5 @@
-#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Largest Queue/data")
-setwd("~/Desktop/Capstone/Mayo/Largest Queue/data")
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Largest Queue/data")
+#setwd("~/Desktop/Capstone/Mayo/Largest Queue/data")
 rm(list = ls())
 zstar <- qnorm(.975)
 duration <- 12*60
@@ -107,14 +107,15 @@ delta <- zstar*s/sqrt(length(dispQ))
 
 ### Queue Length intervals:
 df <- data.frame(x=c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"), L=c(lowerEntryQ,lowerEntryVerQ, lowerOralFillQ, lowerIVFillQ, lowerFillVerQ, lowerDispQ), C=c(mean(entryQ), mean(entryVerQ), mean(oralFillQ), mean(ivFillQ),mean(fillVerQ), mean(dispQ)), U=c(upperEntryQ, upperEntryVerQ, upperOralFillQ, upperIVFillQ, upperFillVerQ, upperDispQ))
+df$x <- factor(df$x, levels = c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"))
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 png("QueueCIs.png")
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 dev.off()
 
@@ -238,12 +239,12 @@ delta <- zstar*s/sqrt(length(ivThrough))
 df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralThrough,lowerIVThrough), C=c(mean(oralThrough), mean(ivThrough)), U=c(upperOralThrough, upperIVThrough))
[…]

### 2019-12-07 Mayo/PharmVer/data/CI Prof.R

@@ -1,5 +1,5 @@
-#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/PharmVer/data")
-setwd("~/Desktop/Capstone/Mayo/PharmVer/data")
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/PharmVer/data")
+#setwd("~/Desktop/Capstone/Mayo/PharmVer/data")
 rm(list = ls())
 zstar <- qnorm(.975)
 duration <- 12*60
@@ -107,14 +107,15 @@ delta <- zstar*s/sqrt(length(dispQ))
 
 ### Queue Length intervals:
 df <- data.frame(x=c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"), L=c(lowerEntryQ,lowerEntryVerQ, lowerOralFillQ, lowerIVFillQ, lowerFillVerQ, lowerDispQ), C=c(mean(entryQ), mean(entryVerQ), mean(oralFillQ), mean(ivFillQ),mean(fillVerQ), mean(dispQ)), U=c(upperEntryQ, upperEntryVerQ, upperOralFillQ, upperIVFillQ, upperFillVerQ, upperDispQ))
+df$x <- factor(df$x, levels = c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"))
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 png("QueueCIs.png")
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 dev.off()
 

### 2019-12-07 Mayo/VMax Priority/data/CI Smart.R

@@ -1,5 +1,5 @@
-#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/VMax Priority/data")
-setwd("~/Desktop/Capstone/Mayo/VMax Priority/data")
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/VMax Priority/data")
+#setwd("~/Desktop/Capstone/Mayo/VMax Priority/data")
 rm(list = ls())
 zstar <- qnorm(.975)
 duration <- 12*60
@@ -107,14 +107,15 @@ delta <- zstar*s/sqrt(length(dispQ))
 
 ### Queue Length intervals:
 df <- data.frame(x=c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"), L=c(lowerEntryQ,lowerEntryVerQ, lowerOralFillQ, lowerIVFillQ, lowerFillVerQ, lowerDispQ), C=c(mean(entryQ), mean(entryVerQ), mean(oralFillQ), mean(ivFillQ),mean(fillVerQ), mean(dispQ)), U=c(upperEntryQ, upperEntryVerQ, upperOralFillQ, upperIVFillQ, upperFillVerQ, upperDispQ))
+df$x <- factor(df$x, levels = c("Entry", "Entry Verification", "Oral Fill", "IV Fill", "Fill Verification", "Dispense"))
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 png("QueueCIs.png")
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(0,15)
 p + labs(title = "Average Queue Length", x = "Queue", y="Average Length")
 dev.off()
 

### 2019-12-08 Mayo/Final Draft/Draft.tex
PNG, axes fixed
Worked a little at work lol

--- 2019-12-03 Mayo/Rough Draft/Draft.tex
@@
 %*******************************************************************%
-\title{\bf Mayo Case Study Rough Draft\\
+\title{\bf Mayo Pharmacy Optimization Case Study\\
 \large Using Discrete Event Simulation}  % Supply information
@@
 \setcounter{page}{2}                    % make it start with "ii"
-\tableofcontents                        % Print table of contents
+%\tableofcontents                        % Print table of contents
 \newpage
@@
 \pagenumbering{arabic}                  % Start text with arabic 1
+Prescription medication is becoming increasingly commonplace in the United States.
+In 2013, the average number of prescriptions per capita was $12.2$, up from $9$ in 1998 [CITE BOTH].
+With this trend in preccription usage on the rise still, pharmacies are becoming an ever greater presence in the lives of americans.
+As such, pharmacies need to adapt to deal with increasing numbers of orders, as well as increasing the speed and accuracy at which they fill orders, in order to remain competitive in an increasingly saturated landscape of pharmacies.
+Consequently, pharmacies must adapt their methodologies and staffing reqirements in order to maximimize the numebr of orders filled and minimize the wait time and employee idle times.
+Obviously, testing multiple different prioritizations and staffing numbers is both expensive and time consuming, so we shall consider a discrete event simulation approach.
 In this case study, we are tasked with both modeling and optimizing the workflow for a pharmacy based on samples of data regarding task duration and incoming order frequency.
@@
 With these optimizations, we should be able to develop a sense of what makes the pharmacy run more efficiently, as well as an idea of what variables could be changed to further increase the accuracy of our simulation, as well as improve the pharmacy's function.
-\section*{Methods}
-\addcontentsline{toc}{section}{Methods}
-In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy.
-This workflow is tied to both legal regulations as well as potentially company specific guidelines.
-This workflow will form the backbone for our simulations main loop.
-The second stage of development is centered around identifying the distributions from the time sample data provided.
-In order to run the simulation, we need to know the distributions that each time variable comes from.
-Finally, we run the simulation and report statistical analysis on the results.
-%In order to effectively model and optimize the workflow in this pharmacy, we consider the given scenario, and how we might optimize it.
-As described, there are essentially no guidelines in place to speed up process workflow, which we will find dramatically affects the overall performance.
-As a pharmacy, we assume that maximizing both the number of prescriptions and the speed at which they are filled is paramount to the public image as well as its financial success.
-\subsection*{Process Workflow}
-\addcontentsline{toc}{subsection}{Process Workflow}
-To begin, we consider the basic workflow.
-As stated, due to regulations, pharmacists are able to perform tasks that technicians are unable to.
-Ignoring the IV technician for the time being as its task is isolated from the main workflow, the task breakdown is as follows:
-\begin{table}[H]
+\section*{Background}
+\addcontentsline{toc}{section}{Background}
+In our prototypical example, there are six basic tasks in the workflow tied to the two different types of orders, oral and IV: order entry, entry verification, oral fill, iv fill, fill verification, and dispensing through the window.
+In addition to these tasks, there are two different classes of employee [Pharmacist and Technician], who are constrained as to which task they may perform due to both legal regulations as well as potentially company specific guidelines.
+These regulations dictate that of the tasks, the verification tasks can only be performed by the pharmacists, while the remaining 3 tasks can be performed by both pharmacists and technicians.
+A breakdown of this hienarchy follows in Table \ref{table:tasks}, with pharmacist specific tasks highlighted in red.
+\begin{table}[h]
 \centering
@@
 \end{table}
+The workflow of this pharmacy follows a fairly linear task order as one might expect from the tasks named above, and is illustrated graphically in Figure \ref{fig:flowchart}.
+\begin{figure}[h]
+\centering
+\includegraphics[scale=.5]{Flowchart.png}
+\caption{Pharmacy workflow by task position noting which tasks are pharmacist only.}
+\label{fig:flowchart}
+\end{figure}
+We see that the workflow only diverges from being liear at the fill stage of the process, and this is due to the fact that one employee is solely tasked with filling IV orders in isolation.
+\section*{Methods}
+\addcontentsline{toc}{section}{Methods}
+In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy.
+This  This workflow will form the backbone for our simulations main loop.
+The second stage of development is centered around identifying the distributions from the time sample data provided.
+In order to run the simulation, we need to know the distributions that each time variable comes from.
+Finally, we run the simulation and report statistical analysis on the results.
+%In order to effectively model and optimize the workflow in this pharmacy, we consider the given scenario, and how we might optimize it.
+As described, there are essentially no guidelines in place to speed up process workflow, which we will find dramatically affects the overall performance.
+As a pharmacy, we assume that maximizing both the number of prescriptions and the speed at which they are filled is paramount to the public image as well as its financial success.
+\subsection*{Process Workflow}
+\addcontentsline{toc}{subsection}{Process Workflow}
+To begin, we consider the basic workflow.
+As stated, due to regulations, pharmacists are able to perform tasks that technicians are unable to.
+Ignoring the IV technician for the time being as its task is isolated from the main workflow, the task breakdown is as follows:
+
 As illustrated in Table \ref{table:tasks}, we see that pharmacists are capable of doing all steps in the workflow, while the technicians may only perform three of the five.

### 2019-12-09 Mayo/Final Draft/Draft.tex
chuggin along

--- 2019-12-03 Mayo/Rough Draft/Draft.tex
@@
 \pagenumbering{arabic}                  % Start text with arabic 1
-In this case study, we are tasked with both modeling and optimizing the workflow for a pharmacy based on samples of data regarding task duration and incoming order frequency.
-In addition to the sample data for the pharmacy, we are also given a brief overview of the basic workflow for the pharmacy.
-Using this information, we shall begin by constructing a discrete event simulation in C++ to test our so called ``control" case, i.e.
+The use of prescription medication is becoming increasingly commonplace in the United States.
+In 2013, the average number of prescriptions taken per capita was $12.2$, up from $9$ in 1998 \cite{georgetown}\cite{statistica}.
+With this trend in preccription usage on the rise still, pharmacies are becoming an ever greater presence in the lives of most americans.
+As such, pharmacies need to adapt to deal with increasing numbers of orders, as well as increasing the speed and accuracy at which they fill orders in order to remain competitive in an increasingly saturated landscape of pharmacies.
+Consequently, pharmacies must adapt their methodologies and staffing reqirements in order to optimize employee effectiveness and efficiency.
+Obviously, testing multiple different optimization schemas is both expensive and time consuming, so pharmacies have begun to consider a discrete event simulation approaches to optimization.
+In this case study, we are tasked with both modeling and optimizing the workflow for a protoype pharmacy based on samples of data regarding task duration and incoming order frequency.
+In addition to the sample data for the pharmacy, we are also given a brief overview of the basic work process order.
+Using this information, we shall construct a discrete event simulation model in C++ to analyze our so called ``control" case, i.e.
 the pharmacy described by the basic information.
@@
 \begin{enumerate}
-\item Optimizing task priority within the workflow (Picking the best queue to pull from)
-\item Optimizing staff breakdown (Best number of pharmacists vs. technicians to employ)
+\item Optimizing task priority within the workflow (picking the best task to pull from)
+\item Optimizing staff breakdown (profit optimizing number of pharmacists vs. technicians to employ)
 \end{enumerate}
-With these optimizations, we should be able to develop a sense of what makes the pharmacy run more efficiently, as well as an idea of what variables could be changed to further increase the accuracy of our simulation, as well as improve the pharmacy's function.
-\section*{Methods}
-\addcontentsline{toc}{section}{Methods}
-In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy.
-This workflow is tied to both legal regulations as well as potentially company specific guidelines.
-This workflow will form the backbone for our simulations main loop.
-The second stage of development is centered around identifying the distributions from the time sample data provided.
-In order to run the simulation, we need to know the distributions that each time variable comes from.
-Finally, we run the simulation and report statistical analysis on the results.
-%In order to effectively model and optimize the workflow in this pharmacy, we consider the given scenario, and how we might optimize it.
-As described, there are essentially no guidelines in place to speed up process workflow, which we will find dramatically affects the overall performance.
-As a pharmacy, we assume that maximizing both the number of prescriptions and the speed at which they are filled is paramount to the public image as well as its financial success.
-\subsection*{Process Workflow}
-\addcontentsline{toc}{subsection}{Process Workflow}
-To begin, we consider the basic workflow.
-As stated, due to regulations, pharmacists are able to perform tasks that technicians are unable to.
-Ignoring the IV technician for the time being as its task is isolated from the main workflow, the task breakdown is as follows:
+With these optimizations, we hope to develop a sense of what changes could increase the efficiency of the pharmacy, as well as an idea of what variables could be manipulated to further increase the accuracy of our simulation, and improve the pharmacy's function.
+\section*{Background}
+\addcontentsline{toc}{section}{Background}
+In our prototypical example, there are two types of prescription orders that the pharmacy recieves, oral and IV.
+Within the pharmacy itself, there are two different classes of employee, pharmacists and technicians, who are constrained as to which task they may perform due to legal regulations.
+As the pharmacy recieves orders, they are entered into the system by a technician.
+Once the order is in the system, it is verified by a pharmacust, and passed to the appropriate area to be prepared by technicians.
+Upon being filled, the order is again verified by a pharmacist, and then dispensed to the consumer by a technician.
+As such, we see that there are six basic tasks in the workflow tied to the two different types of orders: order entry, entry verification, oral or IV preparation, filled order verification, and distribution through the window.
+As noted before, regulations exist to limit what tasks non-pharmacist level employees may perform.
+These regulations dictate that of the tasks, the verification tasks may only be performed by the pharmacists, while the remaining tasks can be performed by both pharmacists and technicians.
+A breakdown of this hienarchy follows in Table \ref{table:tasks}, with pharmacist specific tasks highlighted in red.
+It should also be noted that in our control case, there exists an additional sub-type of technician, whose sole purpose is to prepare IV orders in an isolated room.
+This will be explored in greater detail below.
 \begin{table}[H]
@@
 \end{table}
-As illustrated in Table \ref{table:tasks}, we see that pharmacists are capable of doing all steps in the workflow, while the technicians may only perform three of the five.
-This is to say that $Task_{Technician}\subset Task_{Pharmacist}$.
-With this distinction in mind, we consider the flowchart contained in Figure \ref{fig:flowchart}, which describes the process workflow graphically.
+With this task breakdown in hand, we consider a graphical representation of the path an order takes within the pharmacy, specifically linked to the tasks described above.
+Looking at Figure \ref{fig:flowchart}, we see that the process of filling an order is fairly linear, with the only fork in the workflow occuring after the entry verification step.
+This fork is due to the necessity of establishing an order's type (Oral vs.
+IV) so it may be put in the appropriate filling queue.
+In our control pharmacy, all IV orders are filled in an isolated room by an ``IV Technician" who only prepares IV prescriptions, and does not assist with any other tasks in the workflow.
 \begin{figure}[H]
@@
 \end{figure}
-Here we may clearly see that with the exception of the IV Fill step, the workflow is fairly linear, which will make the simulation fairly simple in theory, allowing for more advanced optimizations.
-The basic workflow is:
-\begin{enumerate}
-\item Order comes in and enters the Entry Task Queue
-\item Employee enters the order, order enters the Entry Verification Queue
-\item Pharmacist verifies the entry, order enters the Fill Queue
-\item Employee fills the order, order enters the Fill Verification Queue
-\item Pharmacist verifies the fill, order enters the Dispense Queue
-\item Employee dispenses the order through the window
-\end{enumerate}
-There is a fork in the process workflow after step 3, where the order's type (Oral vs.
-IV) must be checked so it may be put in the appropriate filling queue, however this does not affect the linearity of the process at this step.
-With this workflow defined, we consider the next step of building our simulation, identifying the distributions from which we sample times from.
+With this workflow defined, we consider the next step of building our simulation, identifying the durations of the different tasks.
 \section*{Distribution Identification}
 \addcontentsline{toc}{section}{Distribution Identification}
-As we have identified in the workflow above, there are essentially six pivotal points that will have times associated with them: Entry, Entry Verification, Oral Drug Preparation, IV Drug Preparation, Order Prep Verification, and Distribution.
-In addition to these six points, we are also aware of the fact that the times between incoming oral and IV orders come from different distributions.
-As part of the given data, we have a sample of the times from each of these eight different categories, ranging in size from 34 to 60 observations.
+As noted above, there are essentially six pivotal tasks that we must establish the duration of in order to effectively perform an analysis.
+In addition to these tasks, we are also aware of the fact that the times between incoming oral and IV orders come from different distributions.
+As part of the given data, we have samples of the completion times of each of these eight different categories, ranging in size from 34 to 60 observations.
 Using each of these samples, we shall construct Cullen and Frey graphs to attempt to isolate the correct distributions.
+These graphs will take the skewness and kurtosis of our task time samples and help to narrow the number of potential distibutions.
 With this set of hypothetical distributions in hand, we shall fit the data and test the goodness of fit statistic to identify the best fit.
@@
 \end{figure}
-Looking at these plots, it appears that the data comes from a normal population, and the Cullen and Frey plot supports this.
+Looking at Figure \ref{fig:orderEntryHistCullen}, it appears that the data comes from a normal population, and the Cullen and Frey plot supports this.
 For completeness, we shall test this sample as being from a normal distribution as well as a gamma and log-normal distribution.
@@
 & Normal Fit & Gamma Fit & log-normal Fit \\\hline
-Kolomogorov-Smirnov & \cellcolor{green!25}0.05172573 & 0.07123761 & 0.08600921\\\hline
-Anderson Darling & \cellcolor{green!25}0.14921512 & 0.28840960 & 0.45314418\\\hline
+%Kolomogorov-Smirnov & \cellcolor{green!25}0.05172573 & 0.07123761 & 0.08600921\\\hline
+%Anderson Darling & \cellcolor{green!25}0.14921512 & 0.28840960 & 0.45314418\\\hline
 AIC & \cellcolor{green!25}219.8769 & 221.3501 & 223.2712\\\hline
@@
 With these distributions in hand, we can begin the construction of the base case of the simulation.
+
+from which we sample times from.
+The workflow of this pharmacy follows a fairly linear task order as one might expect from the tasks named above, and is illustrated graphically in Figure 
+It is important to note that for our base case, we will not consider the failure rate of tasks,
+Using this flowchart, we see that there is
+\section*{Methods}
+\addcontentsline{toc}{section}{Methods}
+In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy.
+This  This workflow will form the backbone for our simulations main loop.
+The second stage of development is centered around identifying the distributions from the time sample data provided.
+In order to run the simulation, we need to know the distributions that each time variable comes from.
+Finally, we run the simulation and report statistical analysis on the results.
+%In order to effectively model and optimize the workflow in this pharmacy, we consider the given scenario, and how we might optimize it.
+As described, there are essentially no guidelines in place to speed up process workflow, which we will find dramatically affects the overall performance.
+As a pharmacy, we assume that maximizing both the number of prescriptions and the speed at which they are filled is paramount to the public image as well as its financial success.
+
 \section*{First Layer of Optimization}
@@
 \begin{thebibliography}{9}
+\bibitem{georgetown} ``Prescription Drugs.” \textit{Health Policy Institute}, \url{hpi.georgetown.edu/rxdrugs/}.
+\bibitem{statistica} Statista Research Department.
+``U.S.
+Average Number of Prescriptions per Capita.” \textit{Statista}, 9 Aug.
+2019, \url{www.statista.com/statistics/315476/prescriptions-in-us-per-capita-by-age-group/}.
 %\bibitem{light} J.

### 2019-12-12 Mayo/Final Draft/Draft.tex
Arrived at workable final draft. Started trying to implement mail orders

@@
 The use of prescription medication is becoming increasingly commonplace in the United States.
-In 2013, the average number of prescriptions taken per capita was $12.2$, up from $9$ in 1998 \cite{georgetown}\cite{statistica}.
-With this trend in preccription usage on the rise still, pharmacies are becoming an ever greater presence in the lives of most americans.
+In 2013, the average number of prescriptions taken per person was $12.2$, up from $9$ in 1998, a $136\%$ increase over 15 years \cite{georgetown}\cite{statistica}.
+With this trend in prescription usage continuing to rise, pharmacies are becoming an ever greater presence in the lives of most Americans.
 As such, pharmacies need to adapt to deal with increasing numbers of orders, as well as increasing the speed and accuracy at which they fill orders in order to remain competitive in an increasingly saturated landscape of pharmacies.
-Consequently, pharmacies must adapt their methodologies and staffing reqirements in order to optimize employee effectiveness and efficiency.
-Obviously, testing multiple different optimization schemas is both expensive and time consuming, so pharmacies have begun to consider a discrete event simulation approaches to optimization.
-In this case study, we are tasked with both modeling and optimizing the workflow for a protoype pharmacy based on samples of data regarding task duration and incoming order frequency.
-In addition to the sample data for the pharmacy, we are also given a brief overview of the basic work process order.
-Using this information, we shall construct a discrete event simulation model in C++ to analyze our so called ``control" case, i.e.
+Consequently, pharmacies must adapt their methodologies and staffing requirements in order to optimize efficiency and cost.
+Obviously, testing different optimization schemas is both expensive and time consuming, so pharmacies have begun to consider computer simulation approaches to optimization as a more cost effective solution.\\\hfill\\
+In this case study, we are tasked with both modeling and optimizing the workflow for a prototype pharmacy based on samples of data regarding task duration and incoming order frequency.
+In addition to the sample data for the pharmacy, we are also given a brief overview of the basic order fulfillment process.
+Using this information, we shall construct a discrete event simulation model to analyze our so called ``control" case, i.e.
 the pharmacy described by the basic information.
-Once this simulation is running and tested, we shall attack the optimization on two fronts.
+Once this simulation is running and tested, we shall attempt to improve the efficiency over the base case.
+In order to achieve this goal, we shall attack the optimization on two fronts.
 \begin{enumerate}
@@
 \addcontentsline{toc}{section}{Background}
-In our prototypical example, there are two types of prescription orders that the pharmacy recieves, oral and IV.
-Within the pharmacy itself, there are two different classes of employee, pharmacists and technicians, who are constrained as to which task they may perform due to legal regulations.
-As the pharmacy recieves orders, they are entered into the system by a technician.
-Once the order is in the system, it is verified by a pharmacust, and passed to the appropriate area to be prepared by technicians.
+In our prototypical example, there are two types of prescription orders that the pharmacy receives, oral and IV, which are handled by two different classes of employee, pharmacists and technicians, who are constrained as to which task they may perform due to legal regulations.
+In our prototype pharmacy, the proposed process is as follows: As the pharmacy receives orders, they are entered into the system by a technician.
+Once the order is in the system, it is verified by a pharmacist, and passed to the appropriate area to be prepared by technicians.
 Upon being filled, the order is again verified by a pharmacist, and then dispensed to the consumer by a technician.
-As such, we see that there are six basic tasks in the workflow tied to the two different types of orders: order entry, entry verification, oral or IV preparation, filled order verification, and distribution through the window.
+As such, we see that there are six basic tasks in the workflow tied to the two different types of orders: order entry, entry verification, oral or IV preparation, prepared order verification, and distribution through the window.
 As noted before, regulations exist to limit what tasks non-pharmacist level employees may perform.
 These regulations dictate that of the tasks, the verification tasks may only be performed by the pharmacists, while the remaining tasks can be performed by both pharmacists and technicians.
-A breakdown of this hienarchy follows in Table \ref{table:tasks}, with pharmacist specific tasks highlighted in red.
+A breakdown of this hierarchy follows in Table \ref{table:tasks}, with pharmacist specific tasks highlighted in red.
 It should also be noted that in our control case, there exists an additional sub-type of technician, whose sole purpose is to prepare IV orders in an isolated room.
@@
 \centering
-\begin{tabular}{|c||c|}
+\begin{tabular}{|c||c|c|}
 \hline
-Technician & Pharmacist\\\hline\hline
-Order Entry & Order Entry \\\hline
-& \cellcolor{red!25}Entry Verification \\\hline
-Drug Preparation & Drug Preparation\\\hline
-& \cellcolor{red!25}Preparation Verification\\\hline
-Distribution & Distribution\\\hline
+Pharmacist & Technician & IV Technician\\\hline\hline
+Order Entry & Order Entry &\\\hline
+\cellcolor{red!25}Entry Verification && \\\hline
+Oral Drug Preparation & Oral Drug Preparation & \cellcolor{blue!25}IV Drug Preparation\\\hline
+\cellcolor{red!25}Preparation Verification &&\\\hline
+Distribution & Distribution&\\\hline
 \end{tabular}
@@
 With this task breakdown in hand, we consider a graphical representation of the path an order takes within the pharmacy, specifically linked to the tasks described above.
-Looking at Figure \ref{fig:flowchart}, we see that the process of filling an order is fairly linear, with the only fork in the workflow occuring after the entry verification step.
+Looking at Figure \ref{fig:flowchart}, we see that the process of filling an order is fairly linear, with the only fork in the workflow occurring after the entry verification step.
 This fork is due to the necessity of establishing an order's type (Oral vs.
@@
 \end{figure}
+For our control case, we operate under the assumption that no tasks in this process have any issues with failure or delays.
+This is obviously a simplified case, but we shall construct the simulation in such a way that including it would be quite simple to do.
 With this workflow defined, we consider the next step of building our simulation, identifying the durations of the different tasks.
@@
 \addcontentsline{toc}{section}{Distribution Identification}
-As noted above, there are essentially six pivotal tasks that we must establish the duration of in order to effectively perform an analysis.
+As noted above, there are six pivotal tasks that we must establish the duration of in order to effectively perform an analysis.
 In addition to these tasks, we are also aware of the fact that the times between incoming oral and IV orders come from different distributions.
-As part of the given data, we have samples of the completion times of each of these eight different categories, ranging in size from 34 to 60 observations.
+As part of the supplied data, we have samples of the completion times of each of these eight different categories, ranging in size from 34 to 60 observations.
 Using each of these samples, we shall construct Cullen and Frey graphs to attempt to isolate the correct distributions.
-These graphs will take the skewness and kurtosis of our task time samples and help to narrow the number of potential distibutions.
+These graphs will take the skewness and kurtosis of our task time samples and plot a point in the $skew^2/kurtosis$ plane which can then be mapped to potential distributions based on theoretical values for each distribution.
 With this set of hypothetical distributions in hand, we shall fit the data and test the goodness of fit statistic to identify the best fit.
@@
 \addcontentsline{toc}{subsection}{Order Entry}
-To begin, we consider the data provided for the order entry times. Using $R$, we construct both a histogram and a Cullen and Frey graph (Figure \ref{fig:orderEntryHistCullen}),
+To begin, we consider the data provided for the order entry times. Using $R$, we construct both a histogram and a Cullen and Frey graph (Figure \ref{fig:orderEntryHistCullen}).
 \begin{figure}[H]
@@
 \end{figure}
-Looking at Figure \ref{fig:orderEntryHistCullen}, it appears that the data comes from a normal population, and the Cullen and Frey plot supports this.
-For completeness, we shall test this sample as being from a normal distribution as well as a gamma and log-normal distribution.
-Once the data has been fit with each of these distributions, $R$ is used to compute a goodness of fit statistic for each model, and these results follow:
+Looking at the histogram of order entry data in Figure \ref{fig:orderEntryHistCullen}, it appears that the data comes from a normal population, and the Cullen and Frey plot supports this.
+For completeness, we shall test this sample as being from a normal distribution as well as a gamma and log-normal distribution, as these distributions also appear to be good potential fits in the Cullen and Frey graph.
+Once the data has been fit with each of these distributions, $R$ is used to compute a goodness of fit statistic, the AIC, for each model.
+The AIC is a sort of score for a model, which weights the accuracy of a fitted model against its own complexity.
+By construction, this score decreases for better models, and increases when models become too complex.
+This prevents over-fitting and reliance on sample data values.
+With this in mind, we consider the AIC scores for each of the three potential distributions for order entry below in Table \ref{table:entryGOF}
 \begin{table}[H]
@@
 \end{table}
-As highlighted in Table \ref{table:entryGOF}, by treating this sample as part of a larger normal population, we produce the smallest goodness-of-fit statistics, implying the best fit.
+As highlighted in Table \ref{table:entryGOF}, by treating this sample as part of a larger normal population, we produce the smallest AIC score, implying the best fit.
 As such, we shall treat this as the correct distribution for sampling purposes in our simulation.
 The relevant distribution statistics follow,
-\[\text{Order Entry}\sim N(\mu=9.873784,\ \sigma=2.095579)\]
+\[\text{Order Entry}\sim \text{Normal}(\mu=9.873784,\ \sigma=2.095579)\]
 \subsection*{Remaining Distributions}
@@
 \begin{align*} 
-\text{Entry Verification Times} &\sim U(1.2726,\ 3.4059)\\
+\text{Entry Verification Times} &\sim \text{Uniform}(1.2726,\ 3.4059)\\
 \text{Oral Preparation Times} &\sim \text{Lognormal}(\mu=2.99140489,\ \sigma=.06300657)\\
@@
 \text{Preparation Verification Times} &\sim \text{Weibull}(shape=2.911269,\ scale=2.143830)\\
-\text{Dispense Times} &\sim N(\mu=2.947898,\ \sigma=0.566620)\\
+\text{Dispense Times} &\sim \text{Normal}(\mu=2.947898,\ \sigma=0.566620)\\
 \text{Oral Incoming Times} &\sim \text{Exponential}(\lambda = 0.129199 )\\
@@
 With these distributions in hand, we can begin the construction of the base case of the simulation.
-
-from which we sample times from.
-The workflow of this pharmacy follows a fairly linear task order as one might expect from the tasks named above, and is illustrated graphically in Figure 
-It is important to note that for our base case, we will not consider the failure rate of tasks,
-Using this flowchart, we see that there is
-\section*{Methods}
-\addcontentsline{toc}{section}{Methods}
-In order to construct our discrete event simulation in C++, we must first identify the basic workflow in the pharmacy.
-This  This workflow will form the backbone for our simulations main loop.
-The second stage of development is centered around identifying the distributions from the time sample data provided.
-In order to run the simulation, we need to know the distributions that each time variable comes from.
-Finally, we run the simulation and report statistical analysis on the results.
 %In order to effectively model and optimize the workflow in this pharmacy, we consider the given scenario, and how we might optimize it.
@@
 As a pharmacy, we assume that maximizing both the number of prescriptions and the speed at which they are filled is paramount to the public image as well as its financial success.
-
-\section*{First Layer of Optimization}
-\addcontentsline{toc}{section}{First Layer of Optimization}
-To begin our two pronged optimization efforts, we begin by trying to improve the task logic. To begin we model the base case.
-\subsection*{Construction of the Base Case}
-\addcontentsline{toc}{subsection}{Base Case}
+\section*{Construction of the Base Case}
+\addcontentsline{toc}{section}{Base Case}
 To construct the simulation of the pharmacy, the programming language C++ was used due to its speed, as well as object oriented structure.
-This structure allowed for maximal customization of our data.
-To build the simulation, two unique class objects were written to house the details required for a given order, as well as each of the employees.
+This structure allowed for maximal customization of our data, enabling the collection of many different statistics, which we report below.
+To build the simulation, two unique class objects were written to house the details required for a given prescription, as well as each of the employees.
 Within these classes relevant structures for computing the idle times and other important statistics are included and updated throughout the simulation.
@@
     Construct workers and place in idle pool
-    Calculate relevant duration times in queues from distribution data
+    Fill queues with sample duration times from distribution data
     while(!endOfSim){
-        Check and see if new order enters in this time step
+        Check and see if a new order enters in this time step
         Check if any active workers have finished task
@@
 It is important to note here the job assignment of the base case.
-In this model, when job assignment begins for each employee, each non-empty job is put into a pool and randomly chosen with no priority.
+In this model, when job assignment begins for each employee, each non-empty task queue is put into a pool and randomly chosen with no priority.
 So, a pharmacist has an equal probability of doing a pharmacist only task or a technician level task.
 Changing this assignment will become a cornerstone of our optimization efforts.
-\subsubsection*{Base Case Results}
-Using the parameters above, the following 95\% confidence intervals were obtained,
+To further remove any bias in the model, the idle worker pool is shuffled randomly before each task assignment step in the simulation.
+This will help to alleviate any artificial effects on worker idle times.
+\subsection*{Base Case Results}
+Running a simulation using the parameters above, we use $R$ to analyze the output data, and obtain the following 95\% confidence intervals for various performance indicators.\\\hfill\\
+First, we consider the numbers of orders that the pharmacy receives on an average day,
 \begin{align*}
-\text{Oral Incoming} &= [91.6024,\ 98.06426] && \text{Number of Orders}\\
-\text{IV Incoming} &= [42.47068,\ 47.12932] && \text{Number of Orders}\\\\
-\text{Entry Queue} &= [0.4310875,\ 0.6114125] && \text{Number of Orders}\\
-\text{Entry Verification Queue} &= [7.997571,\ 12.58185] && \text{Number of Orders}\\
-\text{Oral Fill Queue} &= [0.1240198,\ 0.1679247] && \text{Number of Orders}\\
-\text{IV Fill Queue} &= [0.079518,\ 0.1349264] && \text{Number of Orders}\\
-\text{Fill Verification Queue} &= [3.427384,\ 5.809907] && \text{Number of Orders}\\
-\text{Dispense Queue} &= [0.1735777,\ 0.2304964] && \text{Number of Orders}\\\\
-\text{Oral Filled} &= [67.26063,\ 70.40604] && \text{Number of Orders}\\
-\text{IV Filled} &= [32.72671,\ 37.33995] && \text{Number of Orders}\\\\
-\text{Pharmacist Idle Time} &= [2.811366,\ 4.692106] && \text{Percent of Total Time}\\
-\text{Technician Idle Time} &= [17.50725,\ 20.02053] && \text{Percent of Total Time}\\
-\text{IV Technician Idle Time} &= [67.62806,\ 71.53167] && \text{Percent of Total Time}\\\\
-\text{Oral Throughput Times} &= [105.1253,\ 136.618] && \text{Minutes}\\
-\text{IV Throughput Times} &= [91.9162,\ 127.0587] && \text{Minutes}\\
-\text{Oral Wait Times} &= [68.11842,\ 99.61155] && \text{Minutes}\\
-\text{IV Wait Times} &= [69.27191,\ 104.3281] && \text{Minutes}\\\\
+\text{Oral Incoming} &= [91.6024,\ 98.06426] && \text{(Number of Orders)}\\
+\text{IV Incoming} &= [42.47068,\ 47.12932] && \text{(Number of Orders)}\\
 \end{align*}
+We see that we expect just shy of $100$ oral prescriptions, and just shy of $50$ IV orders per day.
+This indeed aligns with the expected values given the exponential distribution fit that was assigned to them for time between orders.\\\hfill\\
+Next, we consider the average queue lengths for each task in the workflow,
+\begin{align*}
+\text{Entry Queue} &= [0.4310875,\ 0.6114125] && \text{(Number of Orders)}\\
+\text{Entry Verification Queue} &= [7.997571,\ 12.58185] && \text{(Number of Orders)}\\
+\text{Oral Fill Queue} &= [0.1240198,\ 0.1679247] && \text{(Number of Orders)}\\
+\text{IV Fill Queue} &= [0.079518,\ 0.1349264] && \text{(Number of Orders)}\\
+\text{Fill Verification Queue} &= [3.427384,\ 5.809907] && \text{(Number of Orders)}\\
+\text{Dispense Queue} &= [0.1735777,\ 0.2304964] && \text{(Number of Orders)}\\
+\end{align*}
+These values tell us how many prescription orders were sitting idle at each stage of the fulfillment process, helping us identify potential bottleneck points.\\\hfill\\
+Next, we consider arguably the most valuable statistic to a pharmacy from a business standpoint, the number of filled orders. 
+\begin{align*}
+\text{Oral Filled} &= [67.26063,\ 70.40604] && \text{(Number of Orders)}\\
+\text{IV Filled} &= [32.72671,\ 37.33995] && \text{(Number of Orders)}\\
+\end{align*}
+We see here that we expect to fill about $70\%-75\%$ of all incoming orders.
+To see whether there is room for improvement in this number, we consider whether the amount of time for orders from start to finish, the ``throughput", as well as the amount of time the order sits idle leave room for improvement.
+\begin{align*}
+\text{Oral Throughput Times} &= [105.1253,\ 136.618] && \text{(Minutes)}\\
+\text{IV Throughput Times} &= [91.9162,\ 127.0587] && \text{(Minutes)}\\
+\text{Oral Wait Times} &= [68.11842,\ 99.61155] && \text{(Minutes)}\\
+\text{IV Wait Times} &= [69.27191,\ 104.3281] && \text{(Minutes)}\\
+\end{align*}
+Here, we see that it takes an average of around two hours for an order to be filled, and over $70\%$ of this time is spent idle waiting to be selected from the queue.
+This would lead us to believe that there are better systems that could be implemented to increase the fill speed, and consequently the number of orders filled.\\\hfill\\
+While knowing how long and how fast the orders are moving in the model is important, it is equally important for the pharmacy to measure the efficiency and use of its employees.
+Below, we see the estimations for how long each type of employee is idle during the simulations, expressed as a percent of the total time.
+\begin{align*}
+\text{Pharmacist Idle Time} &= [2.811366,\ 4.692106] && \text{(Percent of Total Time)}\\
+\text{Technician Idle Time} &= [17.50725,\ 20.02053] && \text{(Percent of Total Time)}\\
+\text{IV Technician Idle Time} &= [67.62806,\ 71.53167] && \text{(Percent of Total Time)}
+\end{align*}
+We see that as we might expect the IV technician is idle a majority of the time.
+This aligns with the restrictions of the job, as there are fewer IV orders received during the day, as well as the fact that the mean time to fill an IV order is under $6$ minutes.
+As such, there is rarely enough time for a new IV order to enter the fill queue before the technician is done with the previous task.
+This can also be seen above where the IV fill queue is noted to have incredibly small average lengths.\\\hfill\\
 While these intervals do provide important analysis on the data, a graphical interpretation of this data will help us to more accurately examine potential points of congestion in the model.
-Figure \ref{fig:baseQ} has box and whisker plots for each of the queues in the base case.
+Figure \ref{fig:baseQ} has box and whisker plots for each of the average queue lengths in the base case.
 \begin{figure}[H]
@@
 With the pharmacists choosing from all possible tasks equally, they can take work from the technicians, who cannot in return work from the verification tasks.
+This aligns with the estimated idle times from above, as we found the pharmacists to be idle significantly less than the technicians.
 Reducing this congestion will be the goal of our first optimization.
-*******Talk about idle times*******************
+\section*{First Layer of Optimization}
+\addcontentsline{toc}{section}{First Layer of Optimization}
+With the base case of the model constructed and analyzed, we begin the first of our two pronged optimization efforts, optimizing the job choice logic to increase throughput speed, and reduce idle time in the model.
 \subsection*{First Optimization: Lazy Pharmacists}
@@
 Under this scheme, the pharmacists will only do pharmacist specific tasks, leaving the technicians to do the remainder of the tasks.
+The hope is that by removing the pharmacists from the technician tasks that not only will the technician idle times be reduced, but also the lengths of the verification queues will be reduced as well.
 Running the simulation with the same parameters as the base case, under the new job choice logic yields some unexpected results.
@@
 \end{figure}
-Under the original schema, all queues were essentially empty except for the verification queues, while under our new schema all of the non-verification queues show increases.
+Under the original schema, all queues were essentially empty except for the verification queues, while under our new schema all of the non-verification queues show increases, most specifically the first and last steps of the fill process.
 Indeed we find that the average queue length for our new case is slightly larger than before,
@@
 Looking more closely into this idle time data, we see that the average idle time for a pharmacist in the new scheme is approximately $67\%$, which is clearly not an effective use of their time.
+Before looking to see if reducing the number of pharmacists in the model would help to reduce this idle percentage, we first consider the filled order results under this scheme.
+Figure \ref{fig:baseprofFill} shows us a comparison in throughput.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.35]{BaseFilledCIs.png}
+\includegraphics[scale=.35]{ProfFilledCIs.png}
+\caption{Base case (left) vs. Lazy Pharmacist (Right) average number of filled orders}
+\label{fig:baseprofFill}
+\end{figure}
+We see that in fact this method has reduced both the number of oral and IV orders that are filled over the duration of the simulation.
+It is likely not worth exploring further in terms of staffing optimizations as an ``over-staffed" run yielded worse results.
 As such, we seek to find a better process optimization.
@@
 \addcontentsline{toc}{subsection}{Largest Queue}
-Given that forcing the pharmacists to only pull from the verification tasks is hurting the efficiency of the model, we consider a new job assignment logic, choosing the largest possible task.
-So, a pharmacist will choose to take their next task from the largest of all 5 possible queues, while technicians may choose from the 3 technician level queues.
+Given that forcing the pharmacists to only pull from the verification tasks is hurting the efficiency of the model, we consider a new job assignment logic, choosing the most full task queue.
+So, a pharmacist will choose to take their next task from the largest of all five possible queues, while technicians may choose from the three technician level queues.
+This method should help to ensure that both employees and orders are moving as efficiently as possible as it favors maintaining the smallest possible net queue sizes.
 Running the simulation with the same parameters as the base case, under the new job choice logic yields results that are more aligned with what we would expect.
@@
 While these changes may seem somewhat small, consider now the mean throughput times between the two models.
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-We see that by choosing the longest queue as the next task, the average throughput time for an order is reduced by a factor of almost $30\%$, which seems fairly significant.
+We see that by choosing the longest queue as the next task, the average throughput time for an order is reduced by a factor of almost $30\%$.
+As we would expect, this also helps to reduce the average wait time for orders, as well as the idle times of the employees.
 While this method is clearly superior to the base case, we consider finally a combination of the Lazy Pharmacist and Longest Queue methods.
@@
 \addcontentsline{toc}{subsection}{Smart Method}
-As our final job assignment optimization we consider a sort of mixture between choosing the longest queue, and relegating the pharmacists to the verification queues.
+As our final job assignment optimization we consider a sort of mixture between choosing the longest queue and relegating the pharmacists to the verification queues.
 Namely, under this schema, the pharmacist will first check to see if any of the verification queues are non-empty, and if so, they will choose the largest one.
 Otherwise, they choose the largest from the remaining queues.
-The technicians remain unchanged from before.
+The technicians remain unchanged from before, always choosing a task from the largest queue.
 \begin{verbatim}
@@
 Again we implement this model with the basic parameters from before, getting again better results than before.
-Since we have established that the longest queue is our front-runner for the optimization, we shall use it as a basis for comparison for this smart method.
-First, we compare the base queue lengths,
+As before, we consider the comparison between the base case and the smart method queue lengths to begin to test whether we have achieved optimization.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=.35]{BaseQueueCIs.png}
+\includegraphics[scale=.35]{SmartQueueCIs.png}
+\caption{Base Case (left) vs. Smart Method (Right) average queue lengths}
+\label{fig:basevsmart}
+\end{figure}
+As with the longest queue method we see a significant reduction in the average queue length, going from $2.6475$ in the base case to $1.1869$ under the smart method.
+Since we have established that the longest queue is our front-runner for the optimization, we shall also use it as a basis for comparison for this smart method.
+Figure \ref{fig:longvsmart} contains the comparison between the average queue lengths for these two methods.
 \begin{figure}[H]
@@
 \includegraphics[scale=.35]{SmartQueueCIs.png}
-\caption{Largest Queue (left) vs. Smart Method (Right) average queue lengths}
+\caption{Longest Queue (Left) vs. Smart Method (Right) average queue lengths}
 \label{fig:longvsmart}
@@
 \[\overline{Length}_{Longest}=1.389 > 1.187 = \overline{Length}_{Smart}\]
-\[\overline{Throughput}_{Longest}=71.813 > 64.920 = \overline{Length}_{Smart}\]
+\[\overline{Throughput}_{Longest}=71.813 > 64.920 = \overline{Throughput}_{Smart}\]
 It would appear that we have achieved a slight increase in effectiveness with this new implementation, but it is hard to say given the relative magnitudes of the standard deviations in the data, thus further analysis is required.
@@
 \end{figure}
-We see from Figure \ref{fig:anovaBox} that there does seem to be a difference among the models, though it is hard to confirm visually.
-Running the ANOVA test on the null hypothesis of $\mu_i=\mu_j\ \forall i,j\in\text{Methods}$, we arrive at the $F$ statistic, $F=36.96\Rightarrow p<2\times10^{-16}$, which is highly significant.
-Given this $p$ value, we reject the null hypothesis in favor of the alternative, that there is a difference in at least one of the means.
+We see from Figure \ref{fig:anovaBox} that there does seem to be a difference among the models, though it is hard to confirm visually, especially for the longest queue and smart methods.
+Running the ANOVA test on the null hypothesis of $\mu_i=\mu_j\ \forall i,j\in\text{Methods}$, we arrive at the $F$ statistic,
+\[F=36.96\Rightarrow p<2\times10^{-16}\]
+which is highly significant.
+Given that this $p$ value is far less than our standard cutoff of $\alpha = 0.05$, we reject the null hypothesis in favor of the alternative, that there is a difference in at least one of the means.
 Given this result, we shall use $R$ to compute the Tukey honest significant differences between the means, whose results can be found in Table \ref{table:tukey}.
@@
 \end{table}
+The results in Table \ref{table:tukey} are essentially pairwise $t$-tests to compare the means of each methods oral throughput.
 Note, Table \ref{table:tukey} has two rows highlighted.
 These rows correspond to the differences between the base method and largest queue method, as well as the largest queue method to the smart method.
-Based on the table, we can draw the following conclusion comparing the different methods,
+Using our standard $\alpha=0.05$, we can draw the following conclusion comparing the different methods,
 \[\text{Smart $>$ Largest $>$ Base}\]
-Now that we have established an ``optimal" method, we now consider how best to improve efficiency in employees.
+Note, this alpha comparison does not require a Bonferroni correction, as $R$ computes the adjusted $p$-value to correct for the multiple comparisons taking place.
+From these results, we see that while the largest queue did provide significant improvement over the base case, the smart method provided a significant improvement over the largest method.
+As such, we shall treat the smart method as the ``optimal" method for the next stage of our optimization efforts, improving staffing efficiency.
 \section*{Efficiency Mesh}
@@
 Here, each point in our mesh corresponds to a coordinate in the Technician-Pharmacist plane that has a magnitude of profit.
-In order to assure fairness, the simulation is run with the same input sampling for each step, and run 30 times to allow for random variance in choosing queues to be accounted for.
+In order to assure fairness, the simulation is run with the same time distribution sampling inputs for each coordinate configuration, and run 30 times to allow for random variance in choosing queues to be accounted for.
 Let us define the profit function as,
-\[\mathcal{P}=\$55.99(Filled_{Oral}+Filled_{IV})-\$748.92(n_{Pharmacist})-\$63.12(n_{Technician})\] **********Cite money************\\
+\[\mathcal{P}=\mathcal{V}(Filled_{Oral}+Filled_{IV})-\mathcal{C}_{P}(n_{P})-\mathcal{C}_{T}(n_{T})\]
 That is to say, the pharmacy profit for a given employee configuration is revenue per filled order times the number of filled orders less the cost of employees in the configuration.
-Using the Smart Method developed earlier, we create a 3-D surface that describes the profit.
-A 2-D heat-map projection of profit appears in Figure \ref{fig:heatmap}.
-\begin{figure}[h]
+Where $\mathcal{V}$ is the revenue per filled prescription, $n_P$ and $n_T$ are the numbers of pharmacists and technicians in the model, and $\mathcal{C}_P$ and $\mathcal{C}_T$ is the cost per employee of both types.
+From the salary reporting website Glassdoor, we obtain yearly salary data for both pharmacists and pharmacy technicians, and scale it to get an approximate cost for a 12 hour shift in terms of salary \cite{PSalary}\cite{TSalary}.
+Additionally, the average per-prescription revenue is estimated to be $\$55.99$ based on data from 2016 \cite{Revenue}.
+With this data in hand, we may write the profit function as,
+\[\mathcal{P}=\$55.99(Filled_{Oral}+Filled_{IV})-\$748.58(n_{P})-\$161.58(n_{T})\]
+Using the Smart Method developed earlier, we evaluate $\mathcal{P}$ over the mesh of staffing ``coordinates" in order to create a 3-D surface that describes the profit.
+This surface is then projected onto a 2-D heat-map weighted by profit in Figure \ref{fig:heatmap}.
+\begin{figure}[H]
 \centering
@@
 As evidenced by the heat map, we see that the most profitable configurations occur for low numbers of pharmacists and higher numbers of technicians to compensate.
-In fact, we find that the optimal numbers of employees for this test is one pharmacist and seven technicians (6 normal and 1 IV).
-This resulted in a net profit, $\mathcal{P}(1,7)=\$5488.85$, though most of the surrounding mesh points had an approximately similar value, at least in the technician direction.\\
-This being said, there are a number of issues with this efficiency mesh.
-It makes broad assumptions about the value of each filled order, which could obviously be fixed using real data that the pharmacy would be able to provide.
+In fact, we find that the optimal number of employees for this test is one pharmacist and six technicians (5 normal and 1 IV).
+This resulted in an estimated net profit of $\mathcal{P}(1,6)=\$4894.02$ per day, though most of the surrounding mesh points had an approximately similar value, most specifically when moving along the technician axis.\\
+This being said, there are a number of potential issues with this efficiency mesh.
+It makes broad assumptions about the value of each filled order, as well as approximate salary data.
+These approximations could be improved using real world data that the pharmacy would be able to provide, as well as the addition of specific salary data.
+This being said however, due to the massive discrepancy between the salary of pharmacists as opposed to technicians, it is unlikely that the ideal configuration will deviate all that much from our approximation.
 \section*{Conclusions}
 \addcontentsline{toc}{section}{Conclusions}
-After performing both layers of optimization, we see that there is a large range of efficiencies possible for this pharmacy.
+After performing both layers of optimization, we discovered a number of different effects that simple changes to task logic and staffing caused.
+While altering the task choice logic for the pharmacists and main technicians had dramatic effects on the overall effectiveness of the pharmacy, we noted that there was a minimal effect on the IV Technicican.
+In addition, we noticed that regardless of task prioritization method, as overall efficiency increased, the idle times of all employees decreased, while maintaining the trend that pharmacists had less idle time than technicians.
+This is likely due to the fact that they have a larger range of tasks to pull from, as well as the chance to steal a task from a technician.
+%we see that there is a large range of efficiencies possible for this pharmacy.
 As we found before, simple workflow management methods could be implemented to reduce average throughput time by nearly a third, as well as reduce employee idle times...\\
-Note about skill efficiencies and dispositions, as well as leftovers from before, long term running ideas.
-%\subsection*{SIR Model}
-%\addcontentsline{toc}{subsection}{SIR Model}
-%
-%\subsection*{Beta}
-%\addcontentsline{toc}{subsection}{Beta}
-%$\beta$ is a product of many factors, the main being team success, physical locale (weather, population, income), and the social environment of the city\cite{light}.
-In order to compute a given teams $\beta$ value, we must quantify these factors as follows.
-%\subsubsection*{Team Success}
-%\addcontentsline{toc}{subsection}{Team Success}
-%
-%\begin{equation}\label{acoeff}
-%\log(a_t) = 14.1 + 0.2205(WINT)+.091\log(POP)-0.3766\log(INC)
-%\end{equation}
-%\begin{equation}\label{bcoeff}
-%\log(b_t) = 9.171 + .03(WINT)+.028\log(POP)-.1879\log(INC)
-%\end{equation}
-%Each of the coefficients we compute have incredibly large t-values, which aligns with the linear nature of (\ref{a}) and (\ref{b}).
-As such, we are confident that these coefficients are correct for the purposes of our analysis.
-With these coefficients computed, we can compute the following location score for our potential Milwaukee team,
-%
-%\begin{table}[H]
-%\centerfloat
-%\begin{tabular}{lrrrrrrrr}
-%\hline
-%\multicolumn{9}{c}{Location Score for Milwaukee} \\
-%Team & Population$^a$ & GDP per capita$^b$ & Temperature$^c$ & WINT & $a_t$ & $b_t$ & $H_t$ & $h_t$\\
-%\hline
-%Milwaukee & 1.572245 & \$58,680.00 & -2 & 1 & 27583.4 & 1274.342 & 117.1288 & 0.9990123
-%\end{tabular}
-%\caption{$^a$in Millions \cite{population}; $^b$USD \cite{gdp}; $^c$ \degree C \cite{weather}}
-%\label{table:Milwaukee_H}
-%\end{table}
-%
-%\end{description}
+\section*{Further Studies}
+\addcontentsline{toc}{section}{Further Studies}
+\subsection*{Data Improvements}
+\addcontentsline{toc}{subsection}{Data Improvements}
+As we discovered during our analysis, there are many points in this simulation that rely on estimates based on a small amount of data, namely our time distributions for the base case.
+In addition to these estimations, a number of important model effects are omitted due to the lack of data provided.
+Below, we suggest a number of potential improvements to this data.
+\subsubsection*{Time Distribution Updates}
+\addcontentsline{toc}{subsubsection}{Time Distribution Updates}
+During the construction of our models, we used small sample sets of time data to estimate population distribution parameters.
+As such, we potentially ran the risk of under fitting the data, or estimating from fringe data sample cases.
+Larger samples of time data would help us to more accurately get a true estimation of the actual time population parameters.
+Additionally, our model does not allow for employee skill and experience to be factored into the processes at all.
+It seems likely that a pharmacist would have more experience at performing technician level tasks, as they likely were employed as technicians before becoming pharmacists.
+This experience likely translates into faster task completion times, which our model does not account for.
+In this same vein, it is also likely that the incoming order rate is not a constant distribution, but rather a time sensitive process.
+Given that the Mayo Clinic has three main campuses in differing regions of the country, the levels of prescription needs are likely quite different.
+It is likely that more prescriptions are filled during the winter months in the Minnesota area due to an increase in hospitalizations due to vehicle accidents during inclement weather, as well as cold weather related sicknesses; whereas in Florida, there are probably more medications filled for long term conditions like hypertension and blood pressure management due to an older population base, and less winter effects to consider.
+As such, data specific to each region should be included into the model for optimal results.
+\subsubsection*{Other Model Effects}
+\addcontentsline{toc}{subsubsection}{Other Model Effects}
+In addition to the potential issues with the time distribution estimates, there are also a number of human factors that were omitted for simplicity in this study that could potentially be addressed with more data.
+These factors include,
+\begin{itemize}
+\item Failed verification tasks requiring a task to be re-done.
+\item Employee breaks and shift changes.
+\item Leftover prescriptions in various queues from previous day.
+\item Order cancellation/changes.
+\item Impedance by customers (Complaints or questions that occupy an employee for an extended period of time)
+\end{itemize}
+By construction, our model could easily be adapted to include the effects of these factors, using similar techniques to parameter estimation as before.
+This data could be collected and continually updated over time, so that the model is kept current and effective as needs change in the future.
+
 \begin{thebibliography}{9}
@@
 2019, \url{www.statista.com/statistics/315476/prescriptions-in-us-per-capita-by-age-group/}.
-%\bibitem{light} J.
-Light, A.
-Chernin, and J.
-M.
-Heffernan, ``NHL expansion and fan allegiance: a mathematical modelling study,” \textit{Mathematics-in-Industry Case Studies}, vol.
-7, no.
-1, Apr.
-2016.
-%\bibitem{money} M.
-Ozanian and K.
-Badenhausen, ``The NHLs Most Valuable Teams” \textit{Forbes}, 21-Feb-2019.
-[Online].
-Available: \url{https://www.forbes.com/sites/mikeozanian/2018/12/05/the-nhls-most-valuable-teams/}.
-[Accessed: 25-Sep-2019].
-%\bibitem{stats}  HockeyDB.com (2019) National Hockey League history and statistics. \url{http://www.hockeydb.com/ihdb/stats/leagues/141.html}. Web
-%\bibitem{jones}J. C. H. Jones and D. G. Ferguson, ``Location and Survival in the National Hockey League,” \textit{The Journal of Industrial Economics}, vol. 36, no. 4, p. 443, Jun. 1988.
-%\bibitem{population} US Census Bureau and Data Integration Division, ``Population Estimates,” \textit{Metropolitan and Micropolitan Statistical Area Totals Dataset: Population and Estimated Components of Change: April 1, 2010 to July 1, 2014 - U.S Census Bureau}.
-[Online].
-\url{https://web.archive.org/web/20150504102404/http://www.census.gov/popest/data/metro/totals/2014/CBSA-EST2014-alldata.html}.
-[Accessed: 30-Sep-2019].
-%\bibitem{gdp} ``Regional Economic Accounts GDP and Personal Income,” \textit{BEA}.
-[Online].
-\url{https://apps.bea.gov/itable/drilldown.cfm?reqid=70&stepnum=40&Major_Area=5&State=5&Area=XX&TableId=504&Statistic=1&Year=2014&YearBegin=-1&Year_End=-1&Unit_Of_Measure=Levels&Rank=1&Drill=1&nRange=5}.
-[Accessed: 28-Sep-2019].
-%\bibitem{weather} ``Milwaukee Temperatures: Averages by Month,” \textit{Milwaukee WI Average Temperatures by Month - Current Results}.
-[Online].
-\url{https://www.currentresults.com/Weather/Wisconsin/Places/milwaukee-temperatures-by-month-average.php}.
-[Accessed: 30-Sep-2019].
-%\bibitem{whynot} J.
-Hand, C.
-Jozwik, H.
-Magner, Z.
-Brooke, A.
-Landowski, A.
-Parquette, and E.
-Johnson, ``Why Milwaukee is Not an NHL City,” \textit{Milwaukee Magazine}, 16-Nov-2018.
-[Online].
-\url{https://www.milwaukeemag.com/milwaukee-not-nhl-city/}.
-[Accessed: 29-Sep-2019].
-%\bibitem{draft} ``2017 NHL Expansion Draft,” \textit{Wikipedia}, 27-Apr-2019. [Online]. \url{https://en.wikipedia.org/wiki/2017_NHL_Expansion_Draft}. [Accessed: 29-Sep-2019].
-%\bibitem{wisco} ``NHL Players Born in Wisconsin, United States,” \textit{Hockey}.
-[Online].
-\url{https://www.hockey-reference.com/friv/birthplaces.cgi?country=US&province&state=WI&fbclid=IwAR1vb6vzR95-DX0B_zRyV_gLxYcWMneos3Ppn8RBNsnHQqzA9d4sJj4X_aA}.
-[Accessed: 29-Sep-2019].
+\bibitem{PSalary} ``Salary: Pharmacist.” \textit{Glassdoor}, \url{www.glassdoor.com/Salaries/pharmacist-salary-SRCH_KO0,10.htm}.
+\bibitem{TSalary} ``Salary: Pharmacy Technician.” \textit{Glassdoor}, \url{www.glassdoor.com/Salaries/pharmacy-technician-salary-SRCH_KO0,19.htm}.
+\bibitem{Revenue} Fein, Adam J.
+``New Data: Pharmacy Owners' Profits Fall As Industry Competition Rises.” \textit{Drug Channels}, 9 Jan.
+2018, \url{www.drugchannels.net/2018/01/new-data-pharmacy-owners-profits-fall.html}.
 \end{thebibliography}

### 2019-12-12 Mayo/Distributions/DistributionComputer.R

@@ -1,5 +1,5 @@
-#setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Distributions")
-setwd("~/Desktop/Capstone/Mayo/Distributions")
+setwd("~/Desktop/PSM/Fall 2019/Capstone/Mayo/Distributions")
+#setwd("~/Desktop/Capstone/Mayo/Distributions")
 
 rm(list = ls())
 library(fitdistrplus)
@@ -270,3 +270,6 @@ gofstat(ivIncoming.exp)
 (IVPrep.mean <- ivDrugPrep.w[1]$estimate[2]*gamma(1+1/ivDrugPrep.w[1]$estimate[1]))
 (prepVer.mean <- orderPrepVerification.w[1]$estimate[2]*gamma(1+1/orderPrepVerification.w[1]$estimate[1]))
 (disp.mean <- dispensing.norm[1]$estimate[1])
+(totalOral.mean<- entry.mean+entryVer.mean+oralPrep.mean+prepVer.mean+disp.mean)
+(totalIV.mean<- entry.mean+entryVer.mean+IVPrep.mean+prepVer.mean+disp.mean)
+

### 2019-12-12 Mayo/FirstRun/data/CI Base.R

@@ -142,12 +142,12 @@ delta <- zstar*s/sqrt(length(ivOut))
 df <- data.frame(x=c("Oral", "IV"), L=c(lowerOralOut,lowerIVOut), C=c(mean(oralOut), mean(ivOut)), U=c(upperOralOut, upperIVOut))
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(25,75)
 p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
 png("FilledCIs.png")
 p <- ggplot(df, aes(x = x, y = C)) +
   geom_point(size = 4) +
-  geom_errorbar(aes(ymax = U, ymin = L))
+  geom_errorbar(aes(ymax = U, ymin = L))+ylim(25,75)
 p + labs(title = "Orders Filled", x = "Order Type", y="Average Filled")
 dev.off()
 

### 2019-12-12 Mayo/Mail Orders/Script.cpp

@@ -1,0 +1,110 @@
+#include "Script.h"
+
+	Script::Script(){
+		isIV=false;
+		totalTime=0;
+		waitTime=0;
+		inQueue=false;
+	}
+
+	Script::Script(bool IV){
+		isIV=IV;
+		totalTime=0;
+		waitTime=0;
+		inQueue=false;
+	}
+
+	bool Script::getIV(){
+		return isIV;
+	}
+
+	void Script::setIV(bool b){
+		isIV=b;
+	}
+
+	double Script::getEntryTime(){
+		return entryTime;
+	}
+
+	void Script::setEntryTime(double t){
+		entryTime = t;
+	}
+
+	double Script::getEntryVerTime(){
+		return entryVerTime;
+	}
+
+	void Script::setEntryVerTime(double t){
+		entryVerTime=t;
+	}
+
+	double Script::getFillTime(){
+		return fillTime;
+	}
+
+	void Script::setFillTime(double t){
+		fillTime = t;
+	}
+
+	double Script::getFillVerTime(){
+		return fillVerTime;
+	}
+
+	void Script::setFillVerTime(double t){
+		fillVerTime = t;
+	}
+
+	double Script::getDispTime(){
+		return dispTime;
+	}
+
+	void Script::setDispTime(double t){
+		dispTime = t;
+	}
+
+	double Script::getWaitTime(){
+		return waitTime;
+	}
+
+	void Script::updateWaitTime(double t){
+		waitTime+=t;
+	}
+
+	void Script::setWaitTime(double t){
+		waitTime=t;
+	}
+
+	bool Script::getInQueue(){
+		return inQueue;
+	}
+
+	void Script::setInQueue(bool b){
+		inQueue=b;
+	}
+	int Script::getOrderNum(){
+		return orderNumber;
+	}
+	void Script::setOrderNum(int i){
+		orderNumber=i;
+	}
+	double Script::getTotalTime(){
+		return totalTime;
+	}
+	void Script::setTotalTime(double d){
+		totalTime=d;
+	}
+	void Script::updateTotalTime(double d){
+		totalTime=d-totalTime;
+	}
+	double Script::getRunTime(){
+		return runTime;
+	}
+	void Script::calcRunTime(){
+		runTime=entryTime+entryVerTime+fillTime+fillVerTime+dispTime;
+	}
+	void Script::setMail(bool b){
+		isMail=b;
+	}
+	bool Script::getMail(){
+		return isMail;
+	}

### 2019-12-12 Mayo/Mail Orders/Script.h

@@ -1,0 +1,60 @@
+
+//Sourcing error
+#pragma once
+
+//Includes
+#include <iostream>
+#include <vector>
+#include <string>
+#include <queue>
+
+using namespace std;
+
+//Parent Script Class
+class Script{
+	//Public Variables
+	public:
+		Script();
+		Script(bool IV);
+		bool getIV();
+		void setIV(bool b);
+		double getEntryTime();
+		void setEntryTime(double t);
+		double getEntryVerTime();
+		void setEntryVerTime(double t);
+		double getFillTime();
+		void setFillTime(double t);
+		double getFillVerTime();
+		void setFillVerTime(double t);
+		double getDispTime();
+		void setDispTime(double t);
+		double getWaitTime();
+		void updateWaitTime(double t);
+		void setWaitTime(double t);
+		bool getInQueue();
+		void setInQueue(bool b);
+		int getOrderNum();
+		void setOrderNum(int i);
+		double getTotalTime();
+		void setTotalTime(double d);
+		void updateTotalTime(double d);
+		double getRunTime();
+		void calcRunTime();
+		void setMail(bool b);
+		bool getMail();
+	private:
+		//gimme the deets
+		bool isIV;
+		bool isMail;
+		double entryTime;
+		double entryVerTime;
+		double fillTime;
+		double fillVerTime;
+		double dispTime;
+		double totalTime;
+		double waitTime;
+		bool inQueue;
+		int orderNumber;
+		double runTime;
+};
+

### 2019-12-12 Mayo/Mail Orders/SuperQ.cpp

@@ -1,0 +1,47 @@
+#include "SuperQ.h"
+
+	SuperQ::SuperQ(){
+
+	}
+	SuperQ::SuperQ(queue<Script> m, queue<Script> i){
+		mailOrders=m;
+		inPerson=i;
+	}
+	queue<Script> SuperQ::getMailOrders(){
+		return mailOrders;
+	}
+	void SuperQ::setMailOrders(queue<Script> q){
+		mailOrders=q;
+	}
+	queue<Script> SuperQ::getInPerson(){
+		return inPerson;
+	}
+	void SuperQ::setInPerson(queue<Script> q){
+		inPerson=q;
+	}
+	void SuperQ::addMailOrder(Script s){
+		mailOrders.push(s);
+	}
+	void SuperQ::addInPerson(Script s){
+		inPerson.push(s);
+	}
+	bool SuperQ::isPersonEmpty(){
+		return inPerson.empty();
+	}
+	bool SuperQ::isMailEmpty(){
+		return mailOrders.empty();
+	}
+	Script SuperQ::getMailTop(){
+		Script t;
+		t=mailOrders.front();
+		mailOrders.pop();
+		return t;
+
+	}
+        Script SuperQ::getPersonTop(){
+		Script t;
+		t=inPerson.front();
+		inPerson.pop();
+		return t;
+	}
+

### 2019-12-12 Mayo/Mail Orders/SuperQ.h

@@ -1,0 +1,28 @@
+#pragma once
+
+#include <queue>
+#include <iostream>
+#include <vector>
+#include <string>
+#include "Script.h"
+
+using namespace std;
+
+class SuperQ{
+	public:
+		SuperQ();
+		SuperQ(queue<Script> m, queue<Script> i);
+		queue<Script> getMailOrders();
+		void setMailOrders(queue<Script> q);
+		queue<Script> getInPerson();
+		void setInPerson(queue<Script> q);
+		void addMailOrder(Script s);
+		void addInPerson(Script s);
+		bool isPersonEmpty();
+		bool isMailEmpty();
+		Script getMailTop();
+		Script getPersonTop();
+	private:
+		queue<Script> mailOrders;
+		queue<Script> inPerson;
+};

### 2019-12-12 Mayo/Mail Orders/main.cpp

@@ -1,0 +1,933 @@
+//Justin Hood 2019 Capstone Project
+
+#include <chrono>
+#include <iostream>
+#include <ctime>
+#include <random>
+#include <string>
+#include <queue>
+#include <algorithm>
+#include <map>
+#include <fstream>
+#include "Script.h"
+#include "Worker.h"
+#include "SuperQ.h"
+
+
+using namespace std;
+
+//Globals
+int numOrders;
+int tic;
+double toc;
+int nSteps;
+int nTrials;
+int step;
+vector<Worker> idleWorkers;
+vector<Worker> activeWorkers;
+int orderNum;
+
+
+////Setup Queues
+queue<double> oralIncoming;
+queue<double> ivIncoming;
+queue<double> entryTimes;
+queue<double> entryVerTimes;
+queue<double> oralPrepTimes;
+queue<double> ivPrepTimes;
+queue<double> prepVerTimes;
+queue<double> dispenseTimes;
+////Process Queues
+//queue<Script> entryQ;
+SuperQ entryQ;
+queue<Script> entryVerQ;
+queue<Script> oralFillQ;
+queue<Script> ivFillQ;
+queue<Script> fillVerQ;
+queue<Script> dispQ;
+queue<Script> endQ;
+//////Queue Length Holder
+/*vector<int> entryQLengths;
+vector<int> entryVerQLengths;
+vector<int> oralFillQLengths;
+vector<int> ivFillQLengths;
+vector<int> fillVerQLengths;
+vector<int> dispQLengths;*/
+
+//Funky Bois
+queue<double> getOralIncoming(int hours);
+queue<double> getIVIncoming(int hours);
+queue<double> getEntryTimes(int num);
+queue<double> getEntryVerTimes(int num);
+queue<double> getOralPrepTimes(int num);
+queue<double> getIVPrepTimes(int num);
+queue<double> getPrepVerTimes(int num);
+queue<double> getDispenseTimes(int num);
+
+int main(){
+	orderNum=1;
+	//Get the user input to the simulation here.
+	int hrs; //Duration of Sim in hours
+	int numP; //Number of Pharmacists
+	int numT; //Number of Technicians
+	int numSim; //Number of simulations to run
+	cout << "Please enter the duration of the simulation in hours:" <<  endl;
+	cin >> hrs;
+	cout << "Please enter the number of steps per minute:" << endl;
+	cin >> tic;
+	cout << "Please enter the number of Pharmacists in the simulation:" << endl;
+	cin >> numP;
[…]

### 2019-12-13 Mayo/Final Draft/Draft.tex
Katies Edits

@@
 With this trend in prescription usage continuing to rise, pharmacies are becoming an ever greater presence in the lives of most Americans.
-As such, pharmacies need to adapt to deal with increasing numbers of orders, as well as increasing the speed and accuracy at which they fill orders in order to remain competitive in an increasingly saturated landscape of pharmacies.
+As such, pharmacies need to adapt to deal with the increasing numbers of orders, as well as improving the speed and accuracy at which they fill prescriptions in order to remain competitive in an increasingly saturated landscape of pharmacies.
 Consequently, pharmacies must adapt their methodologies and staffing requirements in order to optimize efficiency and cost.
-Obviously, testing different optimization schemas is both expensive and time consuming, so pharmacies have begun to consider computer simulation approaches to optimization as a more cost effective solution.\\\hfill\\
+Testing different optimization schemas is both expensive and time consuming, so pharmacies have begun to consider computer simulation approaches to optimization in search of more cost effective solutions.\\\hfill\\
 In this case study, we are tasked with both modeling and optimizing the workflow for a prototype pharmacy based on samples of data regarding task duration and incoming order frequency.
@@
 Once this simulation is running and tested, we shall attempt to improve the efficiency over the base case.
-In order to achieve this goal, we shall attack the optimization on two fronts.
+In order to achieve this goal, we shall attack the optimization on two fronts:
 \begin{enumerate}
@@
 \end{enumerate}
-With these optimizations, we hope to develop a sense of what changes could increase the efficiency of the pharmacy, as well as an idea of what variables could be manipulated to further increase the accuracy of our simulation, and improve the pharmacy's function.
+With these optimizations, we will develop a sense of what changes could increase the efficiency of the pharmacy.
+We will also address which variables could be manipulated to further increase the accuracy of our simulation and therefore improve the pharmacy's function.
 \section*{Background}
@@
 As such, we see that there are six basic tasks in the workflow tied to the two different types of orders: order entry, entry verification, oral or IV preparation, prepared order verification, and distribution through the window.
-As noted before, regulations exist to limit what tasks non-pharmacist level employees may perform.
-These regulations dictate that of the tasks, the verification tasks may only be performed by the pharmacists, while the remaining tasks can be performed by both pharmacists and technicians.
+As noted before, regulations exist to limit which tasks non-pharmacist level employees may perform.
+These regulations dictate that the verification tasks may only be performed by the pharmacists, while the remaining tasks can be performed by both pharmacists and technicians.
 A breakdown of this hierarchy follows in Table \ref{table:tasks}, with pharmacist specific tasks highlighted in red.
@@
 \centering
-\begin{tabular}{|c||c|c|}
+\begin{tabular}{|c||c||c|}
 \hline
 Pharmacist & Technician & IV Technician\\\hline\hline
-Order Entry & Order Entry &\\\hline
-\cellcolor{red!25}Entry Verification && \\\hline
+Order Entry & Order Entry & \cellcolor{black}\\\hline
+\cellcolor{red!25}Entry Verification &\cellcolor{black}& \cellcolor{black}\\\hline
 Oral Drug Preparation & Oral Drug Preparation & \cellcolor{blue!25}IV Drug Preparation\\\hline
-\cellcolor{red!25}Preparation Verification &&\\\hline
-Distribution & Distribution&\\\hline
+\cellcolor{red!25}Preparation Verification &\cellcolor{black}&\cellcolor{black}\\\hline
+Distribution & Distribution&\cellcolor{black}\\\hline
 \end{tabular}
@@
 With this task breakdown in hand, we consider a graphical representation of the path an order takes within the pharmacy, specifically linked to the tasks described above.
-Looking at Figure \ref{fig:flowchart}, we see that the process of filling an order is fairly linear, with the only fork in the workflow occurring after the entry verification step.
+Looking at Figure \ref{fig:flowchart} below, we see that the process of filling an order is fairly linear, with the only fork in the workflow occurring after the entry verification step.
 This fork is due to the necessity of establishing an order's type (Oral vs.
 IV) so it may be put in the appropriate filling queue.
-In our control pharmacy, all IV orders are filled in an isolated room by an ``IV Technician" who only prepares IV prescriptions, and does not assist with any other tasks in the workflow.
+In our control pharmacy, all IV orders are filled in an isolated room by an ``IV Technician" who only prepares IV prescriptions and does not assist with any other tasks in the workflow.
 \begin{figure}[H]
@@
 \includegraphics[scale=.5]{Flowchart.png}
-\caption{Pharmacy workflow by task position noting which tasks are pharmacist only.}
+\caption{Pharmacy workflow by task position showing which tasks are pharmacist only.}
 \label{fig:flowchart}
 \end{figure}
-For our control case, we operate under the assumption that no tasks in this process have any issues with failure or delays.
-This is obviously a simplified case, but we shall construct the simulation in such a way that including it would be quite simple to do.
-With this workflow defined, we consider the next step of building our simulation, identifying the durations of the different tasks.
+For our control case, we operate under the assumption that no tasks in this process have any issues with failures or delays.
+This is a simplified case, but we shall construct the simulation in such a way that including such issues would be quite easy to do.
+With this workflow defined, we consider the next step of building our simulation: identifying the durations of the different tasks.
 \section*{Distribution Identification}
 \addcontentsline{toc}{section}{Distribution Identification}
-As noted above, there are six pivotal tasks that we must establish the duration of in order to effectively perform an analysis.
-In addition to these tasks, we are also aware of the fact that the times between incoming oral and IV orders come from different distributions.
+As noted above, there are six pivotal task durations that we must establish to effectively perform an analysis.
+In addition to these tasks, we are also aware of the fact that the times between incoming oral and IV orders are from different time distributions.
 As part of the supplied data, we have samples of the completion times of each of these eight different categories, ranging in size from 34 to 60 observations.
-Using each of these samples, we shall construct Cullen and Frey graphs to attempt to isolate the correct distributions.
+Using each of these samples, we shall construct Cullen and Frey graphs to isolate the correct distributions.
 These graphs will take the skewness and kurtosis of our task time samples and plot a point in the $skew^2/kurtosis$ plane which can then be mapped to potential distributions based on theoretical values for each distribution.
@@
 Once the data has been fit with each of these distributions, $R$ is used to compute a goodness of fit statistic, the AIC, for each model.
-The AIC is a sort of score for a model, which weights the accuracy of a fitted model against its own complexity.
-By construction, this score decreases for better models, and increases when models become too complex.
-This prevents over-fitting and reliance on sample data values.
+The AIC is a numerical score for a model, which weights the accuracy of a fitted model against its own complexity.
+By construction, this score decreases for better models, and increases when models become too complex or over-fit.
+This scoring helps to reduce reliance on sample data values and many variable  models that do not capture the nature of the true population.
 With this in mind, we consider the AIC scores for each of the three potential distributions for order entry below in Table \ref{table:entryGOF}
@@
 \hline
-& Normal Fit & Gamma Fit & log-normal Fit \\\hline
+& Normal Fit & Gamma Fit & Log-Normal Fit \\\hline
 %Kolomogorov-Smirnov & \cellcolor{green!25}0.05172573 & 0.07123761 & 0.08600921\\\hline
@@
 As such, we shall treat this as the correct distribution for sampling purposes in our simulation.
-The relevant distribution statistics follow,
+The relevant distribution statistics follow:
 \[\text{Order Entry}\sim \text{Normal}(\mu=9.873784,\ \sigma=2.095579)\]
@@
 \addcontentsline{toc}{section}{Base Case}
-To construct the simulation of the pharmacy, the programming language C++ was used due to its speed, as well as object oriented structure.
-This structure allowed for maximal customization of our data, enabling the collection of many different statistics, which we report below.
+To construct the simulation of the pharmacy, the programming language C++ was used due to its speed and object oriented structure.
+This structure allows for maximal customization of our data, enabling the collection of many different statistics, which we report below.
 To build the simulation, two unique class objects were written to house the details required for a given prescription, as well as each of the employees.
@@
 To further remove any bias in the model, the idle worker pool is shuffled randomly before each task assignment step in the simulation.
-This will help to alleviate any artificial effects on worker idle times.
+This will help to alleviate any artificial bias on worker idle times.
 \subsection*{Base Case Results}
@@
 \end{align*}
-We see that we expect just shy of $100$ oral prescriptions, and just shy of $50$ IV orders per day.
+We see that we expect just shy of $100$ oral prescriptions and $50$ IV orders per day.
 This indeed aligns with the expected values given the exponential distribution fit that was assigned to them for time between orders.\\\hfill\\
-Next, we consider the average queue lengths for each task in the workflow,
+Next, we consider the average queue lengths for each task in the workflow:
 \begin{align*}
@@
 These values tell us how many prescription orders were sitting idle at each stage of the fulfillment process, helping us identify potential bottleneck points.\\\hfill\\
-Next, we consider arguably the most valuable statistic to a pharmacy from a business standpoint, the number of filled orders. 
+Next, we consider arguably the most valuable statistic to a pharmacy from a business standpoint: the number of filled orders. 
 \begin{align*}
@@
 We see here that we expect to fill about $70\%-75\%$ of all incoming orders.
-To see whether there is room for improvement in this number, we consider whether the amount of time for orders from start to finish, the ``throughput", as well as the amount of time the order sits idle leave room for improvement.
+To see whether there is room for improvement in this number, we consider whether the amount of time required to fill orders from start to finish, the ``throughput time", as well as the amount of time the order sits idle can be optimized.
 \begin{align*}
@@
 This would lead us to believe that there are better systems that could be implemented to increase the fill speed, and consequently the number of orders filled.\\\hfill\\
-While knowing how long and how fast the orders are moving in the model is important, it is equally important for the pharmacy to measure the efficiency and use of its employees.
+While knowing how long and how fast the orders are moving in the model is important, it is equally important for the pharmacy to measure the efficiency and utilization of its employees.
 Below, we see the estimations for how long each type of employee is idle during the simulations, expressed as a percent of the total time.
@@
 Notably, these are the two tasks in the workflow that are pharmacist specific.
-This congestion then is likely due to the method by which workers received their job assignments.
-With the pharmacists choosing from all possible tasks equally, they can take work from the technicians, who cannot in return work from the verification tasks.
+This congestion is likely due to the method by which workers received their job assignments.
+With the pharmacists choosing from all possible tasks equally, they can take work from the technicians, who cannot in return work from the verification task pools.
 This aligns with the estimated idle times from above, as we found the pharmacists to be idle significantly less than the technicians.
@@
 \addcontentsline{toc}{section}{First Layer of Optimization}
-With the base case of the model constructed and analyzed, we begin the first of our two pronged optimization efforts, optimizing the job choice logic to increase throughput speed, and reduce idle time in the model.
-\subsection*{First Optimization: Lazy Pharmacists}
-\addcontentsline{toc}{subsection}{Lazy Pharmacists}
-Given that the verification tasks are causing congestion in the base model, we consider the effects of changing the job assignment method in the simulation to the following.
+With the base case of the model constructed and analyzed, we begin the first of our two pronged optimization efforts, optimizing the job choice logic to increase throughput speed and reduce idle time in the model.
+\subsection*{First Optimization: Focused Pharmacists}
+\addcontentsline{toc}{subsection}{Focused Pharmacists}
+Given that the verification tasks are causing congestion in the base model, we consider the effects of changing the job assignment method in the simulation to the following:
 \begin{verbatim}
@@
 Under this scheme, the pharmacists will only do pharmacist specific tasks, leaving the technicians to do the remainder of the tasks.
-The hope is that by removing the pharmacists from the technician tasks that not only will the technician idle times be reduced, but also the lengths of the verification queues will be reduced as well.
-Running the simulation with the same parameters as the base case, under the new job choice logic yields some unexpected results.
+The hope is that removing the pharmacists from the technician tasks will reduce not only the technician idle times, but also the lengths of the verification queues.
+Running the simulation with the same parameters as the base case, but with the new job choice logic yields some unexpected results.
 Firstly, the average queue lengths are much different.
@@
 \includegraphics[scale=.35]{ProfQueueCIs.png}
-\caption{Base case (left) vs. Lazy Pharmacist (Right) average queue lengths}
+\caption{Base case (left) vs. Focused Pharmacist (Right) average queue lengths}
 \label{fig:basevprof}
 \end{figure}
-Under the original schema, all queues were essentially empty except for the verification queues, while under our new schema all of the non-verification queues show increases, most specifically the first and last steps of the fill process.
+Under the original schema, all queues were essentially empty except for the verification queues, while under our new schema all of the non-verification queues show increases, most specifically the first and last steps of the process.
 Indeed we find that the average queue length for our new case is slightly larger than before,
-\[\overline{Length}_{Base}=2.648<2.898=\overline{Length}_{Lazy Pharmacist}\]
+\[\overline{Length}_{Base}=2.648<2.898=\overline{Length}_{Focused Pharmacist}\]
 In addition to this, the average idle time for an employee is significantly larger,
-\[\overline{Idle}_{Base}=14.475\% < 21.627\%=\overline{Idle}_{Lazy Pharmacist}\]
-Looking more closely into this idle time data, we see that the average idle time for a pharmacist in the new scheme is approximately $67\%$, which is clearly not an effective use of their time.
+\[\overline{Idle}_{Base}=14.475\% < 21.627\%=\overline{Idle}_{Focused Pharmacist}\]
+Looking more closely into this idle time data, we see that the average idle time for a pharmacist in the new scheme is approximately $67\%$, which is still not an effective use of their time.
 Before looking to see if reducing the number of pharmacists in the model would help to reduce this idle percentage, we first consider the filled order results under this scheme.
@@
 \includegraphics[scale=.35]{ProfFilledCIs.png}
-\caption{Base case (left) vs. Lazy Pharmacist (Right) average number of filled orders}
+\caption{Base case (left) vs. Focused Pharmacist (Right) average number of filled orders}
 \label{fig:baseprofFill}
 \end{figure}
-We see that in fact this method has reduced both the number of oral and IV orders that are filled over the duration of the simulation.
-It is likely not worth exploring further in terms of staffing optimizations as an ``over-staffed" run yielded worse results.
+We see that in fact this method has reduced both the number of oral and IV orders that are filled over the duration of the simulation, which is our most valuable statistic from a business standpoint.
+It is likely not worth exploring further in terms of staffing optimizations as this ``base-staffed" run yielded worse results than a method based purely on randomness.
 As such, we seek to find a better process optimization.
@@
 \addcontentsline{toc}{subsection}{Largest Queue}
-Given that forcing the pharmacists to only pull from the verification tasks is hurting the efficiency of the model, we consider a new job assignment logic, choosing the most full task queue.
-So, a pharmacist will choose to take their next task from the largest of all five possible queues, while technicians may choose from the three technician level queues.
-This method should help to ensure that both employees and orders are moving as efficiently as possible as it favors maintaining the smallest possible net queue sizes.
+Given that forcing the pharmacists to only pull from the verification tasks is hurting the efficiency of the model, we consider a new job assignment logic: choosing the most full task queue.
+In this optimization a pharmacist will choose to take their next task from the largest of all five possible queues, while technicians choose from the three technician level queues.
+This method should help to ensure that both employees and orders are moving as efficiently as possible because it favors maintaining the smallest possible net queue sizes.
 Running the simulation with the same parameters as the base case, under the new job choice logic yields results that are more aligned with what we would expect.
-Figure \ref{fig:basevlong} shows the comparison on average queue lengths between the base case and the longest queue method.
+Figure \ref{fig:basevlong} shows the comparison of average queue lengths between the base case and the longest queue method.
 \begin{figure}[H]
@@
 \end{figure}
-We see that under this new system, all of the queues (except IV fill) have non-zero means, but that they are all relatively small compared to the mean of approximately 10 for the base entry verification length.
-Looking deeper into the data, we see that the average queue length is reduced from $2.648$ in the base case to $1.389$ in this new method.
+We see that under this new system, all of the queues (except IV fill) have non-zero means, but that they are all relatively small compared to the mean of approximately $10$ orders for the base entry verification length.
+Looking deeper into the data, we see that the average queue length is reduced from $2.648$ orders in the base case to $1.389$ orders in this new method.
 In addition to this, average idle time for the workers is reduced from $14.475\%$ in our base model to $13.395\%$.
-While these changes may seem somewhat small, consider now the mean throughput times between the two models.
+While these changes may seem somewhat small, consider now the mean throughput times between the two models, as shown in Figure \ref{fig:basevlongthrough}.
 \begin{figure}[H]
@@
 As we would expect, this also helps to reduce the average wait time for orders, as well as the idle times of the employees.
-While this method is clearly superior to the base case, we consider finally a combination of the Lazy Pharmacist and Longest Queue methods.
-\subsection*{Third Optimization: Smart Method}
-\addcontentsline{toc}{subsection}{Smart Method}
-As our final job assignment optimization we consider a sort of mixture between choosing the longest queue and relegating the pharmacists to the verification queues.
+While this method is clearly superior to the base case, we will consider finally a combination of the Focused Pharmacist and Longest Queue methods.
+\subsection*{Third Optimization: Combined Method}
+\addcontentsline{toc}{subsection}{Combined Method}
+As our final job assignment optimization we consider a mixture between choosing the longest queue and relegating the pharmacists to the verification queues.
 Namely, under this schema, the pharmacist will first check to see if any of the verification queues are non-empty, and if so, they will choose the largest one.
 Otherwise, they choose the largest from the remaining queues.
-The technicians remain unchanged from before, always choosing a task from the largest queue.
+The technicians remain unchanged from before, always choosing a task from the largest technician queue.
 \begin{verbatim}
@@
 \end{verbatim}
-Again we implement this model with the basic parameters from before, getting again better results than before.
-As before, we consider the comparison between the base case and the smart method queue lengths to begin to test whether we have achieved optimization.
+Again we implement this model with the basic parameters, getting better results than before.
+We consider the comparison between the base case and the combined method queue lengths to begin to test whether we have achieved optimization.
 \begin{figure}[H]
@@
 \includegraphics[scale=.35]{SmartQueueCIs.png}
-\caption{Base Case (left) vs. Smart Method (Right) average queue lengths}
+\caption{Base Case (left) vs. Combined Method (Right) average queue lengths}
 \label{fig:basevsmart}
 \end{figure}
-As with the longest queue method we see a significant reduction in the average queue length, going from $2.6475$ in the base case to $1.1869$ under the smart method.
-Since we have established that the longest queue is our front-runner for the optimization, we shall also use it as a basis for comparison for this smart method.
+From Figure \ref{fig:basevsmart}, we see a significant reduction in the average queue length, going from $2.6475$ orders in the base case to $1.1869$ orders  under the combined method.
+Since we have established that the longest queue is our front-runner for the optimization, we shall also use it as a basis for comparison for this combined method.
 Figure \ref{fig:longvsmart} contains the comparison between the average queue lengths for these two methods.
@@
 \includegraphics[scale=.35]{SmartQueueCIs.png}
-\caption{Longest Queue (Left) vs. Smart Method (Right) average queue lengths}
+\caption{Longest Queue (Left) vs. Combined Method (Right) average queue lengths}
 \label{fig:longvsmart}
 \end{figure}
-As expected based on the results of the lazy pharmacist method, we see improvement in the size of the verification queue lengths at the slight cost to the remainder of the queue lengths.
+As expected based on the results of the focused pharmacist method, we see improvement in the size of the verification queue lengths at the slight cost to the remaining queue lengths.
 Looking into the data we find,
-\[\overline{Length}_{Longest}=1.389 > 1.187 = \overline{Length}_{Smart}\]
-\[\overline{Throughput}_{Longest}=71.813 > 64.920 = \overline{Throughput}_{Smart}\]
-It would appear that we have achieved a slight increase in effectiveness with this new implementation, but it is hard to say given the relative magnitudes of the standard deviations in the data, thus further analysis is required.
+\[\overline{Length}_{Longest}=1.389 > 1.187 = \overline{Length}_{Combined}\]
+\[\overline{Throughput}_{Longest}=71.813 > 64.920 = \overline{Throughput}_{Combined}\]
+It would appear that we have achieved an increase in effectiveness with this new implementation, but it is hard to say given the relative magnitudes of the standard deviations in the data, thus further analysis is required.
 \section*{Comparing the First Stage Optimizations}
@@
 Looking first at the IV filled data across the different methods, we see no marked difference among the four, they are all within one standard deviation of each other.
-As such, we shall focus on the oral filled data, as there is more significant variation in the results.
+We shall focus on the oral filled data, as there is more significant variation in these results.
 First, let us consider a collation of the oral filled data across the methods, Table \ref{table:collate}.
@@
 Base Case & $68.8$ & $4.40$ & $30$\\\hline
-Lazy Pharmacist & $61.7$ & $4.85$ & $30$\\\hline
+Focused Pharmacist & $61.7$ & $4.85$ & $30$\\\hline
 Largest Queue & $73.3$ & $9.18$ & $30$\\\hline
-Smart Method & $78.4$ & $6.04$ & $30$\\\hline
+Combined Method & $78.4$ & $6.04$ & $30$\\\hline
 \end{tabular}
@@
 \end{figure}
-We see from Figure \ref{fig:anovaBox} that there does seem to be a difference among the models, though it is hard to confirm visually, especially for the longest queue and smart methods.
+We see from Figure \ref{fig:anovaBox} that there does seem to be a difference among the models, though it is hard to confirm visually, especially for the longest queue and combined methods.
 Running the ANOVA test on the null hypothesis of $\mu_i=\mu_j\ \forall i,j\in\text{Methods}$, we arrive at the $F$ statistic,
@@
 Methods & Difference & $p$-value\\\hline\hline
-Lazy-Base   &  $-7.133333$ & $0.0001922$\\\hline
+Focused-Base   &  $-7.133333$ & $0.0001922$\\\hline
 \cellcolor{yellow!25}Largest-Base  & \cellcolor{yellow!25}$4.500000$ & \cellcolor{yellow!25}$0.0367813$\\\hline
-Smart-Base  &   $9.600000$ & $0.0000003$\\\hline
-Largest-Lazy & $11.633333$ & $0.0000000$\\\hline
-Smart-Lazy  &  $16.733333$ & $0.0000000$\\\hline
-\cellcolor{yellow!25}Smart-Largest & \cellcolor{yellow!25}$5.100000$ & \cellcolor{yellow!25}$0.0132541$\\\hline
+Combined-Base  &   $9.600000$ & $0.0000003$\\\hline
+Largest-Focused & $11.633333$ & $0.0000000$\\\hline
+Combined-Focused  &  $16.733333$ & $0.0000000$\\\hline
+\cellcolor{yellow!25}Combined-Largest & \cellcolor{yellow!25}$5.100000$ & \cellcolor{yellow!25}$0.0132541$\\\hline
 \end{tabular}
@@
 \end{table}
-The results in Table \ref{table:tukey} are essentially pairwise $t$-tests to compare the means of each methods oral throughput.
-Note, Table \ref{table:tukey} has two rows highlighted.
-These rows correspond to the differences between the base method and largest queue method, as well as the largest queue method to the smart method.
+The results in Table \ref{table:tukey} are analogous to pairwise $t$-tests comparing the means of each method's oral throughput.
+Note: Table \ref{table:tukey} has two rows highlighted.
+These rows correspond to the differences between the base method and the largest queue method, as well as between the largest queue method and the combined method.
 Using our standard $\alpha=0.05$, we can draw the following conclusion comparing the different methods,
-\[\text{Smart $>$ Largest $>$ Base}\]
-Note, this alpha comparison does not require a Bonferroni correction, as $R$ computes the adjusted $p$-value to correct for the multiple comparisons taking place.
-From these results, we see that while the largest queue did provide significant improvement over the base case, the smart method provided a significant improvement over the largest method.
-As such, we shall treat the smart method as the ``optimal" method for the next stage of our optimization efforts, improving staffing efficiency.
+\[\text{Combined $>$ Largest $>$ Base}\]
+Note: this alpha comparison does not require a Bonferroni correction, as $R$ computes the adjusted $p$-value to correct for the multiple comparisons taking place.
+From these results, we see that while the largest queue did provide significant improvement over the base case, the combined method provided significant improvement over the largest queue method.
+As such, we shall treat the combined method as the ``optimal" method for the next stage of our optimization efforts, improving staffing efficiency.
 \section*{Efficiency Mesh}
@@
 While this may be the current conditions of the pharmacy, it is still possible that this is not the most cost effective staffing.
-In order to determine the best possible configuration of employees, we shall construct a $10\times 10$ mesh that defines the pharmacies profit as a function of the number of employees of each type.
+In order to determine the best possible configuration of employees, we shall construct a $10\times 10$ mesh that defines the pharmacy's profit as a function of the number of employees of each type.
 Here, each point in our mesh corresponds to a coordinate in the Technician-Pharmacist plane that has a magnitude of profit.
@@
 \[\mathcal{P}=\$55.99(Filled_{Oral}+Filled_{IV})-\$748.58(n_{P})-\$161.58(n_{T})\]
-Using the Smart Method developed earlier, we evaluate $\mathcal{P}$ over the mesh of staffing ``coordinates" in order to create a 3-D surface that describes the profit.
+Using the Combined Method developed earlier, we evaluate $\mathcal{P}$ over the mesh of staffing ``coordinates" in order to create a 3-D surface that describes the profit.
 This surface is then projected onto a 2-D heat-map weighted by profit in Figure \ref{fig:heatmap}.
@@
 \includegraphics[scale=.75]{profitheatmap.png}
-\caption{Heatmap of profit values using the Smart Method. Note, labeling on the $x$ and $y$ axes is reduced by one due to indexing.}
+\caption{Heatmap of profit values using the Combined Method. Note, labeling on the $x$ and $y$ axes is reduced by one due to indexing.}
 \label{fig:heatmap}
 \end{figure}
-As evidenced by the heat map, we see that the most profitable configurations occur for low numbers of pharmacists and higher numbers of technicians to compensate.
+As evidenced by the heat map, we see that the most profitable configurations occur for lower numbers of pharmacists and higher numbers of technicians to compensate.
 In fact, we find that the optimal number of employees for this test is one pharmacist and six technicians (5 normal and 1 IV).
@@
 These approximations could be improved using real world data that the pharmacy would be able to provide, as well as the addition of specific salary data.
-This being said however, due to the massive discrepancy between the salary of pharmacists as opposed to technicians, it is unlikely that the ideal configuration will deviate all that much from our approximation.
+However, due to the massive discrepancy between the salary of pharmacists as opposed to technicians, it is unlikely that the ideal configuration will deviate much from our approximation.
 \section*{Conclusions}
@@
 After performing both layers of optimization, we discovered a number of different effects that simple changes to task logic and staffing caused.
-While altering the task choice logic for the pharmacists and main technicians had dramatic effects on the overall effectiveness of the pharmacy, we noted that there was a minimal effect on the IV Technicican.
-In addition, we noticed that regardless of task prioritization method, as overall efficiency increased, the idle times of all employees decreased, while maintaining the trend that pharmacists had less idle time than technicians.
-This is likely due to the fact that they have a larger range of tasks to pull from, as well as the chance to steal a task from a technician.
+While altering the task choice logic for the pharmacists and main technicians had a dramatic impact on the overall effectiveness of the pharmacy, we noted that there was a minimal effect on the IV Technicican.
+In addition, we noticed that regardless of task prioritization method, as overall efficiency increased, the idle times of all employees decreased while still maintaining the trend that pharmacists had less idle time than technicians.
+This is likely due to the fact that they have a larger range of tasks to pull from as well as the chance to steal a task from a technician.
 %we see that there is a large range of efficiencies possible for this pharmacy.
@@
 During the construction of our models, we used small sample sets of time data to estimate population distribution parameters.
-As such, we potentially ran the risk of under fitting the data, or estimating from fringe data sample cases.
-Larger samples of time data would help us to more accurately get a true estimation of the actual time population parameters.
-Additionally, our model does not allow for employee skill and experience to be factored into the processes at all.
+As such, we potentially ran the risk of under-fitting the data or estimating from fringe data sample cases.
+Larger samples of time data would help us more accurately get an estimation of the actual time population parameters.
+Additionally, our model does not allow for employee skill and experience to be factored into the processes.
 It seems likely that a pharmacist would have more experience at performing technician level tasks, as they likely were employed as technicians before becoming pharmacists.
@@
 Given that the Mayo Clinic has three main campuses in differing regions of the country, the levels of prescription needs are likely quite different.
-It is likely that more prescriptions are filled during the winter months in the Minnesota area due to an increase in hospitalizations due to vehicle accidents during inclement weather, as well as cold weather related sicknesses; whereas in Florida, there are probably more medications filled for long term conditions like hypertension and blood pressure management due to an older population base, and less winter effects to consider.
+It is likely that more prescriptions are filled during the winter months in the Minnesota area based on an increase in hospitalizations due to vehicle accidents during inclement weather as well as cold weather related sicknesses; whereas in Florida, there are probably more medications filled for long term conditions like hypertension and blood pressure management due to an older population base.
 As such, data specific to each region should be included into the model for optimal results.
@@
 In addition to the potential issues with the time distribution estimates, there are also a number of human factors that were omitted for simplicity in this study that could potentially be addressed with more data.
-These factors include,
+These factors include:
 \begin{itemize}
@@
 \item Order cancellation/changes.
-\item Impedance by customers (Complaints or questions that occupy an employee for an extended period of time)
+\item Impedance by customers (complaints or questions that occupy an employee for an extended period of time)
 \end{itemize}
-By construction, our model could easily be adapted to include the effects of these factors, using similar techniques to parameter estimation as before.
+By construction, our model could easily be adapted to include the effects of these factors using similar techniques to parameter estimation as before.
 This data could be collected and continually updated over time, so that the model is kept current and effective as needs change in the future.

### 2019-12-13 Mayo/Final Draft/Draft.tex
You're a master now

@@
 %*******************************************************************%
-\title{\bf Mayo Pharmacy Optimization Case Study\\
+\title{\huge\bf Mayo Pharmacy Optimization Case Study\\
 \large Using Discrete Event Simulation}  % Supply information
@@
 \addcontentsline{toc}{section}{Abstract}
+The use of prescription medication is becoming more and more commonplace in the United States \cite{georgetown}.
+To combat this, many pharmacies have begun to implement computer simulations to help optimize work flow to reduce cost and waste.
+In this case study, we modeled both the current methodology as well as several different new ``task logics" to get statistical evidence for which was best.
+In addition to this work flow optimization, a staff type optimization was also implemented to maximize profit.
+The results of our analysis point to a size and task prioritized logic, with smaller numbers of pharmacists replaced with more technicians as the most cost effective and efficient configurations.
+\newpage
 \section*{Introduction}                % Print a "chapter" heading\
@@
 Testing different optimization schemas is both expensive and time consuming, so pharmacies have begun to consider computer simulation approaches to optimization in search of more cost effective solutions.\\\hfill\\
-In this case study, we are tasked with both modeling and optimizing the workflow for a prototype pharmacy based on samples of data regarding task duration and incoming order frequency.
+In this case study, we are tasked with both modeling and optimizing the work flow for a prototype pharmacy based on samples of data regarding task duration and incoming order frequency.
 In addition to the sample data for the pharmacy, we are also given a brief overview of the basic order fulfillment process.
@@
 \begin{enumerate}
-\item Optimizing task priority within the workflow (picking the best task to pull from)
+\item Optimizing task priority within the work flow (picking the best task to pull from)
 \item Optimizing staff breakdown (profit optimizing number of pharmacists vs. technicians to employ)
@@
 Upon being filled, the order is again verified by a pharmacist, and then dispensed to the consumer by a technician.
-As such, we see that there are six basic tasks in the workflow tied to the two different types of orders: order entry, entry verification, oral or IV preparation, prepared order verification, and distribution through the window.
+As such, we see that there are six basic tasks in the work flow tied to the two different types of orders: order entry, entry verification, oral or IV preparation, prepared order verification, and distribution through the window.
 As noted before, regulations exist to limit which tasks non-pharmacist level employees may perform.
@@
 \item Order cancellation/changes.
-\item Impedance by customers (complaints or questions that occupy an employee for an extended period of time)
+\item Impedance by customers (complaints or questions that occupy an employee for an extended period of time).
+\item Prioritization of in-person orders over mail orders.
 \end{itemize}
-By construction, our model could easily be adapted to include the effects of these factors using similar techniques to parameter estimation as before.
+By construction, our model could be adapted to include the effects of these factors using similar techniques to parameter estimation as before.
 This data could be collected and continually updated over time, so that the model is kept current and effective as needs change in the future.
-
 \begin{thebibliography}{9}
@@
 2018, \url{www.drugchannels.net/2018/01/new-data-pharmacy-owners-profits-fall.html}.
+\bibitem{DiscretePharm} Reynolds, Matthew, et al.
+``Using Discrete Event Simulation to Design a More Efficient Hospital Pharmacy for Outpatients.” \textit{Health Care Management Science}, vol.
+14, no.
+3, 2011, pp.
+223–236., doi:10.1007/s10729-011-9151-1.
+\bibitem{Discrete} Reynolds, Matthew, et al.
+``Using Discrete Event Simulation to Design a More Efficient Hospital Pharmacy for Outpatients.” \textit{Health Care Management Science}, vol.
+14, no.
+3, 2011, pp.
+223–236., doi:10.1007/s10729-011-9151-1.
 \end{thebibliography}

### 2019-12-13 Mayo/Mail Orders/main.cpp

@@ -40,12 +40,12 @@ queue<double> dispenseTimes;
 ////Process Queues
 //queue<Script> entryQ;
 SuperQ entryQ;
-queue<Script> entryVerQ;
-queue<Script> oralFillQ;
-queue<Script> ivFillQ;
-queue<Script> fillVerQ;
-queue<Script> dispQ;
-queue<Script> endQ;
+SuperQ entryVerQ;
+SuperQ oralFillQ;
+SuperQ ivFillQ;
+SuperQ fillVerQ;
+SuperQ dispQ;
+SuperQ endQ;
 //////Queue Length Holder
 /*vector<int> entryQLengths;
 vector<int> entryVerQLengths;
@@ -63,6 +63,7 @@ queue<double> getOralPrepTimes(int num);
 queue<double> getIVPrepTimes(int num);
 queue<double> getPrepVerTimes(int num);
 queue<double> getDispenseTimes(int num);
+double getRandPercent();
 
 int main(){
 	orderNum=1;
@@ -185,6 +186,12 @@ int main(){
 			if(oralIncoming.size() > 0 && ivIncoming.size() > 0){
 				//First Case, oral enters, but iv does not.
 				if(oralIncoming.front()-toc <=0 && ivIncoming.front()-toc >0){
+					//Set the Mail Status
+					if(getRandPercent()<=0.25){
+						nextOral.setMail(false);
+					}else{
+						nextOral.setMail(true);
+					}
 					//Start the total timer.
 					nextOral.setTotalTime(step);
 					//Entry Time
@@ -208,12 +215,22 @@ int main(){
 					//Set order number and push to queue
 					nextOral.setOrderNum(orderNum);
 					orderNum+=1;
-					entryQ.push(nextOral);
-					
+					if(nextOral.getMail()){
+						entryQ.addMailOrder(nextOral);
+					}else{
+						entryQ.addInPerson(nextOral);
+					}
 					//Step IV, pop the front off of the Oral
 					ivIncoming.front()-=toc;
 					oralIncoming.pop();
 				}else if(oralIncoming.front()-toc >0 && ivIncoming.front()-toc <= 0){
+					//Set the Mail Status
+					if(getRandPercent()<=0.25){
+						nextIV.setMail(false);
+					}else{
+						nextIV.setMail(true);
+					}	
+
 					//Start the total timer.
 					nextIV.setTotalTime(step);
 					//Entry Time
@@ -237,7 +254,11 @@ int main(){
[…]
